### 2015-05-04 descriptive_analysis.Rmd
Added question code book and an Rmd for descriptive analysis.

---
title: "Untitled"
output: html_document
---

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}

library(parsedate)
library(dplyr)
library(zoo)

(load("./JDAP 2_clean.rda"))
library(ggplot2)

d$PublicationDate <- parse_date(with(d, paste(month, year))) %>% as.yearqtr %>% as.character # as.yearqtr # as.yearmon
d$StartDate <- parse_date(d$StartDate) %>% as.yearqtr %>% as.character

x <- group_by(d, StartDate, Q=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
x$date <- parse_date(x$StartDate)
x <- x[order(x$date),]

View(x)
x$StartDate
subset(x, N.total > 1000)

ggplot(data=x) + aes(StartDate, P.resp, fill=Q)+geom_bar(stat="identity") #, order=Response, , fill=Q4

ggplot(d, aes(StartDate, Q4))+geom_bar(stat="identity")

qplot(Q4, data=d, geom="bar", fill=Q4)+facet_wrap(~StartDate)

library(HH)

head(d)

?likert

likert(t(apply(data, 2, table)))

summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2015-05-04 descriptive_analysis.Rmd
First descriptive stats regarding the first two questions.

@@
 ---
-title: "Untitled"
+title: "Preliminary data analysis"
 output: html_document
@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+## Data pre-processing
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+Let's take a look at the numbers of responses by response date and publication date. Please keep in mind that the JDAP adoption dates used in the following analysis are approximate.
 
-```{r}
+```{r, cache=TRUE, message=FALSE, echo=FALSE}
 
@@
 library(zoo)
+library(ggplot2)
+library(assertthat)
 
-(load("./JDAP 2_clean.rda"))
-library(ggplot2)
+load("./data/JDAP 2_clean.rda")
+load("./data/jdap_dates.rda")
 
-d$PublicationDate <- parse_date(with(d, paste(month, year))) %>% as.yearqtr %>% as.character # as.yearqtr # as.yearmon
-d$StartDate <- parse_date(d$StartDate) %>% as.yearqtr %>% as.character
+# add the journal info to the main dataset
+assert_that( all(d$journal %in% dates$journal) )
+d <- left_join(d, dates, by="journal")
 
-x <- group_by(d, StartDate, Q=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
-x$date <- parse_date(x$StartDate)
-x <- x[order(x$date),]
+# format publication and response dates
+d$PublicationDate <- parse_date(with(d, paste(month, year)))
+d$ResponseDate <- parse_date(d$StartDate) %>% as.yearmon %>% as.POSIXct
 
-View(x)
-x$StartDate
-subset(x, N.total > 1000)
+d$ResponseDate_YM <- as.yearmon(d$ResponseDate) %>% as.character
+d$ResponseDate_YQ <- as.yearqtr(d$ResponseDate) %>% as.character
+d$ResponseDate_Y <- strftime(d$ResponseDate, "%Y") %>% as.character
 
-ggplot(data=x) + aes(StartDate, P.resp, fill=Q)+geom_bar(stat="identity") #, order=Response, , fill=Q4
+d$PublicationDate_YM <- as.yearmon(d$PublicationDate) %>% as.character
+d$PublicationDate_YQ <- as.yearqtr(d$PublicationDate) %>% as.character
+d$PublicationDate_Y  <- strftime(d$PublicationDate, "%Y") %>% as.character
 
-ggplot(d, aes(StartDate, Q4))+geom_bar(stat="identity")
+# determine time since JDAP introduction in the journal where the article was published
+d$DaysPolicyToPublication <- difftime(d$PublicationDate, parse_date(d$policy_start), units="days")
+d$DaysPolicyToResponse <- difftime(d$ResponseDate, parse_date(d$policy_start), units="days")
 
-qplot(Q4, data=d, geom="bar", fill=Q4)+facet_wrap(~StartDate)
+d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
+d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
+d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
+d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
+d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
 
-library(HH)
+# number of responses by response date and journal policy in 2015
+group_by(d, Date=ResponseDate_YQ, policy) %>% dplyr::summarize(N=length(StartDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by response date.")
 
-head(d)
+# number of responses by publication date and journal policy in 2015
+group_by(d, Date=PublicationDate_YQ, policy) %>% dplyr::summarize(N=length(PublicationDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by publication date.")
 
-?likert
-
-likert(t(apply(data, 2, table)))
-
-summary(cars)
+# It seems to make more sense to focus on the publication date for plotting, until it is clear why there are hardly any responses from the second half of 2013.
 ```
 
-You can also embed plots, for example:
+## Critical questions
+
+In the following, I will present an overview of the responses to questions 1 and 2. The questions asked about the strength of agreement/disagreement with the following statements:
+
+* _Question 1_ It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
+Include data sharing that occurs by any mechanism (e.g.
+emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
+* _Question 2_ It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
+
+## Attitudes towards data sharing and archiving by journal type
+
+The following plots show the responses regarding the attitudes towards data sharing and archiving by whether or not the journal has adopted a JDAP-equivalent data archiving policy by now (May 2015).
+
+```{r, echo=FALSE, message=FALSE}
+library(dplyr)
+library(ggplot2)
+source("src/multiplot.R")
+
+x <- group_by(d, PolicyBinary, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- x[order(x$Response, decreasing=T),]
+p1 <- ggplot(data=x) + aes(PolicyBinary, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Current policy")+ylab("Percentage")
+
+x <- group_by(d, PolicyBinary, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- x[order(x$Response, decreasing=T),]
+p2 <- ggplot(data=x) + aes(PolicyBinary, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data archiving is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Current policy")+ylab("Percentage")
+
+p1
+
+p2
+
+```
+
+The same plots side by side. Clearly, data sharing is considered more of a community standard than data archiving.
+```{r, echo=FALSE, fig.width=10}
+
+multiplot(p1, p2, cols=2)
+```
+
+## Attitudes towards data sharing and archiving by journal type and journal JDAP adoption date
+
+The following plots show the responses regarding the attitudes towards data sharing and archiving for participants who (i) published in journals which have note adopted the JDAP so far ('No JDAP'), (ii) published in journals which had not _yet_ adopted the JDAP before publication ('Before JDAP'), and (iii) journals which had adopted the JDAP before publication ('After JDAP).
 
 ```{r, echo=FALSE}
-plot(cars)
+x <- group_by(d, PolicyAdoptedAtPublication, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- x[order(x$Response, decreasing=T),]
+p1 <- ggplot(data=x) + aes(PolicyAdoptedAtPublication, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
+
+x <- group_by(d, PolicyAdoptedAtPublication, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- x[order(x$Response, decreasing=T),]
+p2 <- ggplot(data=x) + aes(PolicyAdoptedAtPublication, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data archiving is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
+
+p1
+
+p2
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+The same plots side by side. Clearly, data sharing is considered more of a community standard than data archiving.
+```{r, echo=FALSE, fig.width=10}
+
+multiplot(p1, p2, cols=2)
+```

### 2015-05-04 data/pre_process_data.R

@@ -1,3 +1,4 @@
+
 library(plyr)
 library(dplyr)
 library(tidyr)
@@ -32,6 +33,7 @@ assign_type_to_columns <- function(d, questions, mapping, levels, to_NA, type=or
 }
 
 
+# TODO: Change the file names. 'JDAP 2.csv' is not a very self-explanatory name.
 
 
 d <- read.csv("./JDAP 2.csv", header=T, fill=TRUE, fileEncoding="UTF-8", as.is=T)
@@ -66,7 +68,7 @@ sort(unique(d$journal))
 ### Recode responses to all questions using the agree-disagree scale
 questions_agree_disagree <- c('Q4','Q5','Q17',sprintf("Q18_%d",1:12),sprintf("Q19_%d",1:10), 'Q21', 'Q22')
 mapping_agree_disagree <- c("Strongly disagree"="Strongly Disagree","Somewhat disagree"="Somewhat Disagree","Somewhat agree"="Somewhat Agree","Strongly agree"="Strongly Agree")
-levels_agree_disagree <- c("Strongly Disagree","Disagree","Somewhat Disagree","Neutral","Somewhat Agree","Agree","Strongly Agree")
+levels_agree_disagree <- rev(c("Strongly Disagree","Disagree","Somewhat Disagree","Neutral","Somewhat Agree","Agree","Strongly Agree"))
 d <- assign_type_to_columns(d, questions_agree_disagree, mapping_agree_disagree, levels_agree_disagree, c("","."))  # TODO: What's with the dots in responses to questions 18-19
   
 
@@ -130,23 +132,24 @@ cur_d[several_values,] <- ""
 # collect all responses in one column
 d$Q11_3 <- unique_nonempty(cur_d)
 
+# 
+# ### Recode responses to question 12
+# cur_d <- d[,paste0("Q12_",1:6)]
+# d <- select(d, -starts_with("Q12_"))
+# # overwrite 'other' if another value was specified as well
+# several_values <- num_nonempty(cur_d) > 1
+# cur_d[several_values, 'Q12_6'] <- ""
+# # treat all other conflicting responses as missing
+# several_values <- num_nonempty(cur_d) > 1
+# # TODO: Figure out what to do with these
+# cur_d[several_values,]
+# cur_d[several_values,] <- ""
+# d$Q12 <- unique_nonempty(cur_d)
 
+save(d, file="./JDAP 2_clean.rda")
[…]

### 2015-05-04 data/pre_process_jdap_dates.R

@@ -1,0 +1,31 @@
+dates <- read.csv("./info/Journal data archiving policies (as relevant to JDAP).csv", as.is=T)
+
+# extract only the relevant parts
+dates <- subset(dates, Abbreviation != "")[,c('Abbreviation','Policy.short','Date.policy.took.effect')]
+colnames(dates) <- c('journal', 'policy', 'policy_start')
+
+# reduce the number of policy categories
+dates[dates$policy=="Unclear", 'policy_start'] <- '-'
+dates[dates$policy=="Unclear", 'policy'] <- 'Encouraged'
+dates[dates$policy=="SomeDataTypesRequired", 'policy'] <- 'Encouraged'
+
+dates[dates$policy_start=='-','policy_start'] <- NA
+#date_boundary <- grepl("[<>]", dates$policy_start)
+#date_range <- grepl("-", dates$policy_start)
+
+
+library(dplyr)
+library(parsedate)
+library(zoo)
+
+# parse_date() can deal with extra characters and the sort of ranges defined here. It uses the second date in the range.
+# parse_date("< 18.08.2010")
+# parse_date("31.12.2010-01.01.2010")
+
+dates$policy_start_str <- dates$policy_start
+
+dates$policy_start <- ""
+dates$policy_start[!is.na(dates$policy_start_str)] <- parse_date(dates$policy_start_str[!is.na(dates$policy_start_str)]) %>% as.character
+dates$policy_start
+
+save(dates, file="./jdap_dates.rda")

### 2015-05-04 src/multiplot.R

@@ -1,0 +1,47 @@
+# From: http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/
+
+# Multiple plot function
+#
+# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
+# - cols:   Number of columns in layout
+# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
+#
+# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
+# then plot 1 will go in the upper left, 2 will go in the upper right, and
+# 3 will go all the way across the bottom.
+#
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}

### 2015-05-04 descriptive_analysis.Rmd
Added sample sizes to plots.

@@
 
-x <- group_by(d, PolicyBinary, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- group_by(d, PolicyBinary, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyBinary, N.total))
 x <- x[order(x$Response, decreasing=T),]
-p1 <- ggplot(data=x) + aes(PolicyBinary, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Current policy")+ylab("Percentage")
+p1 <- ggplot(data=x) + aes(Policy, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Current policy")+ylab("Percentage")
 
-x <- group_by(d, PolicyBinary, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- group_by(d, PolicyBinary, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyBinary, N.total))
 x <- x[order(x$Response, decreasing=T),]
@@
 ```{r, echo=FALSE}
-x <- group_by(d, PolicyAdoptedAtPublication, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- group_by(d, PolicyAdoptedAtPublication, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyAdoptedAtPublication, N.total))
 x <- x[order(x$Response, decreasing=T),]
-p1 <- ggplot(data=x) + aes(PolicyAdoptedAtPublication, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
+p1 <- ggplot(data=x) + aes(Policy, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
 
-x <- group_by(d, PolicyAdoptedAtPublication, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total)
+x <- group_by(d, PolicyAdoptedAtPublication, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyAdoptedAtPublication, N.total))
 x <- x[order(x$Response, decreasing=T),]
-p2 <- ggplot(data=x) + aes(PolicyAdoptedAtPublication, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data archiving is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
+p2 <- ggplot(data=x) + aes(Policy, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data archiving is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
 
@@
 ```
+
+```{r, message=FALSE, eval=FALSE}
+
+library(MASS)
+
+d$cPolicy <- ifelse(d$PolicyAdoptedAtPublication=="After JDAP", .5, -.5)
+d$cDate <- as.yearmon(d$PublicationDate) %>% as.double %>% scale(., scale=F)
+
+summary(d$cDate)
+
+m <- polr(Q4 ~ 1 + cPolicy + cDate, data=d, Hess=TRUE)
+
+summary(m)
+
+multiplot(p1, p2, cols=2)
+```

### 2015-05-04 descriptive_analysis.Rmd
Added ordered logistic model results for the first two questions.

@@
 
-```{r, message=FALSE, eval=FALSE}
+### Inferential statistics
+
+```{r, message=FALSE, eval=TRUE, echo=FALSE}
 
 library(MASS)
+library(zoo)
+library(dplyr)
+library(knitr)
 
-d$cPolicy <- ifelse(d$PolicyAdoptedAtPublication=="After JDAP", .5, -.5)
-d$cDate <- as.yearmon(d$PublicationDate) %>% as.double %>% scale(., scale=F)
+d$cAfterPolicyChange <- ifelse(d$PolicyAdoptedAtPublication=="After JDAP", 1, 0)
+d$cNonJDAPJournal <- ifelse(d$PolicyAdoptedAtPublication=="No JDAP", 1, 0)
+d$cDate <- as.double(as.yearmon(d$PublicationDate)) %>% scale(., scale=F)
 
-summary(d$cDate)
+d$respQ4 <- ordered(d$Q4, levels=rev(levels(d$Q4)))
+d$respQ5 <- ordered(d$Q5, levels=rev(levels(d$Q5)))
 
-m <- polr(Q4 ~ 1 + cPolicy + cDate, data=d, Hess=TRUE)
+m4 <- polr(respQ4 ~ 1 + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
+# summary(m4)
+m4.justchange <- polr(respQ4 ~ 1 + cAfterPolicyChange, data=d , Hess=TRUE)
+m4.nochange <- polr(respQ4 ~ 1 + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
+suppressMessages( ci4 <- confint(m4) )
+table4 <- exp(cbind(OR = coef(m4), ci4)) %>% cbind(., t=coef(summary(m4))[1:nrow(.),'t value'])
+#table4 <- cbind(lOR = coef(m4), ci4) %>% cbind(., t=coef(summary(m4))[1:nrow(.),'t value'])
 
-summary(m)
+#anova(m4, m4.justchange, m4.nochange)
 
-multiplot(p1, p2, cols=2)
+m5 <- polr(respQ5 ~ 1  + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
+m5.justchange <- polr(Q5 ~ 1 + cAfterPolicyChange , data=d, Hess=TRUE)
+m5.nochange <- polr(Q5 ~ 1 + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
+# summary(m5)
+suppressMessages( ci5 <- confint(m5) )
+table5 <- exp(cbind(OR = coef(m5), ci5)) %>% cbind(., t=coef(summary(m5))[1:nrow(.),'t value'])
+
+#anova(m5, m5.justchange, m5.nochange)
 ```
+
+The potential effect of JDAP adoption on authors' attitudes is might be confounded by two other factors.
+Firstly, groups of researchers publishing in journals which are not planning to adopt the JDAP (or at least have not done so yet) may inherently differ from groups publishing in journals which were open to adopting the JDAP.
+Secondly, attitudes regarding data archiving may improve over time.
+
+In order to test for an effect of policy change on attitudes while controlling for potential confounding effects, we used an ordinal logistic regression model with three predictors: (i) journal type _(cNonJDAPJournal)_, (ii) (centered) publication date in years _(cDate)_, and (iii) a variable indicating whether the article was published after the the journal adopted a data archiving policy _(cAfterPolicyChange)_.
+
+The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 1*.
+Effects are statistically significant at the $\alpha=0.05$ level when the transformed confidence intervals do not contain $1$.
+Confidence intervals were obtained by profile likelihood.
+According to the model estimates, the introduction of the JDAP data archiving policy increases the odds of a positive response regarding *data sharing* by factor $1.36$ (CI=$[1.16; 1.60]$), while the remaining two predictors do not show any statistically significant effects.
+```{r, message=FALSE, eval=TRUE, echo=FALSE}
+options(digits=2)
+table4
+```
+
+The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 2*.
+According to the model estimates, the introduction of the JDAP data archiving policy increases the odds of a positive response regarding *data archiving* by factor $1.57$ (CI=$[1.33; 1.90]$), while the remaining two predictors do not show any statistically significant effects.
+
+```{r, message=FALSE, eval=TRUE, echo=FALSE}
+options(digits=2)
+table5
+```

### 2015-05-04 descriptive_analysis.Rmd
Included likelihood-ratio tests for analyses of questions 1 and 2.

@@
 
-#anova(m4, m4.justchange, m4.nochange)
-
 m5 <- polr(respQ5 ~ 1  + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
@@
 
-#anova(m5, m5.justchange, m5.nochange)
+aov.m4.justchange <- anova(m4, m4.justchange)
+aov.m4.nochange <- anova(m4, m4.nochange)
+aov.m5.justchange <- anova(m5, m5.justchange)
+aov.m5.nochange <- anova(m5, m5.nochange)
+
+# aov.m5.nochange
+
 ```
@@
 Confidence intervals were obtained by profile likelihood.
-According to the model estimates, the introduction of the JDAP data archiving policy increases the odds of a positive response regarding *data sharing* by factor $1.36$ (CI=$[1.16; 1.60]$), while the remaining two predictors do not show any statistically significant effects.
+According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data sharing* by a factor of $1.36$ (CI=$[1.16; 1.60]$), while the remaining two predictors do not show any statistically significant effects.
+
+```{r, message=FALSE, eval=TRUE, echo=FALSE}
+options(digits=2)
+```
+
+We conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
+The first likelihood-ratio test, comparing the full three-predictor model with a reduced model without the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m4.nochange[["   Df"]][2]`)=`r aov.m4.nochange[["LR stat."]][2]`$, $p<0.001$).
+A second likelihood-ratio test comparing the full model with a reduced model using only the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m4.justchange[["   Df"]][2]`)=`r aov.m4.justchange[["LR stat."]][2]`$, $p=`r aov.m4.justchange[["Pr(Chi)"]][2]`$).
+
 ```{r, message=FALSE, eval=TRUE, echo=FALSE}
@@
 The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 2*.
-According to the model estimates, the introduction of the JDAP data archiving policy increases the odds of a positive response regarding *data archiving* by factor $1.57$ (CI=$[1.33; 1.90]$), while the remaining two predictors do not show any statistically significant effects.
+According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data archiving* by a factor of $1.57$ (CI=$[1.33; 1.90]$), while the remaining two predictors do not show any statistically significant effects.
+
+Here too, we conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
+The first likelihood-ratio test, comparing the full three-predictor model with a reduced model without the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m5.nochange[["   Df"]][2]`)=`r aov.m5.nochange[["LR stat."]][2]`$, $p<0.001$).
+A second likelihood-ratio test comparing the full model with a reduced model using only the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m5.justchange[["   Df"]][2]`)=`r aov.m5.justchange[["LR stat."]][2]`$, $p=`r aov.m5.justchange[["Pr(Chi)"]][2]`$).
 

### 2015-05-17 descriptive_analysis.Rmd
Renamed data files to have more descriptive names.

@@
 We conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
-The first likelihood-ratio test, comparing the full three-predictor model with a reduced model without the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m4.nochange[["   Df"]][2]`)=`r aov.m4.nochange[["LR stat."]][2]`$, $p<0.001$).
-A second likelihood-ratio test comparing the full model with a reduced model using only the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m4.justchange[["   Df"]][2]`)=`r aov.m4.justchange[["LR stat."]][2]`$, $p=`r aov.m4.justchange[["Pr(Chi)"]][2]`$).
+The first likelihood-ratio test, comparing the full three-predictor model with a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m4.nochange[["   Df"]][2]`)=`r aov.m4.nochange[["LR stat."]][2]`$, $p<0.001$).
+A second likelihood-ratio test comparing the full model with a reduced model using _only_ the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m4.justchange[["   Df"]][2]`)=`r aov.m4.justchange[["LR stat."]][2]`$, $p=`r aov.m4.justchange[["Pr(Chi)"]][2]`$).
 
@@
 Here too, we conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
-The first likelihood-ratio test, comparing the full three-predictor model with a reduced model without the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m5.nochange[["   Df"]][2]`)=`r aov.m5.nochange[["LR stat."]][2]`$, $p<0.001$).
-A second likelihood-ratio test comparing the full model with a reduced model using only the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m5.justchange[["   Df"]][2]`)=`r aov.m5.justchange[["LR stat."]][2]`$, $p=`r aov.m5.justchange[["Pr(Chi)"]][2]`$).
+The first likelihood-ratio test, comparing the full three-predictor model with a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m5.nochange[["   Df"]][2]`)=`r aov.m5.nochange[["LR stat."]][2]`$, $p<0.001$).
+A second likelihood-ratio test comparing the full model with a reduced model using _only_ the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m5.justchange[["   Df"]][2]`)=`r aov.m5.justchange[["LR stat."]][2]`$, $p=`r aov.m5.justchange[["Pr(Chi)"]][2]`$).
 

### 2015-05-17 data/pre_process_data.R

@@ -33,10 +33,7 @@ assign_type_to_columns <- function(d, questions, mapping, levels, to_NA, type=or
 }
 
 
-# TODO: Change the file names. 'JDAP 2.csv' is not a very self-explanatory name.
-
-
-d <- read.csv("./JDAP 2.csv", header=T, fill=TRUE, fileEncoding="UTF-8", as.is=T)
+d <- read.csv("./JDAP_Survey_Data.csv", header=T, fill=TRUE, fileEncoding="UTF-8", as.is=T)
 key <- d[1,]
 d <- d[-1,]
 colnames(d)[1:6] <- as.character(key[1:6])
@@ -146,8 +143,8 @@ d$Q11_3 <- unique_nonempty(cur_d)
 # cur_d[several_values,] <- ""
 # d$Q12 <- unique_nonempty(cur_d)
 
-save(d, file="./JDAP 2_clean.rda")
-write.csv(d, file="./JDAP 2_clean.csv")
+save(d, file="./JDAP_Survey_Data_Tidy.rda")
+write.csv(d, file="./JDAP_Survey_Data_Tidy.csv")
 
 
 

### 2015-05-17 analysis.Rmd
Added an analysis draft file.

--- 2015-05-17 descriptive_analysis.Rmd
@@
 ---
-title: "Preliminary data analysis"
-output: html_document
+title: "Data Archiving Attitudes"
+author: Heather Piwowar, Pavel Logacev, Todd J. Vision
+date: "May 17, 2015"
+output:
+  html_document:
+    fig_caption: yes
+    number_sections: yes
+    toc: yes
+    keep_md: yes
+  word_document:
+    fig_caption: yes
+  pdf_document:
+    fig_caption: yes
+    number_sections: yes
+    toc: yes
+  md_document:
+    variant: markdown_github
+<!-- csl: apa.csl -->
+bibliography: bibliography.bib
 ---
 
-## Data pre-processing
+```{r setup, echo=FALSE, include=TRUE}
+suppressPackageStartupMessages({
+  require(dplyr)
+  require(knitr)
+  require(RColorBrewer)
+})
+```
 
-Let's take a look at the numbers of responses by response date and publication date. Please keep in mind that the JDAP adoption dates used in the following analysis are approximate.
+This is the abstract for now.
+
+# Introduction
+Some researchers are sceptical regarding data archiving.
+We conducted a survey in order to find out how the adoption of data archiving policies by journals affects researcher's attitudes towards archiving and sharing data.
+
+# The Survey
+
+<!-- load and prepare data -->
 
@@
 
-load("./data/JDAP 2_clean.rda")
+load("./data/JDAP_Survey_Data_Tidy.rda")
 load("./data/jdap_dates.rda")
+interactive_mode <- FALSE
 
 # add the journal info to the main dataset
-assert_that( all(d$journal %in% dates$journal) )
+assert_that( all(d$journal %in% dates$journal) ) %>% invisible
 d <- left_join(d, dates, by="journal")
@@
 d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
+```
 
-# number of responses by response date and journal policy in 2015
-group_by(d, Date=ResponseDate_YQ, policy) %>% dplyr::summarize(N=length(StartDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by response date.")
+The survey was carried out using [Survey Monkey](www.surveymonkey.com). Invitations to participate were sent out to $n$ <!-- TODO: how many? -->
+authors by email every month. The average non-response rate was $p$. <!-- TODO: response/non-response rates -->
 
-# number of responses by publication date and journal policy in 2015
-group_by(d, Date=PublicationDate_YQ, policy) %>% dplyr::summarize(N=length(PublicationDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by publication date.")
+```{r, message=FALSE,  echo=FALSE, fig.width=5, fig.height=3, fig.cap="Number of invitations and responses by quarter."}
+library(ggplot2)
+library(dplyr)
 
+#   # number of responses by response date
+#   n_by_date <- group_by(d, Date=ResponseDate_YQ) %>% dplyr::summarize(N=length(Date), type="Responses")
+#   n_by_date <- n_by_date %>% mutate(type="Invitations", N=Inf) %>% rbind(n_by_date, .)
+#   # TODO: Add invitation data for number of invitations, if necessary.
+# 
+#   p_by_date <- n_by_date %>%  ggplot(aes(Date, N, color=type, group=type))+geom_point()+geom_line()+theme_bw()+theme(axis.text.x=element_text(angle=90,hjust=1))+ylab("Number of invitations and responses")+xlab("Quarter") #+ ggtitle("Number of invitations and responses by quarter.")
+#   p_by_date
+#
 # It seems to make more sense to focus on the publication date for plotting, until it is clear why there are hardly any responses from the second half of 2013.
+
+  n_by_publication_date <- group_by(d, Date=PublicationDate_YQ) %>% dplyr::summarize(N=length(Date), type="Responses")
+  n_by_publication_date <- n_by_publication_date %>% mutate(type="Invitations", N=Inf) %>% rbind(n_by_publication_date, .)
+  # TODO: Add invitation data for number of invitations, if necessary.
+
+  p_by_publication_date <- n_by_publication_date %>% ggplot(aes(Date, N, fill=type, alpha=type, group=type)) + 
+                ylab("Number of invitations and responses")+xlab("Date of Publication")+geom_bar(stat="identity") + # geom_point()+geom_line()
+                scale_fill_manual(values=c("blue", "blue"))+scale_alpha_manual(values=c(.5, 1)) + 
+                theme(axis.title.y=element_text(size=rel(0.8)), axis.title.x=element_text(size=rel(0.8)), axis.text.x=element_text(angle=90,hjust=1), legend.title=element_blank())
+  print(p_by_publication_date)
+
+#   source("src/multiplot.R")
+#   multiplot(p_by_date, p_by_publication_date, cols=2)
 ```

### 2015-05-17 analysis.Rmd
Updated question codebook.

@@
 title: "Data Archiving Attitudes"
-author: Heather Piwowar, Pavel Logacev, Todd J. Vision
+author: "Heather Piwowar, Pavel Logacev, Todd J. Vision"
 date: "May 17, 2015"
@@
   html_document:
+    css: style.css
     fig_caption: yes
+    keep_md: yes
     number_sections: yes
     toc: yes
-    keep_md: yes
-  word_document:
-    fig_caption: yes
+  md_document:
+    variant: markdown_github
   pdf_document:
@@
     toc: yes
-  md_document:
-    variant: markdown_github
+  word_document:
+    fig_caption: yes
+bibliography: bibliography.bib
 <!-- csl: apa.csl -->
-bibliography: bibliography.bib
 ---
@@
   require(RColorBrewer)
+  require(knitr)
+  #require(kfigr)
+  opts_chunk$set(message=FALSE, warning=FALSE)
 })
+#knit_hooks$set(plot = function(x, options) {
+#   paste('<figure><img src="',
+#         opts_knit$get('base.url'), paste(x, collapse = '.'),
+#         '"><figcaption>', options$fig.cap, '</figcaption></figure>',
+#         sep = '')
+#})
+
+#knit_hooks$set(plot = function(x, options) {
+#   paste0('<figure><img src="',opts_knit$get('base.url'), paste(x, collapse = '.'),'">',
+#          '<figcaption>', options$fig.cap, '</figcaption></figure>')
+#})
 ```
@@
 authors by email every month. The average non-response rate was $p$. <!-- TODO: response/non-response rates -->
+Figure 1 shows the numbers of invitations and responses by the date of the author's last publication.
 
-```{r, message=FALSE,  echo=FALSE, fig.width=5, fig.height=3, fig.cap="Number of invitations and responses by quarter."}
+Participants filled in a questionnaire consisting of 15 questions, most of which were multiple-choice.
+
+In the following, I will present an overview of the responses to questions 1 and 2. The questions asked about the strength of agreement/disagreement with the following statements:
+
+* _Question 1_ It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
+Include data sharing that occurs by any mechanism (e.g.
+emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
+* _Question 2_ It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
+
+```{r responseRates, cache=FALSE, message=FALSE,  echo=FALSE, fig.width=5, fig.height=3, anchor="figure", fig.cap="Number of invitations and responses by quarter."}
 library(ggplot2)
@@
 ```
-
-## Critical questions
-
-In the following, I will present an overview of the responses to questions 1 and 2. The questions asked about the strength of agreement/disagreement with the following statements:
-
-* _Question 1_ It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
-Include data sharing that occurs by any mechanism (e.g.
-emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
-* _Question 2_ It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
 

### 2015-05-17 data/src/pre_process_jdap_adoption_dates.R
Restructured data directory.

@@ -1,4 +1,4 @@
-dates <- read.csv("./info/Journal data archiving policies (as relevant to JDAP).csv", as.is=T)
+dates <- read.csv("../info/Journal data archiving policies (as relevant to JDAP).csv", as.is=T)
 
 # extract only the relevant parts
 dates <- subset(dates, Abbreviation != "")[,c('Abbreviation','Policy.short','Date.policy.took.effect')]
@@ -28,4 +28,5 @@ dates$policy_start <- ""
 dates$policy_start[!is.na(dates$policy_start_str)] <- parse_date(dates$policy_start_str[!is.na(dates$policy_start_str)]) %>% as.character
 dates$policy_start
 
-save(dates, file="./jdap_dates.rda")
+write.table(dates, file="../Journal_JDAP_Adoption_Dates.csv")
+save(dates, file="../Journal_JDAP_Adoption_Dates.rda")

### 2015-05-17 data/src/pre_process_jdap_invitations.R

@@ -1,0 +1,16 @@
+library(parsedate)
+
+d <- read.csv("../raw_data/Invitations_Timing.csv", as.is=T)
+
+d$sent_date <- parse_date(d$sent_date)
+d$publication_date <- parse_date(paste(d$year, d$data_month)) %>% as.yearmon
+d$year <- NULL
+d$data_month <- NULL
+d$journal[d$journal=="unknown"] <- NA
+
+# all notes are the same: 'initial'
+unique(d$note)
+d$note <- NULL
+
+write.table(d, file="../Invitations_Timing.csv")
+save(d, file="../Invitations_Timing.rda")

### 2015-05-17 data/src/pre_process_responses.R

@@ -33,7 +33,7 @@ assign_type_to_columns <- function(d, questions, mapping, levels, to_NA, type=or
 }
 
 
-d <- read.csv("./JDAP_Survey_Data.csv", header=T, fill=TRUE, fileEncoding="UTF-8", as.is=T)
+d <- read.csv("../raw_data/JDAP_Survey_Data.csv", header=T, fill=TRUE, fileEncoding="UTF-8", as.is=T)
 key <- d[1,]
 d <- d[-1,]
 colnames(d)[1:6] <- as.character(key[1:6])
@@ -143,8 +143,8 @@ d$Q11_3 <- unique_nonempty(cur_d)
 # cur_d[several_values,] <- ""
 # d$Q12 <- unique_nonempty(cur_d)
 
-save(d, file="./JDAP_Survey_Data_Tidy.rda")
-write.csv(d, file="./JDAP_Survey_Data_Tidy.csv")
+save(d, file="../JDAP_Survey_Data_Tidy.rda")
+write.csv(d, file="../JDAP_Survey_Data_Tidy.csv")
 
 
 

### 2015-05-21 analysis.Rmd
Significantly improved visualization of likert data, added some EDA.

--- 2015-05-17 descriptive_analysis.Rmd
@@
 ---
-title: "Preliminary data analysis"
-output: html_document
+title: "Data Archiving Attitudes"
+author: "Heather Piwowar, Pavel Logacev, Todd J. Vision"
+date: "May 17, 2015"
+output:
+  html_document:
+    css: style.css
+    fig_caption: yes
+    keep_md: yes
+    number_sections: yes
+    toc: yes
+  md_document:
+    variant: markdown_github
+  pdf_document:
+    fig_caption: yes
+    number_sections: yes
+    toc: yes
+  word_document:
+    fig_caption: yes
+bibliography: bibliography.bib
+<!-- csl: apa.csl -->
 ---
 
-## Data pre-processing
+```{r setup, echo=FALSE, include=TRUE}
+suppressPackageStartupMessages({
+  require(plyr)
+  require(dplyr)
+  require(knitr)
+  require(RColorBrewer)
+  require(knitr)
+  #require(kfigr)
+  opts_chunk$set(message=FALSE, warning=FALSE)
+})
+#knit_hooks$set(plot = function(x, options) {
+#   paste('<figure><img src="',
+#         opts_knit$get('base.url'), paste(x, collapse = '.'),
+#         '"><figcaption>', options$fig.cap, '</figcaption></figure>',
+#         sep = '')
+#})
 
-Let's take a look at the numbers of responses by response date and publication date. Please keep in mind that the JDAP adoption dates used in the following analysis are approximate.
+#knit_hooks$set(plot = function(x, options) {
+#   paste0('<figure><img src="',opts_knit$get('base.url'), paste(x, collapse = '.'),'">',
+#          '<figcaption>', options$fig.cap, '</figcaption></figure>')
+#})
+
+```
+
+This is where the abstract goes.
+
+# Introduction
+Some researchers are sceptical regarding data archiving.
+We conducted a survey in order to find out how the adoption of data archiving policies by journals affects researcher's attitudes towards archiving and sharing data.
+
+# The Survey
+
+## Method
+
+<!-- load and prepare data -->
 
@@
 library(parsedate)
+library(plyr)
 library(dplyr)
@@
 
-load("./data/JDAP 2_clean.rda")
-load("./data/jdap_dates.rda")
+load("./data/JDAP_Survey_Data_Tidy.rda") # loads 'd'
+load("./data/Journal_JDAP_Adoption_Dates.rda") # loads 'dates'
+load("./data/Invitations_Timing.rda") # loads 'invitation_timing'
+interactive_mode <- FALSE
 
 # add the journal info to the main dataset
-assert_that( all(d$journal %in% dates$journal) )
-d <- left_join(d, dates, by="journal")
+assert_that( all(d$journal %in% dates$journal) ) %>% invisible
+d <- left_join(d, dates, by="Journal")
 
-# format publication and response dates
-d$PublicationDate <- parse_date(with(d, paste(month, year)))
-d$ResponseDate <- parse_date(d$StartDate) %>% as.yearmon %>% as.POSIXct
+# # format publication and response dates
+d$PublicationDate <- parse_date(d$PublicationDate) %>% as.yearmon
+d$ResponseDate <- parse_date(d$ResponseDate) %>% as.yearmon
 
@@
 d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
-d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
+# d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
 
-# number of responses by response date and journal policy in 2015
-group_by(d, Date=ResponseDate_YQ, policy) %>% dplyr::summarize(N=length(StartDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by response date.")
+# NOTE: two invitations have NA for a publication date
+# subset(invitation_timing, is.na(publication_date))
 
-# number of responses by publication date and journal policy in 2015
-group_by(d, Date=PublicationDate_YQ, policy) %>% dplyr::summarize(N=length(PublicationDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by publication date.")
+invitation_timing <- subset(invitation_timing, !is.na(publication_date))
+invitation_timing$PublicationDate_YQ <- as.character(invitation_timing$publication_date) %>% parse_date %>% as.yearqtr
+n_invitations_by_publication <- ddply(invitation_timing, .(Date=PublicationDate_YQ), summarize, N=length(PublicationDate_YQ))
+n_invitations_by_sent_month <- ddply(invitation_timing, .(Date=as.yearmon(sent_date)), summarize, N=length(PublicationDate_YQ))
 
-# It seems to make more sense to focus on the publication date for plotting, until it is clear why there are hardly any responses from the second half of 2013.
+d$label_PolicyAdoptedAtPublication <- gsub(" ", "\n", d$PolicyAdoptedAtPublication)
+
 ```
 
-## Critical questions
+The survey was carried out using [Survey Monkey](www.surveymonkey.com).
+Invitations to participate were sent out monthly between February 2011 and March 2014 to a selection of between $`r min(n_invitations_by_sent_month$N)`$ and $`r max(n_invitations_by_sent_month$N)`$ (with an average of $`r round(mean(n_invitations_by_sent_month$N))`$) authors of recently published articles in a pre-selected sample of journals.
+<!-- TODO: how were the journals selected -->
+The invitations were sent out to a total of $`r nrow(invitation_timing)`$ authors, and $`r nrow(d)`$ responded (corresponding to a non-response rate of $`r round(100*nrow(d)/nrow(invitation_timing))`$\%).
+Figure 1 shows the numbers of invitations and responses by the date of the author's last publication.
+Participants filled in a questionnaire consisting of 15 multiple-choice questions regarding their attitudes, concerns and experiences with data archiving and sharing.
+
+```{r responseRates, cache=FALSE, message=FALSE, echo=FALSE, fig.width=5, fig.height=3, anchor="figure", fig.cap="Number of invitations and responses by quarter."}
+
+library(ggplot2)
+library(dplyr)
+library(zoo)
+library(parsedate)
+
+n_by_publication_date <- ddply(d, .(Date=as.character(PublicationDate_YQ)), function(x) c(N=nrow(x))) %>% cbind(., type="Responses")
+n_invitations_by_publication$Date <- as.character(n_invitations_by_publication$Date)
+n_by_publication_date <- n_by_publication_date %>% rbind( cbind(n_invitations_by_publication, type="Invitations"), .)
+
+p_by_publication_date <- n_by_publication_date %>% ggplot(aes(Date, N, fill=type, alpha=type, group=type)) + 
+              ylab("Number of invitations and responses")+xlab("Date of Publication")+geom_bar(stat="identity", position="dodge") +
+              scale_fill_manual(values=c("blue", "blue"))+scale_alpha_manual(values=c(.5, 1))+theme_bw() + 
+              theme(axis.title.y=element_text(size=rel(0.8)), axis.title.x=element_text(size=rel(0.8)), axis.text.x=element_text(angle=90,hjust=1), legend.title=element_blank())
+
+print(p_by_publication_date)
+```
+
+<!-- TODO: how were the responses spread out over journal types? when was the JDAP introduced when it was introduced, mean and SD? -->
+
+## Results
 
@@
 
-## Attitudes towards data sharing and archiving by journal type
-
-The following plots show the responses regarding the attitudes towards data sharing and archiving by whether or not the journal has adopted a JDAP-equivalent data archiving policy by now (May 2015).
-
-```{r, echo=FALSE, message=FALSE}
-library(dplyr)
-library(ggplot2)
-source("src/multiplot.R")
-
-x <- group_by(d, PolicyBinary, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyBinary, N.total))
-x <- x[order(x$Response, decreasing=T),]
-p1 <- ggplot(data=x) + aes(Policy, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Current policy")+ylab("Percentage")
-
-x <- group_by(d, PolicyBinary, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyBinary, N.total))
-x <- x[order(x$Response, decreasing=T),]
-p2 <- ggplot(data=x) + aes(PolicyBinary, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data archiving is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Current policy")+ylab("Percentage")
-
-p1
-
-p2
-
-```
-
-The same plots side by side. Clearly, data sharing is considered more of a community standard than data archiving.
-```{r, echo=FALSE, fig.width=10}
-
-multiplot(p1, p2, cols=2)
-```
-
-## Attitudes towards data sharing and archiving by journal type and journal JDAP adoption date
+---
 
@@
 
-```{r, echo=FALSE}
-x <- group_by(d, PolicyAdoptedAtPublication, Response=Q4) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyAdoptedAtPublication, N.total))
-x <- x[order(x$Response, decreasing=T),]
-p1 <- ggplot(data=x) + aes(Policy, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data sharing is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
+```{r, fig.width=10, fig.height=5, echo=FALSE}
 
-x <- group_by(d, PolicyAdoptedAtPublication, Response=Q5) %>% dplyr::summarize(N.resp=length(StartDate)) %>% filter(!is.na(Response)) %>% dplyr::mutate(N.total=sum(N.resp), P.resp=N.resp/N.total, Policy=sprintf("%s\n(N=%d)", PolicyAdoptedAtPublication, N.total))
-x <- x[order(x$Response, decreasing=T),]
-p2 <- ggplot(data=x) + aes(Policy, P.resp*100, fill=Response, alpha=Response)+geom_bar(stat="identity")+ggtitle("'Data archiving is a community norm.'")+scale_fill_manual(values=c(rep("blue",3),"grey",rep("red",3)))+scale_alpha_manual(values=c(1,.75,.5,1,.5,.75,1))+theme_bw()+xlab("Policy at the time of publication")+ylab("Percentage")
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
 
-p1
+responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
 
-p2
+tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9')) #,'Q_12','Q_13'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
 
-```
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
 
-The same plots side by side. Clearly, data sharing is considered more of a community standard than data archiving.
-```{r, echo=FALSE, fig.width=10}
+print(p)
 
-multiplot(p1, p2, cols=2)
 ```
@@
 
-d$respQ4 <- ordered(d$Q4, levels=rev(levels(d$Q4)))
-d$respQ5 <- ordered(d$Q5, levels=rev(levels(d$Q5)))
+d$respQ1 <- ordered(d$Q_1, levels=rev(levels(d$Q_1)))
+d$respQ2 <- ordered(d$Q_2, levels=rev(levels(d$Q_2)))
 
-m4 <- polr(respQ4 ~ 1 + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
+m4 <- polr(respQ1 ~ 1 + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
 # summary(m4)
-m4.justchange <- polr(respQ4 ~ 1 + cAfterPolicyChange, data=d , Hess=TRUE)
-m4.nochange <- polr(respQ4 ~ 1 + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
+m4.justchange <- polr(respQ1 ~ 1 + cAfterPolicyChange, data=d , Hess=TRUE)
+m4.nochange <- polr(respQ1 ~ 1 + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
 suppressMessages( ci4 <- confint(m4) )
@@
 
-m5 <- polr(respQ5 ~ 1  + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
-m5.justchange <- polr(Q5 ~ 1 + cAfterPolicyChange , data=d, Hess=TRUE)
-m5.nochange <- polr(Q5 ~ 1 + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
+m5 <- polr(respQ2 ~ 1  + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
+m5.justchange <- polr(respQ2 ~ 1 + cAfterPolicyChange , data=d, Hess=TRUE)
+m5.nochange <- polr(respQ2 ~ 1 + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
 # summary(m5)
@@
 
+<!-- http://kbroman.org/knitr_knutshell/pages/figs_tables.html -->
 ```{r, message=FALSE, eval=TRUE, echo=FALSE}
-options(digits=2)
-table4
+kable(table4, digits=2)
 ```
@@
 options(digits=2)
-table5
+kable(table5, digits=2)
 ```
+
+# Appendix
+
+## Appendix A: Questionnaire Structure
+<!-- TODO: Add response options below. -->
+
+How strongly do you disagree/agree with the following statements? (Regarding the next two questions.)
+
+<!-- Field: Q4 -->
+1.
+It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
+Include data sharing that occurs by any mechanism (e.g.
+emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
+
+<!-- Field: Q5 -->
+2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
+
+<!-- Field: Q7 -->
+3. Do any of your published research papers have publicly archived datasets?
+
+<!-- Field: Q9 -->
+4.
+To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups?
+Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
+  a.  I formed new collaborations <!-- Field: Q9_1 -->
+	b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 -->
+	c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 -->
+	d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 -->
+	e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 -->
+	f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 -->
+	g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 -->
+	h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 -->
+	i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 -->
+	j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 -->
+	k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 -->
+	l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 -->
+	m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 -->
+	n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 -->
+	o.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 -->
+	p.  Other (please specify) <!-- Field: Q9_16 / Q9_16_TEXT -->
+
+<!-- Field: Q11-->
+5.
+To your knowledge, what are the policies of these stakeholders as they apply to online public archiving of the datasets associated with your (month) (year) publication in (journal)?
+Choose all that apply
+	a.  The journal  <!-- Field: Q11_1 -->
+	b.  Your funder(s)  <!-- Field: Q11_2 -->
+	c.  Your employer or institution  <!-- Field: Q11_3 -->
+
+<!-- Field: Q12 -->
+6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
+	a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
+	b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
+	c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
+	d.  I don't know   <!-- Field: Q12_4 -->
+	e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
+	f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
+
+<!-- Field: Q13 -->
+7. IF ALL or SOME datasets associated with this paper are publicly available, where are the datasets hosted?
+	a.  Journal supplementary information   <!-- Field: Q13_1 -->
+	b.  A repository for data or research output   <!-- Field: Q13_2 -->
+	c.  A personal or lab website   <!-- Field: Q13_3 -->
+	d.  The entire dataset is in the body of the paper   <!-- Field: Q13_4 -->
+	e.  Other (please specify)   <!-- Field: Q13_5/Q13_5_TEXT -->
+	f.  Not applicable   <!-- Field: Q13_6 -->
+
+<!-- Field: Q14 -->
+8. If NONE or only SOME of the datasets are publicly available, which of the following reflect your experience for the dataset(s) not publicly available, for this paper? Choose all that apply.
+	a.  The dataset has been submitted to a repository and is currently under embargo  <!-- Field: Q14_1 -->
+	b.  We plan to publicly archive the dataset in the future  <!-- Field: Q14_2 -->
+	c.  We plan to share the dataset upon request  <!-- Field: Q14_3 -->
+	d.  We hadn't considered publicly archiving the dataset  <!-- Field: Q14_4 -->
+	e.  We considered publicly archiving data and decided not to  <!-- Field: Q14_5 -->
+	f.  We wanted to publicly archive the data but were not able to, due to resource limitations  <!-- Field: Q14_6 -->
+	g.  We wanted to publicly archive the data but were not able to, for other reasons  <!-- Field: Q14_7 -->
+	h.  Other (please specify)  <!-- Field: Q14_8/Q14_8_TEXT -->
+	i.  Not applicable  <!-- Field: Q14_9 -->
+	j.  We wanted to publicly archive the data but were not able to, due to licencing or funder restrictions  <!-- Field: Q14_10 -->
+
+The questions below refer to the Joint Data Archiving Policy, an example policy statement adopted by ... <!-- TODO -->
+
+<!-- Field: Q17 -->
+9. How strongly do you disagree/agree with this statement? I would seek alternative journals if I learned that my target journal had adopted the Joint Data Archiving Policy (above).
+
+<!-- Field: Q18 -->
+10.
+Imagine you just found a great journal to target when submitting your next manuscript.
+You read the Instruction to Authors and discover the journal adheres to the Joint Data Archiving Policy (above).
+How strongly do you disagree/agree with the following statements?
+I am worried that ...
+	a.  others might do research I am currently working on  <!-- Field: Q18_1 -->
+	b.  others might do research I am planning to do  <!-- Field: Q18_2 -->
+	c.  others might find errors in my research  <!-- Field: Q18_3  -->
+	d.  others might misinterpret my dataset or use it inappropriately  <!-- Field: Q18_4 -->
+	e.  I/we might be bothered with a lot of questions by qualified people  <!-- Field: Q18_5 -->
+	f.  I/we might be bothered with a lot of questions by unqualified people  <!-- Field: Q18_6 -->
+	g.  I/we might not be able to find the data  <!-- Field: Q18_7 -->
+	h.  it might take me/us a lot of time to find the data  <!-- Field: Q18_8 -->
+	i.  it might take me/us a lot of time to format or document the data  <!-- Field: Q18_9 -->
+	j.  it might take me/us a lot of time to submit the data  <!-- Field:  Q18_10-->
+	k.  I might lose intellectual property or commercial opportunities  <!-- Field: Q18_11 -->
+	l.  Other worries (please specify)  <!-- Field: Q18_12/Q18_12_TEXT -->
+
+<!-- Field: Q19 -->
+11.
+Same instructions as the previous question: Imagine you just found a great journal to target when submitting your next manuscript.
+You read the Instruction to Authors and discover the journal adheres to the Joint Data Archiving Policy (above).
+How strongly do you disagree/agree with the following statements?
+I am pleased because...
+	a.  others will build upon my work more easily  <!-- Field: Q19_1  -->
+	b.  I will get more citations  <!-- Field: Q19_2  -->
+	c.  I will form more collaborations  <!-- Field: Q19_3  -->
+	d.  the contribution will be valued by my promotion or tenure committee  <!-- Field: Q19_4  -->
+	c.  the contribution will be valued by my funders  <!-- Field: Q19_5  -->
+	d.  I will be able to reuse other work more easily  <!-- Field: Q19_6  -->
+	e.  I will be able to reuse other work more often  <!-- Field: Q19_7  -->
+	f.  my scientific area will progress more quickly  <!-- Field: Q19_8  -->
+	g.  my scientific area will develop better tools and/or training  <!-- Field: Q19_9  -->
+	h.  I think it is the right thing to do  <!-- Field: Q19_10  -->
+	i.  Other (please specify)  <!-- Field: Q19_11/Q19_11_TEXT  -->
+
+<!-- Field: Q21 -->
+12. How strongly do you disagree/agree with the following statements? Using datasets collected by investigators outside my research group is important in my research.
+
+<!-- Field: Q22 -->
+13. Using datasets collected by investigators outside my research group is important in my teaching or other non-research projects.
+
+<!-- Field: Q23/Q23_TEXT -->
+14. Please choose the title that most closely matches yours:
+
+<!-- Field: Q25 -->
+15. Do you have any comments on the topic, or suggestions for how to improve this questionnaire?
+
+<!-- Field: Q26 -->
+16. Thank you for completing this survey! If you would like to enter the drawing for a $20 Amazon gif... <!-- TODO -->
+
+## Appendix B: Overview of responses to all questions
+
+## Questions 1, 2, 9
+1.
+It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
+Include data sharing that occurs by any mechanism (e.g.
+emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
+2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
+tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
+
+## Questions 3
+3. Do any of your published research papers have publicly archived datasets?
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses <- c("5+ papers","2-4 papers","1 paper","None") # response categories from top to bottom
+tmp <- melt(d, measure.vars=c('Q_3'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="None", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
+
+## Questions 4
+4.
+To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups?
+Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
+  a.  I formed new collaborations <!-- Field: Q9_1 -->
+        b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 -->
+        c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 -->
+        d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 -->
+        e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 -->
+        f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 -->
+        g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 -->
+        h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 -->
+        i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 -->
+        j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 -->
+        k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 -->
+        l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 -->
+        m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 -->
+        n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 -->
+        o.  Other (please specify) <!-- Field: Q9_16 / Q9_16_TEXT -->
+        p.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 -->
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+unique( d$Q_4_17 )
+unique(as.character(d$Q_4_3))
+1:15
+responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
+
+tmp <- melt(d, measure.vars=paste0('Q_4_',c(1:15,17) ))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Never", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+
+print(p)
+
+```
+
+## Questions 5
+5.
+To your knowledge, what are the policies of these stakeholders as they apply to online public archiving of the datasets associated with your (month) (year) publication in (journal)?
+Choose all that apply
+        a.  The journal  <!-- Field: Q11_1 -->
+        b.  Your funder(s)  <!-- Field: Q11_2 -->
+        c.  Your employer or institution  <!-- Field: Q11_3 -->
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
+
+tmp <- melt(d, measure.vars=paste0('Q_5_',c(1:3) ))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+
+print(p)
+
+```
+
+<!-- TODO: Need to reformat data to analyze questions 6 (->Q12), 7 (->Q13),  -->
+
+## Questions 6
+6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
+  a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
+  b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
+  c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
+	d.  I don't know   <!-- Field: Q12_4 -->
+	e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
+	f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+
+d$Q_6_
+
+with(d, xtabs(~I(Q_6_1!="")+I(Q_6_2!="")+I(Q_6_3!="") ))
+
+unique( d$Q_8_2 )
+
+```
+
+## Questions 12, 13
+
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+tmp <- melt(d, measure.vars=c('Q_12','Q_13'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```

### 2015-05-21 data/src/pre_process_jdap_adoption_dates.R

@@ -28,5 +28,7 @@ dates$policy_start <- ""
 dates$policy_start[!is.na(dates$policy_start_str)] <- parse_date(dates$policy_start_str[!is.na(dates$policy_start_str)]) %>% as.character
 dates$policy_start
 
+dates <- rename(dates, Journal=journal)
+
 write.table(dates, file="../Journal_JDAP_Adoption_Dates.csv")
 save(dates, file="../Journal_JDAP_Adoption_Dates.rda")

### 2015-05-21 data/src/pre_process_jdap_invitations.R

@@ -13,4 +13,5 @@ unique(d$note)
 d$note <- NULL
 
 write.table(d, file="../Invitations_Timing.csv")
-save(d, file="../Invitations_Timing.rda")
+invitation_timing <- d
+save(invitation_timing, file="../Invitations_Timing.rda")

### 2015-05-21 data/src/pre_process_responses.R

@@ -43,13 +43,13 @@ assert_that(unique(d$ResponseSet) ==  "Default Response Set")
 d$ResponseSet <- NULL
 key$ResponseSet <- NULL
 
-# temporarily (TODO) delete open questions
-d$Q9_16_TEXT <- NULL
-d$Q12_6_TEXT <- NULL
-d$Q13_5_TEXT <- NULL
-d$Q14_8_TEXT <- NULL
-d$Q18_12_TEXT <- NULL
-d$Q25 <- NULL
+# # temporarily (TODO) delete open questions
+# d$Q9_16_TEXT <- NULL
+# d$Q12_6_TEXT <- NULL
+# d$Q13_5_TEXT <- NULL
+# d$Q14_8_TEXT <- NULL
+# d$Q18_12_TEXT <- NULL
+# d$Q25 <- NULL
 
 # These records look strange. Besides the journal names and year (9999), all the answers that were given are the same. Furthermore, only questions with numberical answers
 # were answered.
@@ -102,6 +102,8 @@ several_values <- num_nonempty(cur_d) > 1
 cur_d[several_values,] <- ""
 # collect all responses in one column
 d$Q11_1 <- unique_nonempty(cur_d)
+# set all empty values to NAs
+d$Q11_1[d$Q11_1 == ""] <- NA
 
 ### Recode responses to question 11_2
 cur_d <- d[,paste0("Q11_2_",1:6)]
@@ -115,6 +117,8 @@ several_values <- num_nonempty(cur_d) > 1
 cur_d[several_values,] <- ""
 # collect all responses in one column
 d$Q11_2 <- unique_nonempty(cur_d)
+# set all empty values to NAs
+d$Q11_2[d$Q11_2 == ""] <- NA
 
 ### Recode responses to question 11_3
 cur_d <- d[,paste0("Q11_3_",1:6)]
@@ -128,6 +132,8 @@ several_values <- num_nonempty(cur_d) > 1
 cur_d[several_values,] <- ""
 # collect all responses in one column
 d$Q11_3 <- unique_nonempty(cur_d)
+# set all empty values to NAs
+d$Q11_3[d$Q11_3 == ""] <- NA
 
 # 
 # ### Recode responses to question 12
@@ -142,6 +148,20 @@ d$Q11_3 <- unique_nonempty(cur_d)
 # cur_d[several_values,]
 # cur_d[several_values,] <- ""
[…]

### 2015-05-21 src/plotLikert.R

@@ -1,0 +1,73 @@
+plot_likert <- function(d, response_order, above_mid, response, var_x, var_facet=NULL, na.label="No response", 
+                        xlab="% Responses", ylab="", include.N=FALSE) 
+{
+    stopifnot(above_mid %in% response_order)
+    
+    grouping_vars <- c(var_x, var_facet)
+    names(response) <- "Response"
+
+    agg_responses <- ddply(d, c(response, grouping_vars), function(x) c(N.resp=nrow(x)))
+    agg_totals <- ddply(d, c(grouping_vars), function(x) c(N.total=nrow(x)))
+    agg <- left_join(agg_responses, agg_totals, by=c(grouping_vars))
+    agg$P.resp <- with(agg, N.resp/N.total)
+    agg$sgnP.resp <- agg$P.resp
+    
+    if (include.N) {
+      agg[,var_x] <- sprintf("%s\n(N=%s)", agg[,var_x], agg$N.total)
+    }
+    
+    agg$Response <- as.character(agg$Response)
+    if (na.label != "") {
+      agg$Response[is.na(agg$Response)] <- na.label
+    } else {
+      agg <- agg[!is.na(agg$Response),]
+    }
+    
+    neutral_levels <- unique(agg$Response) %>% .[!. %in% response_order]
+    agg$Response <- ordered(agg$Response, levels=c(response_order, neutral_levels))
+    
+    is_neutral <- with(agg, !Response %in% response_order)
+    agg_neutral <- agg[is_neutral,]
+    agg_neg <- subset(agg[!is_neutral,], Response > above_mid)
+    agg_pos <- subset(agg[!is_neutral,], Response <= above_mid)
+    agg_neg$sgnP.resp <- -agg_neg$sgnP.resp
+    
+    n_pos <- length(unique(agg_pos$Response))
+    n_neg <- length(unique(agg_neg$Response))
+    n_neutral <- length(unique(agg_neutral$Response))
+    
+    fill_type <- c(rep("blue",n_pos), rep("red",n_neg), rep("darkgrey",n_neutral))
+    names(fill_type) <- sort(unique(agg$Response))
+    
+    alpha_type <- c(seq(1,.25,length.out=n_pos), seq(.25,1,length.out=n_neg), seq(1,.25,length.out=n_neutral) )
+    names(alpha_type) <- sort(unique(agg$Response))
+    
+    agg_pos <- agg_pos[order(agg_pos$Response, decreasing=T),]
[…]

### 2015-05-24 analysis.Rmd
Added more exploratory plots, and fixed a few quirks in data pre-processing.

@@
 
+_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
+
 <!-- Field: Q5 -->
@@
 
+_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
+
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
+tmp <- melt(d, measure.vars=c('Q_1','Q_2'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
+
 <!-- Field: Q7 -->
 3. Do any of your published research papers have publicly archived datasets?
+
+  Response Options:
+  1. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
+  2. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
+  3. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
+  4. No, none of my paper-related datasets are publicly available on the internet
+  5. I've never published a paper based on a dataset collected by me or my co-authors
+  6. I'm not sure if any of my papers have publicly available datasets
+
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses <- c("5+ papers with archived data","2-4 papers with archived data","1 paper with archived data","No papers with archived data") # response categories from top to bottom
+tmp <- melt(d, measure.vars=c('Q_3'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="1 paper with archived data", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
 
@@
 Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
-  a.  I formed new collaborations <!-- Field: Q9_1 -->
-	b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 -->
-	c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 -->
-	d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 -->
-	e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 -->
-	f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 -->
-	g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 -->
-	h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 -->
-	i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 -->
-	j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 -->
-	k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 -->
-	l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 -->
-	m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 -->
-	n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 -->
-	o.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 -->
-	p.  Other (please specify) <!-- Field: Q9_16 / Q9_16_TEXT -->
+  a.  I formed new collaborations <!-- Field: Q9_1 / Q_4_1 -->
+	b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 / Q_4_2 -->
+	c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 / Q_4_3 -->
+	d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 / Q_4_4 -->
+	e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 / Q_4_5 -->
+	f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 / Q_4_6 -->
+	g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 / Q_4_7 -->
+	h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 / Q_4_8 -->
+	i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 / Q_4_9 -->
+	j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 / Q_4_10 -->
+	k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 / Q_4_11 -->
+	l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 / Q_4_12 -->
+	m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 / Q_4_13 -->
+	n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 / Q_4_14 -->
+	o.  Other (please specify) <!-- Field: Q9_16 - Q9_16_TEXT / Q_4_15 - Q_4_15_TEXT -->
+  p.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 / Q_4_16 -->
+
+  Response Options:
+  1. Many times
+  2. A few times
+  3. Once
+  4. Never
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
+tmp <- melt(d, measure.vars=paste0('Q_4_',1:16 ))
+tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
+p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+
+print(p)
+
+```
 
@@
 
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
+tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
+tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
+p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+#p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+
+print(p)
+
+```
+
 <!-- Field: Q12 -->
 6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
+
+Response options:
 	a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
@@
 	f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
+cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
+cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
+cur_d$variable <- NULL
+
+d$Q_6
+
+levels <- c("ALL datasets are publicly available online","SOME but not all of the datasets are publicly available online",
+            "NONE of the datasets are publicly available online","We did not collect any data for that publication",
+            "I don't know", "Other (please specify)")
+cur_d$value <- ordered(cur_d$value, levels=levels)
+
+x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
+p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")
+
+p + theme_bw()
+
+```
 
@@
 	f.  Not applicable   <!-- Field: Q13_6 -->
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
+cur_d <- d[,c(id_vars,paste0('Q_7_', 1:6))]
+cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
+cur_d$variable <- NULL
+
+levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website",
+            "The entire dataset is in the body of the paper", "Not applicable", "Other (please specify)")
+cur_d$value <- ordered(cur_d$value, levels=levels)
+
+x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
+p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")
+
+p + theme_bw()
+
+```
 
@@
 
+Response options:
+  i. Strongly Agree
+  ii. Agree
+  iii. Somewhat Agree
+  iv. Neutral
+  v. Somewhat Disagree
+  vi. Disagree
+  vii. Strongly Disagree
+
+```{r, fig.width=5, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
+tmp <- melt(d, measure.vars=c('Q_9'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
 <!-- Field: Q18 -->
@@
 
-## Questions 1, 2, 9
-1.
-It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
-Include data sharing that occurs by any mechanism (e.g.
-emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
-2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
-
-tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
-
-```
-
-## Questions 3
-3. Do any of your published research papers have publicly archived datasets?
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses <- c("5+ papers","2-4 papers","1 paper","None") # response categories from top to bottom
-tmp <- melt(d, measure.vars=c('Q_3'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="None", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
-
-```
-
-## Questions 4
-4.
-To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups?
-Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
-  a.  I formed new collaborations <!-- Field: Q9_1 -->
-        b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 -->
-        c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 -->
-        d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 -->
-        e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 -->
-        f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 -->
-        g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 -->
-        h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 -->
-        i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 -->
-        j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 -->
-        k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 -->
-        l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 -->
-        m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 -->
-        n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 -->
-        o.  Other (please specify) <!-- Field: Q9_16 / Q9_16_TEXT -->
-        p.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 -->
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-unique( d$Q_4_17 )
-unique(as.character(d$Q_4_3))
-1:15
-responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
-
-tmp <- melt(d, measure.vars=paste0('Q_4_',c(1:15,17) ))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Never", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
-
-print(p)
-
-```
-
 ## Questions 5
@@
 
-<!-- TODO: Need to reformat data to analyze questions 6 (->Q12), 7 (->Q13),  -->
-
 ## Questions 6
@@
 f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
+<!-- TODO: What is d$Q_6_7 ??? -->
 
-```{r, fig.width=10, fig.height=5, echo=FALSE}
+```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}
 
@@
 library(reshape2)
+library(plyr)
+library(dplyr)
+library(vcd)
 
-d$Q_6_
+cnames <- paste0('Q_6_',1:6)
+x <- d[,cnames]
+new_cnames <- apply(x, 2, function(x) unique(x[x!=""])) 
+colnames(x) <- new_cnames
+x <- x!=""
+x
 
-with(d, xtabs(~I(Q_6_1!="")+I(Q_6_2!="")+I(Q_6_3!="") ))
-
-unique( d$Q_8_2 )
+res <- apply(x, 2, function(c1) apply(x, 2, function(c2) sum(c1&c2) ))
+res[lower.tri(res)] <- NA
+diag(res) <- NA
+res
 
@@
 
-```{r, fig.width=7, fig.height=5, echo=FALSE}
+```{r, eval=FALSE, fig.width=7, fig.height=5, echo=FALSE}
 

### 2015-05-24 data/src/pre_process_responses.R

@@ -78,11 +78,11 @@ d <- assign_type_to_columns(d, questions_never_often, c(), levels_never_often, c
 
 ### Recode responses to question 7
 mapping_Q7 <- c("I'm not sure if any of my papers have publicly available datasets"="Not sure",
-                "I've never published a paper based on a dataset collected by me or my co-authors"="No papers with own data",
-                "No, none of my paper-related datasets are publicly available on the internet"="None",
-                "Yes, a dataset from <b>one paper</b> is publicly available on the internet"="1 paper",
-                "Yes, datasets from <b>2-4 papers</b> are publicly available on the internet"="2-4 papers",
-                "Yes, datasets from <b>5 or more papers</b> are publicly available on the internet"="5+ papers")
+                "I've never published a paper based on a dataset collected by me or my co-authors"="No papers based on own data",
+                "No, none of my paper-related datasets are publicly available on the internet"="No papers with archived data",
+                "Yes, a dataset from <b>one paper</b> is publicly available on the internet"="1 paper with archived data",
+                "Yes, datasets from <b>2-4 papers</b> are publicly available on the internet"="2-4 papers with archived data",
+                "Yes, datasets from <b>5 or more papers</b> are publicly available on the internet"="5+ papers with archived data")
 d <- assign_type_to_columns(d, 'Q7', mapping_Q7, mapping_Q7, c(""), factor)
 
 
@@ -162,6 +162,7 @@ d <- select(d, ResponseID, ResponseDate, PublicationDate, Journal=journal, Q_1=Q
             Q_4_=starts_with("Q9"), Q_5_=starts_with("Q11"), Q_6_=starts_with("Q12"), Q_7_=starts_with("Q13"),
             Q_8_=starts_with("Q14"), Q_9=Q17, Q_10_=starts_with("Q18"), Q_11_=starts_with("Q19"),
             Q_12=Q21, Q_13=Q22, Q_14_=starts_with("Q23"), Q_15=Q25, Q_16=Q26 )
+d <- rename(d, Q_4_15_TEXT=Q_4_16, Q_4_16=Q_4_17, Q_6_6_TEXT=Q_6_7, Q_7_5_TEXT=Q_7_6, Q_7_6=Q_7_7  )
 
 save(d, file="../JDAP_Survey_Data_Tidy.rda")
 write.csv(d, file="../JDAP_Survey_Data_Tidy.csv")

### 2015-05-24 src/plotLikert.R

@@ -63,7 +63,7 @@ plot_likert <- function(d, response_order, above_mid, response, var_x, var_facet
              scale_alpha_manual(values=alpha_type,  breaks=names(alpha_type), labels=names(alpha_type)) 
     
     plot_breaks <- seq(-100,100,10)
-    plot_labels <- c(seq(100,0,-10), seq(10,100,10))
+    plot_labels <- c(seq(100,10,-10), 0, seq(10,100,10))
     p <- p + ggplot2::xlab(ylab) + ggplot2::ylab(xlab) + scale_y_continuous(breaks=plot_breaks, labels=plot_labels)
     
     facet_formula <- sprintf("%s ~ %s", ifelse(nrow(agg_neutral), "ResponseNeutrality", "."),

### 2015-05-27 analysis.Rmd
Added plots for all relevant questions.

@@
 interactive_mode <- FALSE
+jdap_adoption_dates <- dates
 
@@
 
+<!--
 _(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
-
-<!-- Field: Q5 -->
-2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
-
-_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
+-->
 
@@
 
-tmp <- melt(d, measure.vars=c('Q_1','Q_2'))
+tmp <- melt(d, measure.vars=c('Q_1'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
+
+<!-- Field: Q5 -->
+2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
+
+<!--
+_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
+-->
+
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
+tmp <- melt(d, measure.vars=c('Q_2'))
 tmp$variable <- gsub("Q_", "Question ", tmp$variable)
@@
 3. Do any of your published research papers have publicly archived datasets?
-
-  Response Options:
-  1. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
-  2. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
-  3. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
-  4. No, none of my paper-related datasets are publicly available on the internet
-  5. I've never published a paper based on a dataset collected by me or my co-authors
-  6. I'm not sure if any of my papers have publicly available datasets
+  a. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
+  b. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
+  c. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
+  d. No, none of my paper-related datasets are publicly available on the internet
+  e. I've never published a paper based on a dataset collected by me or my co-authors
+  f. I'm not sure if any of my papers have publicly available datasets
 
@@
 
+<!--
   Response Options:
@@
   4. Never
+-->
 
@@
 
+facet_labels <- c('Journal', 'Funder(s)', 'Employer or institution')
 responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
 tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
-tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+tmp$variable <- facet_labels[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
+tmp$variable <- factor(tmp$variable, levels=facet_labels)
+
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
 #p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
@@
 
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
+```{r, fig.width=10, fig.height=5, echo=FALSE, eval=FALSE}
+library(dplyr)
 library(ggplot2)
@@
 cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
-cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
+cur_d <- melt(cur_d, id.vars=id_vars) %>% %>% subset(value != "")
 cur_d$variable <- NULL
-
-d$Q_6
 
@@
 
-x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
-p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")
+tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
 
-p + theme_bw()
+p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value, alpha=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
+p + theme_bw() + scale_fill_manual(values=c(rep("blue",2), rep("red",2), "grey", "green" )) + scale_alpha_manual(values=c(1,.5, 1,.5, 1,1))
 
@@
 levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website",
-            "The entire dataset is in the body of the paper", "Not applicable", "Other (please specify)")
+            "Not applicable", "The entire dataset is in the body of the paper", "Other (please specify)")
 cur_d$value <- ordered(cur_d$value, levels=levels)
 
-x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
-p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")
+tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
 
+p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
 p + theme_bw()
@@
 
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
+cur_d <- d[,c(id_vars,paste0('Q_8_', 1:10))]
+cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
+cur_d$variable <- NULL
+
+levels <- c("The dataset has been submitted to a repository and is currently under embargo",
+            "We plan to publicly archive the dataset in the future",
+            "We plan to share the dataset upon request",
+            "We hadn't considered publicly archiving the dataset",
+            "We considered publicly archiving data and decided not to",
+            "We wanted to publicly archive the data but were not able to, due to resource limitations",
+            "We wanted to publicly archive the data but were not able to, for other reasons",           
+            "We wanted to publicly archive the data but were not able to, due to licencing or funder restrictions",
+            "Not applicable", "Other (please specify)")
+cur_d$value <- ordered(cur_d$value, levels=levels)
+
+tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
+
+p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
+p + theme_bw()
+
+```
+
 The questions below refer to the Joint Data Archiving Policy, an example policy statement adopted by ... <!-- TODO -->
@@
 
+<!--
 Response options:
@@
   vii. Strongly Disagree
+-->
 
@@
 ```
+
 <!-- Field: Q18 -->
@@
 
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
+tmp <- melt(d, measure.vars=paste0('Q_10_',1:11 ))
+tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("10_", "", .) %>% as.integer]
+p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+
+print(p)
+
+```
+
 <!-- Field: Q19 -->
@@
 
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
+tmp <- melt(d, measure.vars=paste0('Q_11_',1:10 ))
+
+tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("11_", "", .) %>% as.integer]
+p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+
+print(p)
+
+```
+
+How strongly do you disagree/agree with the following statements?
+
 <!-- Field: Q21 -->
-12. How strongly do you disagree/agree with the following statements? Using datasets collected by investigators outside my research group is important in my research.
+12.  Using datasets collected by investigators outside my research group is important in my research.
+
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
+tmp <- melt(d, measure.vars=c('Q_12'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
 
@@
 13. Using datasets collected by investigators outside my research group is important in my teaching or other non-research projects.
+
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
+tmp <- melt(d, measure.vars=c('Q_13'))
+tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+
+print(p)
+
+```
 
@@
 
-## Appendix B: Overview of responses to all questions
+## Appendix B: JDAP Adoption Dates
 
-## Questions 5
-5.
-To your knowledge, what are the policies of these stakeholders as they apply to online public archiving of the datasets associated with your (month) (year) publication in (journal)?
-Choose all that apply
-        a.  The journal  <!-- Field: Q11_1 -->
-        b.  Your funder(s)  <!-- Field: Q11_2 -->
-        c.  Your employer or institution  <!-- Field: Q11_3 -->
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+library(knitr)
 
-```{r, fig.width=10, fig.height=5, echo=FALSE}
+journals_in_dataset <- unique(d$Journal)
+relevant_jdap_adoption_dates <- subset(jdap_adoption_dates, Journal %in% journals_in_dataset)
 
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
-
-tmp <- melt(d, measure.vars=paste0('Q_5_',c(1:3) ))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
-
-print(p)
+table <- subset(relevant_jdap_adoption_dates, policy == "Required")[,c('JournalName','policy_start_str')]
+colnames(table) <- c('Journal', 'Adoption Date of JDAP or Equivalent Policy')
+rownames(table) <- NULL
+kable(table)
 
 ```
-
-## Questions 6
-6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
-a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
-  b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
-  c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
-  d.  I don't know   <!-- Field: Q12_4 -->
-e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
-f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
-<!-- TODO: What is d$Q_6_7 ??? -->
-
-```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-library(plyr)
-library(dplyr)
-library(vcd)
-
-cnames <- paste0('Q_6_',1:6)
-x <- d[,cnames]
-new_cnames <- apply(x, 2, function(x) unique(x[x!=""])) 
-colnames(x) <- new_cnames
-x <- x!=""
-x
-
-res <- apply(x, 2, function(c1) apply(x, 2, function(c2) sum(c1&c2) ))
-res[lower.tri(res)] <- NA
-diag(res) <- NA
-res
-
-```
-
-## Questions 12, 13
-
-```{r, eval=FALSE, fig.width=7, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-tmp <- melt(d, measure.vars=c('Q_12','Q_13'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
-
-```

### 2015-05-27 data/src/pre_process_jdap_adoption_dates.R

@@ -1,8 +1,8 @@
 dates <- read.csv("../info/Journal data archiving policies (as relevant to JDAP).csv", as.is=T)
 
 # extract only the relevant parts
-dates <- subset(dates, Abbreviation != "")[,c('Abbreviation','Policy.short','Date.policy.took.effect')]
-colnames(dates) <- c('journal', 'policy', 'policy_start')
+dates <- subset(dates, Abbreviation != "")[,c('Journal','Abbreviation','Policy.short','Date.policy.took.effect')]
+colnames(dates) <- c('JournalName','Journal', 'policy', 'policy_start')
 
 # reduce the number of policy categories
 dates[dates$policy=="Unclear", 'policy_start'] <- '-'
@@ -27,8 +27,6 @@ dates$policy_start_str <- dates$policy_start
 dates$policy_start <- ""
 dates$policy_start[!is.na(dates$policy_start_str)] <- parse_date(dates$policy_start_str[!is.na(dates$policy_start_str)]) %>% as.character
 dates$policy_start
-
-dates <- rename(dates, Journal=journal)
 
 write.table(dates, file="../Journal_JDAP_Adoption_Dates.csv")
 save(dates, file="../Journal_JDAP_Adoption_Dates.rda")

### 2015-05-27 data/src/pre_process_responses.R

@@ -63,7 +63,7 @@ sort(unique(d$journal))
 
 
 ### Recode responses to all questions using the agree-disagree scale
-questions_agree_disagree <- c('Q4','Q5','Q17',sprintf("Q18_%d",1:12),sprintf("Q19_%d",1:10), 'Q21', 'Q22')
+questions_agree_disagree <- c('Q4','Q5','Q17',sprintf("Q18_%d",1:12),sprintf("Q19_%d",1:11), 'Q21', 'Q22')
 mapping_agree_disagree <- c("Strongly disagree"="Strongly Disagree","Somewhat disagree"="Somewhat Disagree","Somewhat agree"="Somewhat Agree","Strongly agree"="Strongly Agree")
 levels_agree_disagree <- rev(c("Strongly Disagree","Disagree","Somewhat Disagree","Neutral","Somewhat Agree","Agree","Strongly Agree"))
 d <- assign_type_to_columns(d, questions_agree_disagree, mapping_agree_disagree, levels_agree_disagree, c("","."))  # TODO: What's with the dots in responses to questions 18-19
@@ -162,7 +162,8 @@ d <- select(d, ResponseID, ResponseDate, PublicationDate, Journal=journal, Q_1=Q
             Q_4_=starts_with("Q9"), Q_5_=starts_with("Q11"), Q_6_=starts_with("Q12"), Q_7_=starts_with("Q13"),
             Q_8_=starts_with("Q14"), Q_9=Q17, Q_10_=starts_with("Q18"), Q_11_=starts_with("Q19"),
             Q_12=Q21, Q_13=Q22, Q_14_=starts_with("Q23"), Q_15=Q25, Q_16=Q26 )
-d <- rename(d, Q_4_15_TEXT=Q_4_16, Q_4_16=Q_4_17, Q_6_6_TEXT=Q_6_7, Q_7_5_TEXT=Q_7_6, Q_7_6=Q_7_7  )
+d <- rename(d, Q_4_15_TEXT=Q_4_16, Q_4_16=Q_4_17, Q_6_6_TEXT=Q_6_7, Q_7_5_TEXT=Q_7_6, Q_7_6=Q_7_7, Q_8_8_TEXT=Q_8_9, 
+            Q_8_9=Q_8_10, Q_8_10=Q_8_11, Q_10_12_TEXT=Q_10_13, Q_11_11_TEXT=Q_11_12 )
 
[…]

### 2015-06-08 data/src/pre_process_jdap_adoption_dates.R
Workaround for a bug in the parsedate package which resulted in the time difference between JDAP introduction and publication being computed incorrectly (sometimes having the wrong sign).

@@ -1,3 +1,8 @@
+library(dplyr)
+library(zoo)
+source("../../src/aux_functions.R")
+
+
 dates <- read.csv("../info/Journal data archiving policies (as relevant to JDAP).csv", as.is=T)
 
 # extract only the relevant parts
@@ -12,11 +17,6 @@ dates[dates$policy=="SomeDataTypesRequired", 'policy'] <- 'Encouraged'
 dates[dates$policy_start=='-','policy_start'] <- NA
 #date_boundary <- grepl("[<>]", dates$policy_start)
 #date_range <- grepl("-", dates$policy_start)
-
-
-library(dplyr)
-library(parsedate)
-library(zoo)
 
 # parse_date() can deal with extra characters and the sort of ranges defined here. It uses the second date in the range.
 # parse_date("< 18.08.2010")

### 2015-06-08 data/src/pre_process_jdap_invitations.R

@@ -1,4 +1,7 @@
-library(parsedate)
+library(zoo)
+library(plyr)
+library(dplyr)
+source("../../src/aux_functions.R")
 
 d <- read.csv("../raw_data/Invitations_Timing.csv", as.is=T)
 

### 2015-06-08 data/src/pre_process_responses.R

@@ -3,15 +3,7 @@ library(plyr)
 library(dplyr)
 library(tidyr)
 library(assertthat)
-
-vmap <- function (vec, from, to) {
-  newVec <- vec
-  for (i in 1:length(from)) {
-    newVec[vec == from[i]] <- to[i]
-  }
-  return(newVec)
-}
-nmap <- function (vec, fromto, cast = I) cast(vmap(vec, names(fromto), fromto))
+source("../../src/aux_functions.R")
 
 assign_type_to_columns <- function(d, questions, mapping, levels, to_NA, type=ordered) {
   expected_levels  <- c(levels, to_NA)
@@ -149,7 +141,6 @@ d$Q11_3[d$Q11_3 == ""] <- NA
 # cur_d[several_values,] <- ""
 # d$Q12 <- unique_nonempty(cur_d)
 
-library(parsedate)
 library(plyr)
 library(dplyr)
 library(zoo)

### 2015-06-08 src/_netstacked_ggplot.R

@@ -1,0 +1,64 @@
+# Source code from: http://statisfactions.com/2012/improved-net-stacked-distribution-graphs-via-ggplot2-trickery/
+
+net_stacked <- function(x) {
+  
+  ## x: a data.frame or list, where each column is a ordered factor with the same levels
+  ## lower levels are presumed to be "negative" responses; middle value presumed to be neutral
+  ## returns a ggplot2 object of a net stacked distribution plot
+  
+  ## Test that all elements of x have the same levels, are ordered, etc.
+  all_levels <- levels(x[[1]])
+  n <- length(all_levels)
+  levelscheck <- all(sapply(x, function(y)
+    all(c(is.ordered(y), levels(y) == all_levels))
+  ))
+  if(!levelscheck)
+    stop("All levels of x must be ordered factors with the same levels")
+  
+  ## Reverse order of columns (to make ggplot2 output look right after coord_flip)
+  x <- x[length(x):1]
+  
+  ## Identify middle and "negative" levels
+  if(n %% 2 == 1)
+    neutral <- all_levels[ceiling(n/2)]
+  else
+    neutral <- NULL
+  
+  negatives <- all_levels[1:floor(n/2)]
+  positives <- setdiff(all_levels, c(negatives, neutral))
+  
+  ## remove neutral, summarize as proportion
+  listall <- lapply(names(x), function(y) {
+    column <- (na.omit(x[[y]]))
+    out <- data.frame(Question = y, prop.table(table(column)))
+    names(out) <- c("Question", "Response", "Freq")
+    
+    if(!is.null(neutral))
+      out <- out[out$Response != neutral,]
+    
+    out
+  })
+  
+  dfall <- do.call(rbind, listall)
+  
+  ## split by positive/negative
+  pos <- dfall[dfall$Response %in% positives,]
+  neg <- dfall[dfall$Response %in% negatives,]
+  
+  ## Negate the frequencies of negative responses, reverse order
+  neg$Freq <- -neg$Freq
+  neg$Response <- ordered(neg$Response, levels = rev(levels(neg$Response)))
+  
+  stackedchart <- ggplot() +
+    aes(Question, Freq, fill = Response, order = Response) + 
+    geom_bar(data = neg, stat = "identity") +
+    geom_bar(data = pos, stat = "identity") + geom_hline(yintercept=0) +
+    scale_y_continuous(name = "",
+                       labels = paste0(seq(-100, 100, 20), "%"),
[…]

### 2015-06-08 src/_plotLikert2.R

@@ -1,0 +1,79 @@
+
+responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # from top to bottom
+
+library(reshape2)
+x <- melt(d, measure.vars=c('Q4','Q5','Q17','Q21','Q22'))
+
+p <- plot_likert(x, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+  
+p
+
+
+response_order <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # from top to botoom
+above_mid <- "Somewhat Agree"
+na.label = "No response"
+xlab <- "% Responses"
+ylab <- "JDAP Policy"
+
+d$Response <- d[,]
+d$XVar <- d[,]
+
+plot_likert <- function(d, response='Q4', grouping_vars=, )
+  
+plot_likert <- function(d, response, grouping_vars, ) {
+  d$Response <- d[,]
+  d$XVar <- d[,]
+  
+    agg_responses <- ddply(d, .(Response, XVar), summarize, N.resp=length(Response))
+    agg_totals <- ddply(d, .(XVar), summarize, N.total=length(Response))
+    agg <- left_join(agg_responses, agg_totals, by="XVar")
+    agg$P.resp <- with(agg, N.resp/N.total)
+    
+    agg$Response <- as.character(agg$Response)
+    if (na.label != "") {
+      agg$Response[is.na(agg$Response)] <- na.label
+    } else {
+      agg <- agg[!is.na(agg$Response),]
+    }
+    
+    neutral_levels <- unique(agg$Response) %>% .[!. %in% response_order]
+    agg$Response <- ordered(agg$Response, levels=c(response_order, neutral_levels))
+    
+    is_neutral <- with(agg, !Response %in% response_order)
+    agg_neutral <- agg[is_neutral,]
+    agg_neg <- subset(agg[!is_neutral,], Response > above_mid)
+    agg_pos <- subset(agg[!is_neutral,], Response <= above_mid)
+    
+    n_pos <- length(unique(agg_pos$Response))
+    n_neg <- length(unique(agg_neg$Response))
+    n_neutral <- length(unique(agg_neutral$Response))
+    
[…]

### 2015-06-08 analysis.Rmd
Analysis update following the parsedate workaround.

@@
 
-library(parsedate)
 library(plyr)
@@
 library(assertthat)
+source("./src/aux_functions.R")
 
@@
 
+d$PolicyStartDate <- parse_date(d$policy_start)
+
 # determine time since JDAP introduction in the journal where the article was published
-d$DaysPolicyToPublication <- difftime(d$PublicationDate, parse_date(d$policy_start), units="days")
-d$DaysPolicyToResponse <- difftime(d$ResponseDate, parse_date(d$policy_start), units="days")
+d$DaysPolicyToPublication <- difftime(d$PublicationDate, d$PolicyStartDate, units="days")
+d$DaysPolicyToResponse <- difftime(d$ResponseDate, d$PolicyStartDate, units="days")
 
-d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
-d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
-d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
-d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
-# d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
+levels_TimeClass <- c("No JDAP","Before JDAP","After JDAP") 
+levels_TimeClassByYear <- c("No\nJDAP","Before\nJDAP","1st Year\nAfter\nJDAP", "1+ Year\nAfter\nJDAP") 
+d$PolicyAdoptedAtPublication <- ifelse(is.na(d$DaysPolicyToPublication), levels_TimeClass[1], ifelse(d$DaysPolicyToPublication<0, levels_TimeClass[2], levels_TimeClass[3]))
+d$PolicyAdoptedAtResponse <- ifelse(is.na(d$DaysPolicyToResponse), levels_TimeClass[1], ifelse(d$DaysPolicyToResponse<0, levels_TimeClass[2], levels_TimeClass[3]))
+
+d$PolicyAdoptedAtPublicationByYears <- ifelse(is.na(d$DaysPolicyToPublication), levels_TimeClassByYear[1], ifelse(d$DaysPolicyToPublication<0, levels_TimeClassByYear[2], ifelse(d$DaysPolicyToPublication<365, levels_TimeClassByYear[3], levels_TimeClassByYear[4] )))
+d$PolicyAdoptedAtResponseByYears <- ifelse(is.na(d$DaysPolicyToResponse), levels_TimeClassByYear[1], ifelse(d$DaysPolicyToResponse<0, levels_TimeClassByYear[2], ifelse(d$DaysPolicyToResponse<365, levels_TimeClassByYear[3], levels_TimeClassByYear[4] )))
 
@@
 
-d$label_PolicyAdoptedAtPublication <- gsub(" ", "\n", d$PolicyAdoptedAtPublication)
+# unique(d$PolicyAdoptedAtPublication)
+# d$label_PolicyAdoptedAtPublication <- ordered(d$PolicyAdoptedAtPublication, levels=c("No\nJDAP", "Before\nJDAP", "After\nJDAP"))
+d$label_PolicyAdoptedAtPublication <- ordered(gsub(" ","\n",d$PolicyAdoptedAtPublication), levels=gsub(" ","\n",levels_TimeClass))
+
+# Note: These are very surprising responses
+# d_unexpected_responses <- subset(d, label_PolicyAdoptedAtPublication==levels_TimeClassByYear[4]) %>% subset(Q_9 == "Strongly Agree")
+#d_unexpected_responses$Q_9 %>% summary
+#summary(as.factor(d_unexpected_responses$Journal))
+#d_unexpected_responses %>% head(2)
+
+#head(d_unexpected_responses,3)
+#subset(d_unexpected_responses, )
 
@@
 responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
-
+question_labels <- c('Q_1'='"Data sharing is a community norm."\n(Question 1)',
+                     'Q_2'='"Data archiving is a community norm."\n(Question 2)',
+                     'Q_9'='"I would seek alternative journals\nif JDAP was introduced."\n(Question 9)')
 tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9')) #,'Q_12','Q_13'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
+tmp$variable <- as.character(tmp$variable)
+tmp$variable <- ordered(nmap(tmp$variable, question_labels), levels=question_labels)
+#tmp$variable <- gsub("Q_", "Question ", tmp$variable) # gsub("Q_", "Question ", tmp$variable)
 
 p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
 print(p)

### 2018-03-20 manuscript.Rmd
get all the analysis into the main file

--- 2015-06-08 analysis.Rmd
@@
 title: "Data Archiving Attitudes"
-author: "Heather Piwowar, Pavel Logacev, Todd J. Vision"
-date: "May 17, 2015"
+author: "Heather A. Piwowar, Todd J. Vision"
+date: "March 20, 2018"
+csl: f1000-research.csl
 output:
@@
     fig_caption: yes
-bibliography: bibliography.bib
-<!-- csl: apa.csl -->
+bibliography: input_references.bib
 ---
 
-```{r setup, echo=FALSE, include=TRUE}
-suppressPackageStartupMessages({
-  require(plyr)
-  require(dplyr)
-  require(knitr)
-  require(RColorBrewer)
-  require(knitr)
-  #require(kfigr)
-  opts_chunk$set(message=FALSE, warning=FALSE)
-})
-#knit_hooks$set(plot = function(x, options) {
-#   paste('<figure><img src="',
-#         opts_knit$get('base.url'), paste(x, collapse = '.'),
-#         '"><figcaption>', options$fig.cap, '</figcaption></figure>',
-#         sep = '')
-#})
-
-#knit_hooks$set(plot = function(x, options) {
-#   paste0('<figure><img src="',opts_knit$get('base.url'), paste(x, collapse = '.'),'">',
-#          '<figcaption>', options$fig.cap, '</figcaption></figure>')
-#})
-
+```{r, cache=FALSE, message=FALSE, echo=FALSE, warning=FALSE}
+require(knitcitations)
+options("citation_format" = "pandoc")
+cleanbib()
+bib=read.bibtex("input_references.bib")
 ```
 
-This is where the abstract goes.
+There have been previous studies of data sharing patterns, but we are not aware of any prior research that examined attitudes and experiences of authors before and after policy implementation.
+
+The promise of data sharing and the role of data sharing policies
+
+Sharing data is a tenet of science, yet commonplace in only a few subdisciplines.
+Publicly available datasets have many potential reuses.
+Unfortunately, these advantages only indirectly benefit the stakeholders who bear most of the costs for sharing their datasets: the primary data-producing investigators.
+As a result, authors often actively or passively withhold their research datasets from other investigators
+`r citep(c(bib["blumenthal1997withhol"], bib["ochsner2008much-ro"], bib["savage2009empiric"]))`.
+
+Recognizing that a data sharing culture is unlikely to be achieved without policy guidance, funders and journals have begun to request and require that investigators share their research datasets with other researchers `r citep(c(bib["brown2003the-cha"], bib["enriquez2010data-ci"]))`.
+Funders are motivated by the promise of resource efficiency and rapid progress.
+The motivation for journals to act as an advocate and gatekeeper for data sharing is less straightforward.
+Journals seek to publish “well-written, properly formatted research that meets community standards” and in so doing have assumed monitoring tasks to “remind researchers of community expectations and enforce some behaviors seen as advantageous to the progress of science” `r citep(bib["mccain1995mandati"])`.
+This role has been encouraged by many letters, white-papers, and editorials in high-profile journals.
+
+Policies should only be adopted if their benefits outweigh their costs, across the wide array of stakeholders `r citep(bib["foster2007share-a"])`.
+Requiring data sharing can raise controversy `r citep(c(bib["campbell2002data-wi"], bib["king1995a-revis"]))`, increase short-term system costs `r citep(bib["beagrie2009busines"])`, and possibly motivate authors to seek alternative locations for publishing.
+The goal of this study is quantify the some of the short-term benefits and costs of policy adoption in the practices, attitudes, and opinions of data producing authors.
+
+#### Dimensions of impact
+
+A journal policy that requires authors to share the datasets that support their results as a condition of publication may impact the practices, attitudes, and opinions of data producing authors in many ways.
+Here, we emphasize the short-term impacts on authors who publish in the policy-adopting journals.
+
+The most direct impact is likely a change in frequency of data sharing, and a shift to data archiving locations specified in the policy.
+Early studies suggest that authors who publish in journals with data sharing policies are more likely to share their data than authors who publish similar studies in similar journals `r citep(c(bib["piwowar2008a-revie"], bib["Piwowar_2011"]))`, but these investigations were correlative and did not attempt to directly measure the impact of journal policies over time.
+Previous work emphasizes the importance of sharing data through best-practice archiving methods and locations.
+Authors who share data upon request often discriminate against use and users `r citep(c(bib["campbell2008what-ar"], bib["reidpath2001data-sh"]))`.
+The permanence of data sharing mechanisms is also a concern; email and lab-website based sharing choices have been shown to be impermanent solutions at best `r citep(c(bib["wren2008url-dec"], bib["wren2006e-mail"]))`.
+
+An question of particular interest is whether the adoption of data sharing mandates leads authors to perceive that it has become a community norm to share data in their field.
+If so, this shift in attitude may in and of itself it may lead to more data sharing: previous research has found that scientists “look beyond their individual interests to social cues from reference groups when deciding whether to withhold or share information requested by others” `r citep(bib["haas2009to-shar"])`.
+This is consistent with findings that have found a correlation between information sharing and perceived community norm of openness and sharing `r citep(c(bib["haeusslerinforma"], bib["kuo2008a-study"]))`, as well as evidence that a scientist’s sharing decisions are influenced by expectation of reciprocity `r citep(bib["gouldnertheoret"])` and that their prior experiences with sharing predicts future sharing decisions `r citep(bib["campbell2002data-sh"])`.
+
+A few previous studies have estimated the impact of sharing data on the experiences of authors `r citep(c(bib["blumenthal2006data-wi"], bib["gleditsch2003posting"], bib["piwowar2007sharing"], bib["ventura2005mandato"]))`, but there is much to be learned in this area to ground expectations, accurately estimate costs and benefits, and learn about ways policies could be improved to enhance positive experiences and avoid negative ones.
+
+Journal publishers and editors may be particularly interested in whether authors start to view data sharing mandates more positively after they have experience with them.
+In particular, knowing whether experience with a data sharing policy makes authors more or less likely include the existence of data sharing policies in their decisions about future publishing venues `r citep(bib["bjork2009a-metho"])` would be of great interest to journals considering the adoption of such policies.
+
+Evaluating the impact of a journal data sharing policy on dataset reuse is also critical.
+Such an evaluation would require a longer timeframe than that of the current proposal and may be felt most strongly in a different author population; we hope to pursue this area in future work.
+
+Upcoming policy change is a useful opportunity for policy evaluation
+
+Several journals plan to adopt the Joint Data Archiving Policy in early 2011, as described at http://datadryad.org/jdap.  Participating journals include:
+
+- American Naturalist
+- Evolution
+- Evolutionary Applications
+- Heredity
+- Journal of Evolutionary Biology
+- Molecular Biology and Evolution.
+- Molecular Ecology
+
+This is a great opportunity to study the effect of journal data sharing mandates on the attitudes, behaviour, experiences of authors to help inform future policy decisions.
+
+The JDAP policy requires data sharing in a public archive.
+Early evidence suggests stronger policies are associated with a higher frequency of data sharing `r citep(c(bib["piwowar2008a-revie"], bib["Piwowar_2011"]))`.
+Since JDAP requires data sharing as a condition of publication, studying this policy adoption is an opportunity to possibly measure the maximum likely effect.
+Also, since the adopting journals include almost all of the high-impact journals in the field of Evolutionary Science (as per the 2009 ISI JCR), it is likely that even authors who dislike the policies will continue publishing in these journals and possibly participate in our measurement of opinions.
+
+We note that authors in evolution and ecology have been surveyed several other times to assess data sharing attitudes and experiences, but these questionnaires have not been correlated to journal policy adoption `r citep(bib["scherle2008buildin"])`.
+
+Because measurements of actual dataset archiving behavior can be accurately measured with a retrospective analysis of research artifacts, our proposed survey does not emphasize data archiving behaviour.
+Instead, the questionnaire will focus on information that is difficult or impossible to collect without a timely survey of data-producing investigators.
+
+Rigorous research is needed into the impact of journal policies
+
+Although some data sharing mandates appear to have achieved almost universal sharing `r citep(bib["noor2006data-sh"])`, this is not always the case `r citep(bib["ochsner2008much-ro"])`.
+Several surveys have asked about author’s perceived obstacle to sharing data `r citep(c(bib["hedstrom2008researc"], bib["scherle2008buildin"]))`, but changes in these attitudes have not been monitored across a policy change.
+To our knowledge, the impact of data sharing mandates have only been subject to one evaluation:  the editors of Physiological Genomics briefly surveyed their authors and reviewers two years after instituting a policy that required public archiving of gene expression microarray data `r citep(bib["ventura2005mandato"])`, though unfortunately no baseline measurements are available about attitudes before the policy.
+Interestingly, a recent large-scale evaluation `r citep(bib["Piwowar_2011"])` into the prevalence of microarray data sharing found this same journal to have the highest rate of public archiving.
+
+Robust studies of journal policies are infrequent, even in areas beyond data sharing.
+A systematic review in 2006 examined the effect of journal adoption of CONSORT requirements for standard reporting of clinical trials `r citep(bib["plint2006does-th"])`.
+It found that most publications about the journal policies were editorials or letters (699 of 1129 articles about the CONSORT policy).
+Of the studies, many were non-comparative (231 of 248), only a very few (12) were considered to be comparative studies with appropriate outcomes and sufficient detail, and only one study had predefined control group.
+The authors conclude that, “Studies evaluating the effectiveness of the CONSORT checklist are methodologically weak” `r citep(bib["plint2006does-th"])`.
+This suggests that high quality evaluations are indeed rare and thus potentially valuable contributions.
+
+Research questions
+
+The specific research questions for this study include:
+
+- How do authors’ attitudes, experiences, and practices around public data archiving change when the journals they publish in adopt mandatory data archiving policies?
+- Are changes specific to the journals that implement the policies, or do they extend to other journals in the same subfield?
+
+## Primary analysis
+The primary analysis will be a seven-point Likert scale asking how strongly authors believe:  “It is the community norm in my field to publicly share datasets upon study publication by archiving all datasets online, for use by anyone for any purpose.”
+
+About twelve other survey questions will allow secondary and exploratory analyses.
+
+## Methods
+Participants will be recruited from corresponding authors who publish in specific journals between November 2010 and November 2013.
+Specifically, email addresses will be collected for papers published the previous month (or 3 previous months, for the initial month of recruitment) in each of the target journals through the ISI Web of Science.
+No other identifying information (author names, article title, etc) will be retained.
+
+Recruitment email lists will be compared across months, and emails only sent to those who have not previously received a recruitment email to reduce survey fatigue and ill-will.
+
+The email invitation will include a URL where subjects can learn more about the study and then read a fact sheet, consent, and participate if they choose.
+This email will also contain an “opt out” option, which will remove their address from the reminder list.
+Those who have not “opted out” will be contacted by email again, a week later, politely asking them to take the survey if they haven’t already.
+
+Individual participants can expect to spend 7-10 minutes maximum answering the online questionnaire.
+
+Before the initial round of invitations is sent, I will inform journal editors of this ongoing survey and provide contact information in case they have questions, suggestions, or concerns.
+
+Previous studies suggest 10%-30% of authors will complete the survey `r citep(c(bib["haeusslerinforma"], bib["wren2007the-wri"]))`.
+
+Gender, ethnicity, and race are irrelevant to the study.
+Other than the requirement that participants be 18 years of age or older, age is irrelevant to the study.
+Medical history and/or conditions are irrelevant to the study.
+
+To facilitate legal consent, this study is restricted to participants who are 18 years of age or older.
+The study is intended to establish knowledge about the implications of policies on active researchers.
+No other criteria are necessary for inclusion; no criteria are grounds for exclusion.
+
+## Methods 2
+
+We expect the JDAP policies to be implemented in or about January 2011, though it will take several months to see any effect because the policies will likely be applied to newly submitted papers it will take multiple months for these papers to be published.
+This timeline is likely to vary across JDAP-adopting journals depending on the length of their publication cycle.
+
+Participants will be recruited from corresponding authors who publish in specific journals between November 2010 and November 2013.
+An invitation to the survey will be issued once a month to all corresponding authors who published in specific journals the prior month.
+The responses of authors who published in JDAP-adopting journals will be compared, over time, to a) the responses of authors who publish in in-community journals that do not adopt JDAP, and b) the responses of authors who publish in outside-community journals that do not adopt JDAP.
+
+### Data collection
+
+The instrument used to collect data is be an online questionnaire.
+The questionnaire is designed to elicit the respondent’s practices, experiences, and opinions around public archiving of research datasets by asking about their opinion of community norms, recent behaviour with respect to a recently published paper, previous experiences with data sharing, and attitudes toward hypothetical situations.
+
+The primary analysis will be a seven-point Likert scale asking how strongly authors believe:  “It is the community norm in my field to publicly share datasets upon study publication by archiving all datasets online, for use by anyone for any purpose.”  About twelve other survey questions will allow secondary and exploratory analyses.
+
+Aggregate answers will be compared over time, to understand if answers of authors in journals that adopt JDAP begin to differ from those of authors in comparable within-community and outside-community control journals.
+
+The online survey will be administered through ViewsFlash® 6 by Cogix, hosted by Duke University.  There will be no way link the responses with the identities of participants.
+
+### Limitations
+
+The limitations of this study design include:
+
+- There is limited time before JDAP is implemented (~January 2011), so I will only have two pre-JDAP-implementation control time points.
+This limitation will be mitigated by the fact that there will be a lag between policy adoption is applicable to submitting authors and when their papers published.
+- There are many variables that are also important to views of community norms and decisions about sharing that I am not collecting to keep the survey short and maintain anonymity.
+These include university characteristics, industry affiliations, subfield, publication rate, and age.
+- This study makes no attempt to understand the rigor with which data sharing is encouraged in journals beyond their written policies:  many journals without policies nonetheless expect data sharing and many with written policies fail to enforce them.
+- The opinions of corresponding authors with respect to data sharing may not be typical of all authors:  a future study could be done to quantify this.
+- By only inviting authors to participate the first time they are listed as corresponding authors within our study scope, the population we are polling will shift gradually over time away from highly-prolific authors.
+- Respondents may be reluctant to self-report when they do not share their datasets, particularly as their sense of sharing as a community norm increases, since survey respondents are often reluctant to report engaging in socially undesirable behavior.
+- It will be difficult or impossible to derive causality direction for an association between reported data sharing behaviour and reported perception of data sharing as a community norm.
+- Finally, this study only facilitates a relatively short-term look at policy effect:  it will likely take many more years for the effect of these policies to be fully felt.
+
+Analysis of policy impact will be done using a modification of the commonly accepted difference-in-difference approach, as described by `r citep(bib["abadie2010synthet"])`.
+The responses of authors who published in JDAP-adopting journals will be compared, over time, to a) the responses of authors who publish in in-community journals that do not adopt JDAP, and b) the responses of authors who publish in outside-community journals that do not adopt JDAP.
+Because it is not clear which in-community and outside-community journals would provide the best counterfactual control of the JDAP-adopting journals, we will construct a “synthetic control” from a combination of responses across a subset of the control journals, as described in `r citep(bib["abadie2010synthet"])`.
+
+### Sample size
+
+The proposed study is subject to two different types of uncertainty:  uncertainty about the estimation of aggregate parameters, and also “uncertainty about the ability of the control group to reproduce the counterfactual of how the treated unit would have evolved in the absence of the treatment” (`r citep(bib["abadie2010synthet"])`.
+It is difficult to know how to conduct a formal power analysis in these conditions.
+We have based our sample size decisions on the following information.
+
+For populating the “treatment arm,” we plan to ask all corresponding authors of all JDAP-adopting journals.
+The average number of papers published per month in the JDAP journals is 168.
+Previous studies suggest 10%-30% of authors will complete the survey `r citep(c(bib["haeusslerinforma"], bib["wren2007the-wri"]))`.
+If we assume a response rate of 20%, we will receive about 33 responses from the intervention group every month.
+This would result in 95% confidence intervals around a Likert mean of 3.5 out of 7 ranges from 2.4 to 4.6.
+If these confidence intervals prove too wide to enable effective comparisons, we could aggregate the monthly data into less frequent samples across time.
+
+For populating the “control arms,” we recognize that the uncertainty is predominantly determined by the applicability of the controls.
+Little information is currently available to determine, a priori, which journals will serve as appropriate controls.
+As such, we suggest that surveying twice as many control journals as treatment journals may be an appropriate rule of thumb.
+This balances the need to avoid overpowering the study (and thereby increasing survey-fatigue and effort) with a desire to ensure the most useful results (anticipating that unexpected future events may render some controls inappropriate during the three years of this study, as well as recognizing that the quality of inference improves as the number of available comparison units increases `r citep(bib["abadie2010synthet"])`.
+
+Control journals will be selected by manual selection from a set of journals identified through ISI Journal Citation report categories as well as co-citation lists.
+Attempts will be made to choose journals with comparable impact factors and inclination to produce quantitative datasets.
+
+A 20% response rate and two control groups that are each twice as large as our treatment arm means we would receive about 33 treatment responses, 66 in-community control responses, and 66 outside-community responses per month.
+In total, we expect about 165 responses per month.
+Over the three years of data collection, this would lead to almost 6000 responses.
+The actual number of responses will be less than this, because will only invite each corresponding author once.
+On the other hand, the number of articles published by journals may increase over time and thus lead to a larger-than-anticipated sample.
+
+Finally, we note that to the best of our knowledge, a similar study has not been administered and/or published.
+If this sample size proves to be inadequate, the results can be viewed as pilot information to help inform future studies.
+
+### Data sharing plan
+
+Recruitment email addresses will be associated with the journal and month of publication.
+No other identifying information (author names, article title, etc) will be retained from ISI Web of Science.
+The researcher will not keep a record of participants’ names nor interface with them personally or by phone.
+Questionnaire responses will be submitted via online web survey tool ViewsFlash®:  the recruitment email addresses will not be linked to their corresponding survey response, but only linked in aggregate (in groups defined by journal and month of publication).
+
+Email addresses that are voluntarily provided by participants will be kept only for the duration of the prize drawing each month, and will not be linked to the survey responses in any way.
+
+Survey responses will be associated with journal and month of publication.
+The survey also asks the subjects to self-identify their job title (student, postdoc, tenured faculty, etc.)  We believe these datapoints will not be sufficient to permit reidentification, and will make no attempts to identify the respondents.
+
+To maximize the usefulness of this research, we plan to make the anonymous questionnaire responses openly available in a data repository for reuse, after aggregating or obfuscating any responses that could otherwise facilitate identification.
+
+### Recruitment
+
+Participants will be recruited from corresponding authors who publish in specific journals between November 2010 and February 2012.
+Specifically, email addresses will be collected for original research papers published the previous month (or 3 previous months, for the initial month of recruitment) in each of the target journals, using the ISI Web of Science.
+The email addresses will be associated with the journal and month of publication.
+No other identifying information (author names, article title, etc) will be retained.
+
+Recruitment email lists will be compared across months, and emails only sent to those who have not previously received a recruitment email to reduce survey fatigue and ill-will.
+
+A recruitment email will be sent to all identified email addresses, excluding those who had received a recruitment email in a prior month.
+The email invitation will include a URL where subjects can learn more about the study and then read a fact sheet, consent, and participate if they choose.
+This email will also contain an “opt out” option, which will remove their address from the reminder list.
+Those who have not “opted out” will be contacted by email again, a week later, politely asking them to take the survey if they haven’t already.
+
+Before the initial round of invitations is sent, we will inform journal editors of this ongoing survey and provide contact information in case they have questions, suggestions, or concerns.
+
+Individual participants can expect to spend 7-10 minutes maximum answering the online questionnaire.
+
+Previous studies suggest 10%-30% of authors will complete the survey `r citep(c(bib["haeusslerinforma"], bib["wren2007the-wri"]))`.
+
+some more: `r citep(c(
+bib["2015thank-y"],
+bib["anagnostou2015when-da"],
+bib["nosek2015scienti"],
+bib["stodden2018an-empi"],
+bib["budin-ljosne2014data-sh"],
+bib["hate2015sweat-s"],
+bib["naudet2018data-sh"],
+bib["curty2017attitud"],
+bib["linek2017data-sh"],
+bib["longo2016data-sh"],
+bib["berger2016iscbs-i"],
+bib["chigusa2017state-o"],
+bib["womack2015researc"],
+bib["doi:10.1002/asi.23917"],
+bib["plos-medicine-editors2016can-dat"],
+bib["van-tuyl2016water-w"],
+bib["vasilevsky2017reprodu"],
+bib["doi:10.1002/asi.23336"],
+bib["pearce2011data-sh"],
+bib["alsheikh-ali2011public-"],
+bib["vines2013mandate"],
+bib["roche2014trouble"],
+bib["roche2015public-"],
+bib["lin2014recomme"],
+bib["whitlock2016a-balan"],
+bib["naughton-l2016making-"],
+bib["teunis2015do-corr"],
+bib["fetterman2015the-rep"]
+))
+`
+
+## Methods
+
+## Data pre-processing
+
+Let's take a look at the numbers of responses by response date and publication date. Please keep in mind that the JDAP adoption dates used in the following analysis are approximate.
+
+```{r, cache=TRUE, message=FALSE, echo=FALSE}
+
+library(parsedate)
+library(dplyr)
+library(zoo)
+library(ggplot2)
+library(assertthat)
+
+load("./data/JDAP 2_clean.rda")
+load("./data/jdap_dates.rda")
+
+# add the journal info to the main dataset
+assert_that( all(d$journal %in% dates$journal) )
+d <- left_join(d, dates, by="journal")
+
+# format publication and response dates
+d$PublicationDate <- parse_date(with(d, paste(month, year)))
+d$ResponseDate <- parse_date(d$StartDate) %>% as.yearmon %>% as.POSIXct
+
+d$ResponseDate_YM <- as.yearmon(d$ResponseDate) %>% as.character
+d$ResponseDate_YQ <- as.yearqtr(d$ResponseDate) %>% as.character
+d$ResponseDate_Y <- strftime(d$ResponseDate, "%Y") %>% as.character
+
+d$PublicationDate_YM <- as.yearmon(d$PublicationDate) %>% as.character
+d$PublicationDate_YQ <- as.yearqtr(d$PublicationDate) %>% as.character
+d$PublicationDate_Y  <- strftime(d$PublicationDate, "%Y") %>% as.character
+
+# determine time since JDAP introduction in the journal where the article was published
+d$DaysPolicyToPublication <- difftime(d$PublicationDate, parse_date(d$policy_start), units="days")
+d$DaysPolicyToResponse <- difftime(d$ResponseDate, parse_date(d$policy_start), units="days")
+
+d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
+d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
+d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
+d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
+d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
+
+# number of responses by response date and journal policy in 2015
+group_by(d, Date=ResponseDate_YQ, policy) %>% dplyr::summarize(N=length(StartDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by response date.")
+
+# number of responses by publication date and journal policy in 2015
+group_by(d, Date=PublicationDate_YQ, policy) %>% dplyr::summarize(N=length(PublicationDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by publication date.")
+
+# It seems to make more sense to focus on the publication date for plotting, until it is clear why there are hardly any responses from the second half of 2013.
+```
 
@@
 
-In the following, I will present an overview of the responses to questions 1 and 2. The questions asked about the strength of agreement/disagreement with the following statements:
+In the following, I will present an overview of the responses to questions 1, 2, and 9. The questions asked about the strength of agreement/disagreement with the following statements:
 
@@
 * _Question 2_ It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
+* _Question 9_ I would seek alternative journals if JDAP was introduced.
 
@@
 library(reshape2)
+source("./src/aux_functions.R")
 source("./src/plotLikert.R")
@@
 
+And again, this time limited to people with at least one paper with archived data:
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_have_data <- c("5+ papers with archived data","2-4 papers with archived data","1 paper with archived data") # "No papers with archived data", response categories from top to bottom
+d_with_data <- subset(d, Q_3 %in% responses_have_data)
+
+responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
+tmp <- melt(d_with_data, measure.vars=paste0('Q_4_',1:16 ))
+tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
+p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+
+print(p)
+
+```
+
+And one more time, for people with no archived data:
+
+And again, this time limited to people with at least one paper with archived data:
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+responses_have_no_data <- c("No papers with archived data") 
+d_with_no_data <- subset(d, Q_3 %in% responses_have_no_data)
+
+responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
+tmp <- melt(d_with_data, measure.vars=paste0('Q_4_',1:16 ))
+tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
+p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+
+print(p)
+
+```
 <!-- Field: Q11-->
@@
 cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
-cur_d <- melt(cur_d, id.vars=id_vars) %>% %>% subset(value != "")
+cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
 cur_d$variable <- NULL
@@
 ```
+
+## Bibliolography
+
+```{r  results="asis", echo=FALSE, message=FALSE}
+# bibliography(sorting='nyt')
+write.bibtex(file="output_references.bib")
+````

### 2018-03-20 src/aux_functions.R

@@ -1,64 +1,19 @@
-# Source code from: http://statisfactions.com/2012/improved-net-stacked-distribution-graphs-via-ggplot2-trickery/
+vmap <- function (vec, from, to) {
+  newVec <- vec
+  for (i in 1:length(from)) {
+    newVec[vec == from[i]] <- to[i]
+  }
+  return(newVec)
+}
+nmap <- function (vec, fromto, cast = I) cast(vmap(vec, names(fromto), fromto))
 
-net_stacked <- function(x) {
-  
-  ## x: a data.frame or list, where each column is a ordered factor with the same levels
-  ## lower levels are presumed to be "negative" responses; middle value presumed to be neutral
-  ## returns a ggplot2 object of a net stacked distribution plot
-  
-  ## Test that all elements of x have the same levels, are ordered, etc.
-  all_levels <- levels(x[[1]])
-  n <- length(all_levels)
-  levelscheck <- all(sapply(x, function(y)
-    all(c(is.ordered(y), levels(y) == all_levels))
-  ))
-  if(!levelscheck)
-    stop("All levels of x must be ordered factors with the same levels")
-  
-  ## Reverse order of columns (to make ggplot2 output look right after coord_flip)
-  x <- x[length(x):1]
-  
-  ## Identify middle and "negative" levels
-  if(n %% 2 == 1)
-    neutral <- all_levels[ceiling(n/2)]
-  else
-    neutral <- NULL
-  
-  negatives <- all_levels[1:floor(n/2)]
-  positives <- setdiff(all_levels, c(negatives, neutral))
-  
-  ## remove neutral, summarize as proportion
-  listall <- lapply(names(x), function(y) {
-    column <- (na.omit(x[[y]]))
-    out <- data.frame(Question = y, prop.table(table(column)))
-    names(out) <- c("Question", "Response", "Freq")
-    
-    if(!is.null(neutral))
-      out <- out[out$Response != neutral,]
-    
-    out
-  })
-  
-  dfall <- do.call(rbind, listall)
-  
-  ## split by positive/negative
-  pos <- dfall[dfall$Response %in% positives,]
-  neg <- dfall[dfall$Response %in% negatives,]
-  
-  ## Negate the frequencies of negative responses, reverse order
-  neg$Freq <- -neg$Freq
-  neg$Response <- ordered(neg$Response, levels = rev(levels(neg$Response)))
-  
-  stackedchart <- ggplot() +
[…]

### 2018-03-20 src/plotLikert.R

@@ -1,0 +1,73 @@
+plot_likert <- function(d, response_order, above_mid, response, var_x, var_facet=NULL, na.label="No response", 
+                        xlab="% Responses", ylab="", include.N=FALSE) 
+{
+    stopifnot(above_mid %in% response_order)
+    
+    grouping_vars <- c(var_x, var_facet)
+    names(response) <- "Response"
+
+    agg_responses <- ddply(d, c(response, grouping_vars), function(x) c(N.resp=nrow(x)))
+    agg_totals <- ddply(d, c(grouping_vars), function(x) c(N.total=nrow(x)))
+    agg <- left_join(agg_responses, agg_totals, by=c(grouping_vars))
+    agg$P.resp <- with(agg, N.resp/N.total)
+    agg$sgnP.resp <- agg$P.resp
+    
+    if (include.N) {
+      agg[,var_x] <- sprintf("%s\n(N=%s)", agg[,var_x], agg$N.total)
+    }
+    
+    agg$Response <- as.character(agg$Response)
+    if (na.label != "") {
+      agg$Response[is.na(agg$Response)] <- na.label
+    } else {
+      agg <- agg[!is.na(agg$Response),]
+    }
+    
+    neutral_levels <- unique(agg$Response) %>% .[!. %in% response_order]
+    agg$Response <- ordered(agg$Response, levels=c(response_order, neutral_levels))
+    
+    is_neutral <- with(agg, !Response %in% response_order)
+    agg_neutral <- agg[is_neutral,]
+    agg_neg <- subset(agg[!is_neutral,], Response > above_mid)
+    agg_pos <- subset(agg[!is_neutral,], Response <= above_mid)
+    agg_neg$sgnP.resp <- -agg_neg$sgnP.resp
+    
+    n_pos <- length(unique(agg_pos$Response))
+    n_neg <- length(unique(agg_neg$Response))
+    n_neutral <- length(unique(agg_neutral$Response))
+    
+    fill_type <- c(rep("blue",n_pos), rep("red",n_neg), rep("darkgrey",n_neutral))
+    names(fill_type) <- sort(unique(agg$Response))
+    
+    alpha_type <- c(seq(1,.25,length.out=n_pos), seq(.25,1,length.out=n_neg), seq(1,.25,length.out=n_neutral) )
+    names(alpha_type) <- sort(unique(agg$Response))
+    
+    agg_pos <- agg_pos[order(agg_pos$Response, decreasing=T),]
[…]

### 2018-03-20 data/overview/raw_data_overview.Rmd

--- 2015-05-24 analysis.Rmd
@@
 ---
-title: "Data Archiving Attitudes"
-author: "Heather Piwowar, Pavel Logacev, Todd J. Vision"
-date: "May 17, 2015"
+title: "Overview of responses to questions with multiple non-exclusive options"
 output:
   html_document:
-    css: style.css
     fig_caption: yes
@@
     fig_caption: yes
-bibliography: bibliography.bib
-<!-- csl: apa.csl -->
 ---
@@
 
-This is where the abstract goes.
-
-# Introduction
-Some researchers are sceptical regarding data archiving.
-We conducted a survey in order to find out how the adoption of data archiving policies by journals affects researcher's attitudes towards archiving and sharing data.
-
-# The Survey
-
-## Method
-
-<!-- load and prepare data -->
+# Load data
 
@@
 library(assertthat)
+source("./src/aux_functions.R")
 
-load("./data/JDAP_Survey_Data_Tidy.rda") # loads 'd'
-load("./data/Journal_JDAP_Adoption_Dates.rda") # loads 'dates'
-load("./data/Invitations_Timing.rda") # loads 'invitation_timing'
-interactive_mode <- FALSE
+d <- read.csv("../raw_data/JDAP_Survey_Data.csv", header=T, fill=TRUE, fileEncoding="UTF-8", as.is=T)
+key <- d[1,]
+d <- d[-1,]
+colnames(d)[1:6] <- as.character(key[1:6])
 
-# add the journal info to the main dataset
-assert_that( all(d$journal %in% dates$journal) ) %>% invisible
-d <- left_join(d, dates, by="Journal")
+cross_tab_responses <- function(d, cnames) {
+  x <- d[,cnames]
+  new_cnames <- apply(x, 2, function(x) unique(x[x!=""])) 
+  colnames(x) <- new_cnames #%>% gsub(" ", "\n", .)
+  x <- x!=""
 
-# # format publication and response dates
-d$PublicationDate <- parse_date(d$PublicationDate) %>% as.yearmon
-d$ResponseDate <- parse_date(d$ResponseDate) %>% as.yearmon
+  res <- apply(x, 2, function(c1) apply(x, 2, function(c2) sum(c1&c2) ))
+  res[lower.tri(res)] <- NA
+  # diag(res) <- NA
 
-d$ResponseDate_YM <- as.yearmon(d$ResponseDate) %>% as.character
-d$ResponseDate_YQ <- as.yearqtr(d$ResponseDate) %>% as.character
-d$ResponseDate_Y <- strftime(d$ResponseDate, "%Y") %>% as.character
+  # colnames(res) <- new_cnames %>% gsub(" ", " ", .) %>% sprintf("\"%s\"", .)
 
-d$PublicationDate_YM <- as.yearmon(d$PublicationDate) %>% as.character
-d$PublicationDate_YQ <- as.yearqtr(d$PublicationDate) %>% as.character
-d$PublicationDate_Y  <- strftime(d$PublicationDate, "%Y") %>% as.character
-
-# determine time since JDAP introduction in the journal where the article was published
-d$DaysPolicyToPublication <- difftime(d$PublicationDate, parse_date(d$policy_start), units="days")
-d$DaysPolicyToResponse <- difftime(d$ResponseDate, parse_date(d$policy_start), units="days")
-
-d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
-d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
-d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
-d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
-# d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
-
-# NOTE: two invitations have NA for a publication date
-# subset(invitation_timing, is.na(publication_date))
-
-invitation_timing <- subset(invitation_timing, !is.na(publication_date))
-invitation_timing$PublicationDate_YQ <- as.character(invitation_timing$publication_date) %>% parse_date %>% as.yearqtr
-n_invitations_by_publication <- ddply(invitation_timing, .(Date=PublicationDate_YQ), summarize, N=length(PublicationDate_YQ))
-n_invitations_by_sent_month <- ddply(invitation_timing, .(Date=as.yearmon(sent_date)), summarize, N=length(PublicationDate_YQ))
-
-d$label_PolicyAdoptedAtPublication <- gsub(" ", "\n", d$PolicyAdoptedAtPublication)
+  res
+}
 
@@
 
-The survey was carried out using [Survey Monkey](www.surveymonkey.com).
-Invitations to participate were sent out monthly between February 2011 and March 2014 to a selection of between $`r min(n_invitations_by_sent_month$N)`$ and $`r max(n_invitations_by_sent_month$N)`$ (with an average of $`r round(mean(n_invitations_by_sent_month$N))`$) authors of recently published articles in a pre-selected sample of journals.
-<!-- TODO: how were the journals selected -->
-The invitations were sent out to a total of $`r nrow(invitation_timing)`$ authors, and $`r nrow(d)`$ responded (corresponding to a non-response rate of $`r round(100*nrow(d)/nrow(invitation_timing))`$\%).
-Figure 1 shows the numbers of invitations and responses by the date of the author's last publication.
-Participants filled in a questionnaire consisting of 15 multiple-choice questions regarding their attitudes, concerns and experiences with data archiving and sharing.
-
-```{r responseRates, cache=FALSE, message=FALSE, echo=FALSE, fig.width=5, fig.height=3, anchor="figure", fig.cap="Number of invitations and responses by quarter."}
-
-library(ggplot2)
-library(dplyr)
-library(zoo)
-library(parsedate)
-
-n_by_publication_date <- ddply(d, .(Date=as.character(PublicationDate_YQ)), function(x) c(N=nrow(x))) %>% cbind(., type="Responses")
-n_invitations_by_publication$Date <- as.character(n_invitations_by_publication$Date)
-n_by_publication_date <- n_by_publication_date %>% rbind( cbind(n_invitations_by_publication, type="Invitations"), .)
-
-p_by_publication_date <- n_by_publication_date %>% ggplot(aes(Date, N, fill=type, alpha=type, group=type)) + 
-              ylab("Number of invitations and responses")+xlab("Date of Publication")+geom_bar(stat="identity", position="dodge") +
-              scale_fill_manual(values=c("blue", "blue"))+scale_alpha_manual(values=c(.5, 1))+theme_bw() + 
-              theme(axis.title.y=element_text(size=rel(0.8)), axis.title.x=element_text(size=rel(0.8)), axis.text.x=element_text(angle=90,hjust=1), legend.title=element_blank())
-
-print(p_by_publication_date)
-```
-
-<!-- TODO: how were the responses spread out over journal types? when was the JDAP introduced when it was introduced, mean and SD? -->
-
-## Results
-
-In the following, I will present an overview of the responses to questions 1 and 2. The questions asked about the strength of agreement/disagreement with the following statements:
-
-* _Question 1_ It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
-Include data sharing that occurs by any mechanism (e.g.
-emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
-* _Question 2_ It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
-
----
-
-The following plots show the responses regarding the attitudes towards data sharing and archiving for participants who (i) published in journals which have note adopted the JDAP so far ('No JDAP'), (ii) published in journals which had not _yet_ adopted the JDAP before publication ('Before JDAP'), and (iii) journals which had adopted the JDAP before publication ('After JDAP).
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
-
-tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9')) #,'Q_12','Q_13'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
+```{r, message=FALSE, eval=TRUE, echo=FALSE}
+options(digits=2)
 
@@
 
-### Inferential statistics
-
-```{r, message=FALSE, eval=TRUE, echo=FALSE}
-
-library(MASS)
-library(zoo)
-library(dplyr)
-library(knitr)
-
-d$cAfterPolicyChange <- ifelse(d$PolicyAdoptedAtPublication=="After JDAP", 1, 0)
-d$cNonJDAPJournal <- ifelse(d$PolicyAdoptedAtPublication=="No JDAP", 1, 0)
-d$cDate <- as.double(as.yearmon(d$PublicationDate)) %>% scale(., scale=F)
-
-d$respQ1 <- ordered(d$Q_1, levels=rev(levels(d$Q_1)))
-d$respQ2 <- ordered(d$Q_2, levels=rev(levels(d$Q_2)))
-
-m4 <- polr(respQ1 ~ 1 + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
-# summary(m4)
-m4.justchange <- polr(respQ1 ~ 1 + cAfterPolicyChange, data=d , Hess=TRUE)
-m4.nochange <- polr(respQ1 ~ 1 + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
-suppressMessages( ci4 <- confint(m4) )
-table4 <- exp(cbind(OR = coef(m4), ci4)) %>% cbind(., t=coef(summary(m4))[1:nrow(.),'t value'])
-#table4 <- cbind(lOR = coef(m4), ci4) %>% cbind(., t=coef(summary(m4))[1:nrow(.),'t value'])
-
-m5 <- polr(respQ2 ~ 1  + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
-m5.justchange <- polr(respQ2 ~ 1 + cAfterPolicyChange , data=d, Hess=TRUE)
-m5.nochange <- polr(respQ2 ~ 1 + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
-# summary(m5)
-suppressMessages( ci5 <- confint(m5) )
-table5 <- exp(cbind(OR = coef(m5), ci5)) %>% cbind(., t=coef(summary(m5))[1:nrow(.),'t value'])
-
-aov.m4.justchange <- anova(m4, m4.justchange)
-aov.m4.nochange <- anova(m4, m4.nochange)
-aov.m5.justchange <- anova(m5, m5.justchange)
-aov.m5.nochange <- anova(m5, m5.nochange)
-
-# aov.m5.nochange
-
-```
-
-The potential effect of JDAP adoption on authors' attitudes is might be confounded by two other factors.
-Firstly, groups of researchers publishing in journals which are not planning to adopt the JDAP (or at least have not done so yet) may inherently differ from groups publishing in journals which were open to adopting the JDAP.
-Secondly, attitudes regarding data archiving may improve over time.
-
-In order to test for an effect of policy change on attitudes while controlling for potential confounding effects, we used an ordinal logistic regression model with three predictors: (i) journal type _(cNonJDAPJournal)_, (ii) (centered) publication date in years _(cDate)_, and (iii) a variable indicating whether the article was published after the the journal adopted a data archiving policy _(cAfterPolicyChange)_.
-
-The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 1*.
-Effects are statistically significant at the $\alpha=0.05$ level when the transformed confidence intervals do not contain $1$.
-Confidence intervals were obtained by profile likelihood.
-According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data sharing* by a factor of $1.36$ (CI=$[1.16; 1.60]$), while the remaining two predictors do not show any statistically significant effects.
-
-```{r, message=FALSE, eval=TRUE, echo=FALSE}
-options(digits=2)
-```
-
-We conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
-The first likelihood-ratio test, comparing the full three-predictor model with a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m4.nochange[["   Df"]][2]`)=`r aov.m4.nochange[["LR stat."]][2]`$, $p<0.001$).
-A second likelihood-ratio test comparing the full model with a reduced model using _only_ the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m4.justchange[["   Df"]][2]`)=`r aov.m4.justchange[["LR stat."]][2]`$, $p=`r aov.m4.justchange[["Pr(Chi)"]][2]`$).
-
-<!-- http://kbroman.org/knitr_knutshell/pages/figs_tables.html -->
-```{r, message=FALSE, eval=TRUE, echo=FALSE}
-kable(table4, digits=2)
-```
-
-The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 2*.
-According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data archiving* by a factor of $1.57$ (CI=$[1.33; 1.90]$), while the remaining two predictors do not show any statistically significant effects.
-
-Here too, we conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
-The first likelihood-ratio test, comparing the full three-predictor model with a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m5.nochange[["   Df"]][2]`)=`r aov.m5.nochange[["LR stat."]][2]`$, $p<0.001$).
-A second likelihood-ratio test comparing the full model with a reduced model using _only_ the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m5.justchange[["   Df"]][2]`)=`r aov.m5.justchange[["LR stat."]][2]`$, $p=`r aov.m5.justchange[["Pr(Chi)"]][2]`$).
-
-```{r, message=FALSE, eval=TRUE, echo=FALSE}
-options(digits=2)
-kable(table5, digits=2)
-```
-
-# Appendix
-
-## Appendix A: Questionnaire Structure
-<!-- TODO: Add response options below. -->
-
-How strongly do you disagree/agree with the following statements? (Regarding the next two questions.)
-
-<!-- Field: Q4 -->
-1.
-It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
-Include data sharing that occurs by any mechanism (e.g.
-emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
-
-_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
-
-<!-- Field: Q5 -->
-2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
-
-_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
-
-```{r, fig.width=7, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
-
-tmp <- melt(d, measure.vars=c('Q_1','Q_2'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
-
-```
-
-<!-- Field: Q7 -->
-3. Do any of your published research papers have publicly archived datasets?
-
-  Response Options:
-  1. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
-  2. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
-  3. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
-  4. No, none of my paper-related datasets are publicly available on the internet
-  5. I've never published a paper based on a dataset collected by me or my co-authors
-  6. I'm not sure if any of my papers have publicly available datasets
-
-```{r, fig.width=7, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses <- c("5+ papers with archived data","2-4 papers with archived data","1 paper with archived data","No papers with archived data") # response categories from top to bottom
-tmp <- melt(d, measure.vars=c('Q_3'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="1 paper with archived data", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
-
-```
-
-<!-- Field: Q9 -->
-4.
-To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups?
-Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
-  a.  I formed new collaborations <!-- Field: Q9_1 / Q_4_1 -->
-	b.  I formed new collaborations that led/are leading to publications <!-- Field: Q9_2 / Q_4_2 -->
-	c.  I formed new collaborations that led/are leading to grants <!-- Field: Q9_3 / Q_4_3 -->
-	d.  Others have used my datasets and formally cited me <!-- Field: Q9_4 / Q_4_4 -->
-	e.  Others have used my datasets but did not formally cite me <!-- Field: Q9_5 / Q_4_5 -->
-	f.  Others have found errors in my research through my datasets <!-- Field: Q9_7 / Q_4_6 -->
-	g.  Others misinterpreted my datasets or used them inappropriately <!-- Field: Q9_8 / Q_4_7 -->
-	h.  I have had ongoing research projects scooped by another scientist <!-- Field: Q9_9 / Q_4_8 -->
-	i.  I have had future research plans scooped by another scientist <!-- Field: Q9_10 / Q_4_9 -->
-	j.  The ability of a junior colleague in my group (graduate student, postdoctoral fellow, or junior faculty member) to publish subsequent research has been compromised <!-- Field: Q9_11 / Q_4_10 -->
-	k.  My ability to receive commercial benefit from my research has been diminished <!-- Field: Q9_12 / Q_4_11 -->
-	l.  I spent a lot of money preparing data for sharing <!-- Field: Q9_13 / Q_4_12 -->
-	m.  I spent a lot of time preparing data for sharing <!-- Field: Q9_14 / Q_4_13 -->
-	n.  I spent a lot of time answering questions from qualified researchers about my shared data <!-- Field: Q9_15 / Q_4_14 -->
-	o.  Other (please specify) <!-- Field: Q9_16 - Q9_16_TEXT / Q_4_15 - Q_4_15_TEXT -->
-  p.  I spent a lot of time answering questions from unqualified researchers about my shared data <!-- Field: Q9_17 / Q_4_16 -->
-
-  Response Options:
-  1. Many times
-  2. A few times
-  3. Once
-  4. Never
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
-tmp <- melt(d, measure.vars=paste0('Q_4_',1:16 ))
-tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
-p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
-
-print(p)
-
-```
+# Question 5
 
@@
 
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
+library(plyr)
+library(dplyr)
+library(knitr)
+library(pander)
 
-responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
-tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
-tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
-#p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+cross_tab_responses(d, paste0('Q11_1_',1:6)) %>% kable
 
-print(p)
+cross_tab_responses(d, paste0('Q11_2_',1:6)) %>% kable
+
+cross_tab_responses(d, paste0('Q11_3_',1:6)) %>% kable
 
@@
 
+# Question 6
+
 <!-- Field: Q12 -->
 6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
-
-Response options:
   a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
@@
 
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
+library(plyr)
+library(dplyr)
+library(knitr)
 
-id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
-cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
-cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
-cur_d$variable <- NULL
-
-d$Q_6
-
-levels <- c("ALL datasets are publicly available online","SOME but not all of the datasets are publicly available online",
-            "NONE of the datasets are publicly available online","We did not collect any data for that publication",
-            "I don't know", "Other (please specify)")
-cur_d$value <- ordered(cur_d$value, levels=levels)
-
-x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
-p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")
-
-p + theme_bw()
+cross_tab_responses(d, paste0('Q12_',1:6)) %>% kable
 
 ```
+
+# Question 7
 
@@
 
-```{r, fig.width=10, fig.height=5, echo=FALSE}
+```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}
 
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
-cur_d <- d[,c(id_vars,paste0('Q_7_', 1:6))]
-cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
-cur_d$variable <- NULL
-
-levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website",
-            "The entire dataset is in the body of the paper", "Not applicable", "Other (please specify)")
-cur_d$value <- ordered(cur_d$value, levels=levels)
-
-x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
-p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")
-
-p + theme_bw()
+# library(plyr)
+# library(dplyr)
+# library(knitr)
+# 
+# cross_tab_responses(d, paste0('Q13_',1:6)) %>% kable
 
 ```
+
+# Question 8
 
@@
 
-The questions below refer to the Joint Data Archiving Policy, an example policy statement adopted by ... <!-- TODO -->
+```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}
 
-<!-- Field: Q17 -->
-9. How strongly do you disagree/agree with this statement? I would seek alternative journals if I learned that my target journal had adopted the Joint Data Archiving Policy (above).
-
-Response options:
-  i. Strongly Agree
-  ii. Agree
-  iii. Somewhat Agree
-  iv. Neutral
-  v. Somewhat Disagree
-  vi. Disagree
-  vii. Strongly Disagree
-
-```{r, fig.width=5, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
-
-tmp <- melt(d, measure.vars=c('Q_9'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
+# library(plyr)
+# library(dplyr)
+# library(knitr)
+# 
+# cross_tab_responses(d, paste0('Q14_',1:10)) %>% kable
 
 ```
+
+# Question 8
+
 <!-- Field: Q18 -->
@@
 
+```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}
+
+# library(plyr)
+# library(dplyr)
+# library(knitr)
+# 
+# d[,paste0('Q18_',1:3)] %>% head
+# 
+# 
+# cross_tab_responses(d, paste0('Q18_',1:3)) %>% kable
+
+```
+
+# Question 11
+
 <!-- Field: Q19 -->
@@
 
-<!-- Field: Q21 -->
-12. How strongly do you disagree/agree with the following statements? Using datasets collected by investigators outside my research group is important in my research.
+```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}
 
-<!-- Field: Q22 -->
-13. Using datasets collected by investigators outside my research group is important in my teaching or other non-research projects.
-
-<!-- Field: Q23/Q23_TEXT -->
-14. Please choose the title that most closely matches yours:
-
-<!-- Field: Q25 -->
-15. Do you have any comments on the topic, or suggestions for how to improve this questionnaire?
-
-<!-- Field: Q26 -->
-16. Thank you for completing this survey! If you would like to enter the drawing for a $20 Amazon gif... <!-- TODO -->
-
-## Appendix B: Overview of responses to all questions
-
-## Questions 5
-5.
-To your knowledge, what are the policies of these stakeholders as they apply to online public archiving of the datasets associated with your (month) (year) publication in (journal)?
-Choose all that apply
-        a.  The journal  <!-- Field: Q11_1 -->
-        b.  Your funder(s)  <!-- Field: Q11_2 -->
-        c.  Your employer or institution  <!-- Field: Q11_3 -->
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
-
-tmp <- melt(d, measure.vars=paste0('Q_5_',c(1:3) ))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
-
-print(p)
+# library(plyr)
+# library(dplyr)
+# library(knitr)
+# 
+# cross_tab_responses(d, paste0('Q19_',1:11)) %>% kable
 
 ```
-
-## Questions 6
-6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
-a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
-  b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
-  c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
-  d.  I don't know   <!-- Field: Q12_4 -->
-e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
-f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
-<!-- TODO: What is d$Q_6_7 ??? -->
-
-```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-library(plyr)
-library(dplyr)
-library(vcd)
-
-cnames <- paste0('Q_6_',1:6)
-x <- d[,cnames]
-new_cnames <- apply(x, 2, function(x) unique(x[x!=""])) 
-colnames(x) <- new_cnames
-x <- x!=""
-x
-
-res <- apply(x, 2, function(c1) apply(x, 2, function(c2) sum(c1&c2) ))
-res[lower.tri(res)] <- NA
-diag(res) <- NA
-res
-
-```
-
-## Questions 12, 13
-
-```{r, eval=FALSE, fig.width=7, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-tmp <- melt(d, measure.vars=c('Q_12','Q_13'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
-
-```

### 2018-03-20 manuscript.Rmd
add data back in

@@
 
-## Data pre-processing
-
-Let's take a look at the numbers of responses by response date and publication date. Please keep in mind that the JDAP adoption dates used in the following analysis are approximate.
-
-```{r, cache=TRUE, message=FALSE, echo=FALSE}
-
-library(parsedate)
-library(dplyr)
-library(zoo)
-library(ggplot2)
-library(assertthat)
-
-load("./data/JDAP 2_clean.rda")
-load("./data/jdap_dates.rda")
-
-# add the journal info to the main dataset
-assert_that( all(d$journal %in% dates$journal) )
-d <- left_join(d, dates, by="journal")
-
-# format publication and response dates
-d$PublicationDate <- parse_date(with(d, paste(month, year)))
-d$ResponseDate <- parse_date(d$StartDate) %>% as.yearmon %>% as.POSIXct
-
-d$ResponseDate_YM <- as.yearmon(d$ResponseDate) %>% as.character
-d$ResponseDate_YQ <- as.yearqtr(d$ResponseDate) %>% as.character
-d$ResponseDate_Y <- strftime(d$ResponseDate, "%Y") %>% as.character
-
-d$PublicationDate_YM <- as.yearmon(d$PublicationDate) %>% as.character
-d$PublicationDate_YQ <- as.yearqtr(d$PublicationDate) %>% as.character
-d$PublicationDate_Y  <- strftime(d$PublicationDate, "%Y") %>% as.character
-
-# determine time since JDAP introduction in the journal where the article was published
-d$DaysPolicyToPublication <- difftime(d$PublicationDate, parse_date(d$policy_start), units="days")
-d$DaysPolicyToResponse <- difftime(d$ResponseDate, parse_date(d$policy_start), units="days")
-
-d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
-d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
-d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
-d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
-d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
-
-# number of responses by response date and journal policy in 2015
-group_by(d, Date=ResponseDate_YQ, policy) %>% dplyr::summarize(N=length(StartDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by response date.")
-
-# number of responses by publication date and journal policy in 2015
-group_by(d, Date=PublicationDate_YQ, policy) %>% dplyr::summarize(N=length(PublicationDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by publication date.")
-
-# It seems to make more sense to focus on the publication date for plotting, until it is clear why there are hardly any responses from the second half of 2013.
-```
-
 # Introduction
@@
 ## Method
-
-<!-- load and prepare data -->
 
@@
 
-load("./data/JDAP_Survey_Data_Tidy.rda") # loads 'd'
-load("./data/Journal_JDAP_Adoption_Dates.rda") # loads 'dates'
-load("./data/Invitations_Timing.rda") # loads 'invitation_timing'
+load("./data/derived/JDAP_Survey_Data_Tidy.rda") # loads 'd'
+load("./data/derived/Journal_JDAP_Adoption_Dates.rda") # loads 'dates'
+load("./data/derived/Invitations_Timing.rda") # loads 'invitation_timing'
 interactive_mode <- FALSE
@@
 Participants filled in a questionnaire consisting of 15 multiple-choice questions regarding their attitudes, concerns and experiences with data archiving and sharing.
-
-```{r responseRates, cache=FALSE, message=FALSE, echo=FALSE, fig.width=5, fig.height=3, anchor="figure", fig.cap="Number of invitations and responses by quarter."}
-
-library(ggplot2)
-library(dplyr)
-library(zoo)
-library(parsedate)
-
-n_by_publication_date <- ddply(d, .(Date=as.character(PublicationDate_YQ)), function(x) c(N=nrow(x))) %>% cbind(., type="Responses")
-n_invitations_by_publication$Date <- as.character(n_invitations_by_publication$Date)
-n_by_publication_date <- n_by_publication_date %>% rbind( cbind(n_invitations_by_publication, type="Invitations"), .)
-
-p_by_publication_date <- n_by_publication_date %>% ggplot(aes(Date, N, fill=type, alpha=type, group=type)) + 
-              ylab("Number of invitations and responses")+xlab("Date of Publication")+geom_bar(stat="identity", position="dodge") +
-              scale_fill_manual(values=c("blue", "blue"))+scale_alpha_manual(values=c(.5, 1))+theme_bw() + 
-              theme(axis.title.y=element_text(size=rel(0.8)), axis.title.x=element_text(size=rel(0.8)), axis.text.x=element_text(angle=90,hjust=1), legend.title=element_blank())
-
-print(p_by_publication_date)
-```
-
-<!-- TODO: how were the responses spread out over journal types? when was the JDAP introduced when it was introduced, mean and SD? -->
 

### 2018-03-20 manuscript.Rmd
fix label ordering, and make stacked bars

@@
 d$label_PolicyAdoptedAtPublication <- ordered(gsub(" ","\n",d$PolicyAdoptedAtPublication), levels=gsub(" ","\n",levels_TimeClass))
+d$label_PolicyAdoptedAtPublication_space <- ordered(gsub(" "," ",d$PolicyAdoptedAtPublication), levels=gsub(" "," ", levels_TimeClass))
 
@@
 
+library(dplyr)
 library(ggplot2)
@@
 tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
 p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
@@
 
-p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
+p <- ggplot(tmp, aes(x = label_PolicyAdoptedAtPublication, y = 100*class.Proportion, fill = value)) + geom_bar(stat = "identity")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
+
 p + theme_bw()
@@
 tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
 
@@
 tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("10_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
 p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
@@
 tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("11_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
 p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

### 2018-03-20 manuscript.Rmd
make .md

@@
 date: "March 20, 2018"
-csl: f1000-research.csl
 output:
+  md_document:
+    variant: markdown_github
   html_document:
@@
     toc: yes
-  md_document:
-    variant: markdown_github
   pdf_document:
@@
     fig_caption: yes
+csl: f1000-research.csl
 bibliography: input_references.bib

### 2018-03-21 manuscript.Rmd
updates

@@
 output:
-  md_document:
-    variant: markdown_github
   html_document:
@@
     toc: yes
+  md_document:
+    variant: markdown_github
   pdf_document:
@@
     fig_caption: yes
-csl: f1000-research.csl
+csl: peerj.csl
 bibliography: input_references.bib
@@
 
+# Abstract
+
+# Introduction
+
 There have been previous studies of data sharing patterns, but we are not aware of any prior research that examined attitudes and experiences of authors before and after policy implementation.
 
-The promise of data sharing and the role of data sharing policies
+## The promise of data sharing
 
@@
 `r citep(c(bib["blumenthal1997withhol"], bib["ochsner2008much-ro"], bib["savage2009empiric"]))`.
+
+## Data archiving journal policies
 
@@
 
-#### Dimensions of impact
-
 A journal policy that requires authors to share the datasets that support their results as a condition of publication may impact the practices, attitudes, and opinions of data producing authors in many ways.
-Here, we emphasize the short-term impacts on authors who publish in the policy-adopting journals.
-
 The most direct impact is likely a change in frequency of data sharing, and a shift to data archiving locations specified in the policy.
@@
 
-Upcoming policy change is a useful opportunity for policy evaluation
+## Upcoming policy change is a useful opportunity for policy evaluation
 
-Several journals plan to adopt the Joint Data Archiving Policy in early 2011, as described at http://datadryad.org/jdap.  Participating journals include:
-
-- American Naturalist
-- Evolution
-- Evolutionary Applications
-- Heredity
-- Journal of Evolutionary Biology
-- Molecular Biology and Evolution.
-- Molecular Ecology
+Several journals plan to adopt the Joint Data Archiving Policy in early 2011, as described at http://datadryad.org/jdap.
 
@@
 
-Rigorous research is needed into the impact of journal policies
+## Rigorous research is needed into the impact of journal policies
 
@@
 
-Research questions
+## Research questions
 
@@
 - Are changes specific to the journals that implement the policies, or do they extend to other journals in the same subfield?
+- Does publishing in a journal with a mandatory data archiving policy decrease an author's willingness to publish in a journal with a mandatory data archiving policy again?
 
-## Primary analysis
-The primary analysis will be a seven-point Likert scale asking how strongly authors believe:  “It is the community norm in my field to publicly share datasets upon study publication by archiving all datasets online, for use by anyone for any purpose.”
+Twelve other survey questions will allow secondary and exploratory analyses.
 
-About twelve other survey questions will allow secondary and exploratory analyses.
+# Methods
 
-## Methods
-Participants will be recruited from corresponding authors who publish in specific journals between November 2010 and November 2013.
-Specifically, email addresses will be collected for papers published the previous month (or 3 previous months, for the initial month of recruitment) in each of the target journals through the ISI Web of Science.
-No other identifying information (author names, article title, etc) will be retained.
-
-Recruitment email lists will be compared across months, and emails only sent to those who have not previously received a recruitment email to reduce survey fatigue and ill-will.
-
-The email invitation will include a URL where subjects can learn more about the study and then read a fact sheet, consent, and participate if they choose.
-This email will also contain an “opt out” option, which will remove their address from the reminder list.
-Those who have not “opted out” will be contacted by email again, a week later, politely asking them to take the survey if they haven’t already.
-
-Individual participants can expect to spend 7-10 minutes maximum answering the online questionnaire.
-
-Before the initial round of invitations is sent, I will inform journal editors of this ongoing survey and provide contact information in case they have questions, suggestions, or concerns.
-
-Previous studies suggest 10%-30% of authors will complete the survey `r citep(c(bib["haeusslerinforma"], bib["wren2007the-wri"]))`.
-
-Gender, ethnicity, and race are irrelevant to the study.
-Other than the requirement that participants be 18 years of age or older, age is irrelevant to the study.
-Medical history and/or conditions are irrelevant to the study.
-
-To facilitate legal consent, this study is restricted to participants who are 18 years of age or older.
-The study is intended to establish knowledge about the implications of policies on active researchers.
-No other criteria are necessary for inclusion; no criteria are grounds for exclusion.
-
-## Methods 2
-
-We expect the JDAP policies to be implemented in or about January 2011, though it will take several months to see any effect because the policies will likely be applied to newly submitted papers it will take multiple months for these papers to be published.
-This timeline is likely to vary across JDAP-adopting journals depending on the length of their publication cycle.
-
-Participants will be recruited from corresponding authors who publish in specific journals between November 2010 and November 2013.
-An invitation to the survey will be issued once a month to all corresponding authors who published in specific journals the prior month.
-The responses of authors who published in JDAP-adopting journals will be compared, over time, to a) the responses of authors who publish in in-community journals that do not adopt JDAP, and b) the responses of authors who publish in outside-community journals that do not adopt JDAP.
-
-### Data collection
+Participants were recruited from corresponding authors who publish in specific journals between November 2010 and November 2013.
+The responses of authors who published in JDAP-adopting journals were then compared, over time, to the responses of authors who published in similar journals that did not adopt JDAP.
 
 The instrument used to collect data is be an online questionnaire.
-The questionnaire is designed to elicit the respondent’s practices, experiences, and opinions around public archiving of research datasets by asking about their opinion of community norms, recent behaviour with respect to a recently published paper, previous experiences with data sharing, and attitudes toward hypothetical situations.
+The questionnaire is designed to elicit the respondent’s practices, experiences, and opinions around public archiving of research datasets by asking about their opinion of community norms, recent behaviour with respect to a recently published paper, previous experiences with data sharing, and attitudes toward hypothetical journal policies
+
+## Control jounrnals and sample size
+
+The proposed study is subject to two different types of uncertainty:  uncertainty about the estimation of aggregate parameters, and also “uncertainty about the ability of the control group to reproduce the counterfactual of how the treated unit would have evolved in the absence of the treatment” (`r citep(bib["abadie2010synthet"])`.
+It was difficult to know how to conduct a formal power analysis in these conditions, so we  based our sample size decisions on the following information.
+
+For populating the “treatment arm,” we asked all corresponding authors of all JDAP-adopting journals.
+
+For populating the “control arms,” we recognized that the uncertainty is predominantly determined by the applicability of the controls.
+Little information is currently available to determine, a priori, which journals will serve as appropriate controls.
+As such, we decided that surveying twice as many control journals as treatment journals was an appropriate rule of thumb.
+This balanced the need to avoid overpowering the study (and thereby increasing survey-fatigue and effort) with a desire to ensure the most useful results (anticipating that unexpected future events may render some controls inappropriate during the three years of this study, as well as recognizing that the quality of inference improves as the number of available comparison units increases `r citep(bib["abadie2010synthet"])`.
+
+Control journals were selected by manual selection from a set of journals identified through ISI Journal Citation report categories as well as co-citation lists.
+Attempts were made to choose journals with comparable impact factors and inclination to produce quantitative datasets.
+
+Assuming a 20% response rate and a control arm that was twice as large as the treatment arm, we expected a maximum of 165 responses per month, or almost 6000 responses over the course of the three year study.
+The actual number of responses was expected to be lower than this because only invited each corresponding author the first time they published a paper.
+
+Journal editors were informed of the survey before it began and given contact information in case they had questions, suggestions, or concerns.
+
+## Participant recruitment
+
+Participants were recruited from corresponding authors who published in specific journals between November 2010 and November 2013.
+Specifically, email addresses were collected for papers published the previous month (or 3 previous months, for the initial month of recruitment) in each of the target journals through the ISI Web of Science.
+No other identifying information (author names, article title, etc) was retained.
+
+The email invitation included  a URL where subjects can learn more about the study and then read a fact sheet, consent, and participate if they choose.
+This email contained contain an “opt out” option, which will remove their address from the reminder list.
+Those who did not “opt out” were contacted by email again, a week later, politely asking them to take the survey if they haven’t already.
+
+Recruitment email lists were compared across months, and emails only sent to those who have not previously received a recruitment email to reduce survey fatigue and ill-will.
+
+The online survey was administered through Qualtrics, hosted by the University of North Carolina.  The online questionnaire took about 10 minutes to complete.
+
+## Analysis
+
+The responses of authors who published in JDAP-adopting journals were compared, over time, to  the responses of authors who published in similar journals that did not adopt JDAP.
 
@@
 
-Aggregate answers will be compared over time, to understand if answers of authors in journals that adopt JDAP begin to differ from those of authors in comparable within-community and outside-community control journals.
+# Results
 
-The online survey will be administered through ViewsFlash® 6 by Cogix, hosted by Duke University.  There will be no way link the responses with the identities of participants.
+## Response rate
 
-### Limitations
-
-The limitations of this study design include:
-
-- There is limited time before JDAP is implemented (~January 2011), so I will only have two pre-JDAP-implementation control time points.
-This limitation will be mitigated by the fact that there will be a lag between policy adoption is applicable to submitting authors and when their papers published.
-- There are many variables that are also important to views of community norms and decisions about sharing that I am not collecting to keep the survey short and maintain anonymity.
-These include university characteristics, industry affiliations, subfield, publication rate, and age.
-- This study makes no attempt to understand the rigor with which data sharing is encouraged in journals beyond their written policies:  many journals without policies nonetheless expect data sharing and many with written policies fail to enforce them.
-- The opinions of corresponding authors with respect to data sharing may not be typical of all authors:  a future study could be done to quantify this.
-- By only inviting authors to participate the first time they are listed as corresponding authors within our study scope, the population we are polling will shift gradually over time away from highly-prolific authors.
-- Respondents may be reluctant to self-report when they do not share their datasets, particularly as their sense of sharing as a community norm increases, since survey respondents are often reluctant to report engaging in socially undesirable behavior.
-- It will be difficult or impossible to derive causality direction for an association between reported data sharing behaviour and reported perception of data sharing as a community norm.
-- Finally, this study only facilitates a relatively short-term look at policy effect:  it will likely take many more years for the effect of these policies to be fully felt.
-
-Analysis of policy impact will be done using a modification of the commonly accepted difference-in-difference approach, as described by `r citep(bib["abadie2010synthet"])`.
-The responses of authors who published in JDAP-adopting journals will be compared, over time, to a) the responses of authors who publish in in-community journals that do not adopt JDAP, and b) the responses of authors who publish in outside-community journals that do not adopt JDAP.
-Because it is not clear which in-community and outside-community journals would provide the best counterfactual control of the JDAP-adopting journals, we will construct a “synthetic control” from a combination of responses across a subset of the control journals, as described in `r citep(bib["abadie2010synthet"])`.
-
-### Sample size
-
-The proposed study is subject to two different types of uncertainty:  uncertainty about the estimation of aggregate parameters, and also “uncertainty about the ability of the control group to reproduce the counterfactual of how the treated unit would have evolved in the absence of the treatment” (`r citep(bib["abadie2010synthet"])`.
-It is difficult to know how to conduct a formal power analysis in these conditions.
-We have based our sample size decisions on the following information.
-
-For populating the “treatment arm,” we plan to ask all corresponding authors of all JDAP-adopting journals.
-The average number of papers published per month in the JDAP journals is 168.
-Previous studies suggest 10%-30% of authors will complete the survey `r citep(c(bib["haeusslerinforma"], bib["wren2007the-wri"]))`.
-If we assume a response rate of 20%, we will receive about 33 responses from the intervention group every month.
-This would result in 95% confidence intervals around a Likert mean of 3.5 out of 7 ranges from 2.4 to 4.6.
-If these confidence intervals prove too wide to enable effective comparisons, we could aggregate the monthly data into less frequent samples across time.
-
-For populating the “control arms,” we recognize that the uncertainty is predominantly determined by the applicability of the controls.
-Little information is currently available to determine, a priori, which journals will serve as appropriate controls.
-As such, we suggest that surveying twice as many control journals as treatment journals may be an appropriate rule of thumb.
-This balances the need to avoid overpowering the study (and thereby increasing survey-fatigue and effort) with a desire to ensure the most useful results (anticipating that unexpected future events may render some controls inappropriate during the three years of this study, as well as recognizing that the quality of inference improves as the number of available comparison units increases `r citep(bib["abadie2010synthet"])`.
-
-Control journals will be selected by manual selection from a set of journals identified through ISI Journal Citation report categories as well as co-citation lists.
-Attempts will be made to choose journals with comparable impact factors and inclination to produce quantitative datasets.
-
-A 20% response rate and two control groups that are each twice as large as our treatment arm means we would receive about 33 treatment responses, 66 in-community control responses, and 66 outside-community responses per month.
-In total, we expect about 165 responses per month.
-Over the three years of data collection, this would lead to almost 6000 responses.
-The actual number of responses will be less than this, because will only invite each corresponding author once.
-On the other hand, the number of articles published by journals may increase over time and thus lead to a larger-than-anticipated sample.
-
-Finally, we note that to the best of our knowledge, a similar study has not been administered and/or published.
-If this sample size proves to be inadequate, the results can be viewed as pilot information to help inform future studies.
-
-### Data sharing plan
-
-Recruitment email addresses will be associated with the journal and month of publication.
-No other identifying information (author names, article title, etc) will be retained from ISI Web of Science.
-The researcher will not keep a record of participants’ names nor interface with them personally or by phone.
-Questionnaire responses will be submitted via online web survey tool ViewsFlash®:  the recruitment email addresses will not be linked to their corresponding survey response, but only linked in aggregate (in groups defined by journal and month of publication).
-
-Email addresses that are voluntarily provided by participants will be kept only for the duration of the prize drawing each month, and will not be linked to the survey responses in any way.
-
-Survey responses will be associated with journal and month of publication.
-The survey also asks the subjects to self-identify their job title (student, postdoc, tenured faculty, etc.)  We believe these datapoints will not be sufficient to permit reidentification, and will make no attempts to identify the respondents.
-
-To maximize the usefulness of this research, we plan to make the anonymous questionnaire responses openly available in a data repository for reuse, after aggregating or obfuscating any responses that could otherwise facilitate identification.
-
-### Recruitment
-
-Participants will be recruited from corresponding authors who publish in specific journals between November 2010 and February 2012.
-Specifically, email addresses will be collected for original research papers published the previous month (or 3 previous months, for the initial month of recruitment) in each of the target journals, using the ISI Web of Science.
-The email addresses will be associated with the journal and month of publication.
-No other identifying information (author names, article title, etc) will be retained.
-
-Recruitment email lists will be compared across months, and emails only sent to those who have not previously received a recruitment email to reduce survey fatigue and ill-will.
-
-A recruitment email will be sent to all identified email addresses, excluding those who had received a recruitment email in a prior month.
-The email invitation will include a URL where subjects can learn more about the study and then read a fact sheet, consent, and participate if they choose.
-This email will also contain an “opt out” option, which will remove their address from the reminder list.
-Those who have not “opted out” will be contacted by email again, a week later, politely asking them to take the survey if they haven’t already.
-
-Before the initial round of invitations is sent, we will inform journal editors of this ongoing survey and provide contact information in case they have questions, suggestions, or concerns.
-
-Individual participants can expect to spend 7-10 minutes maximum answering the online questionnaire.
-
-Previous studies suggest 10%-30% of authors will complete the survey `r citep(c(bib["haeusslerinforma"], bib["wren2007the-wri"]))`.
-
-some more: `r citep(c(
-bib["2015thank-y"],
-bib["anagnostou2015when-da"],
-bib["nosek2015scienti"],
-bib["stodden2018an-empi"],
-bib["budin-ljosne2014data-sh"],
-bib["hate2015sweat-s"],
-bib["naudet2018data-sh"],
-bib["curty2017attitud"],
-bib["linek2017data-sh"],
-bib["longo2016data-sh"],
-bib["berger2016iscbs-i"],
-bib["chigusa2017state-o"],
-bib["womack2015researc"],
-bib["doi:10.1002/asi.23917"],
-bib["plos-medicine-editors2016can-dat"],
-bib["van-tuyl2016water-w"],
-bib["vasilevsky2017reprodu"],
-bib["doi:10.1002/asi.23336"],
-bib["pearce2011data-sh"],
-bib["alsheikh-ali2011public-"],
-bib["vines2013mandate"],
-bib["roche2014trouble"],
-bib["roche2015public-"],
-bib["lin2014recomme"],
-bib["whitlock2016a-balan"],
-bib["naughton-l2016making-"],
-bib["teunis2015do-corr"],
-bib["fetterman2015the-rep"]
-))
-`
-
-## Methods
-
-# Introduction
-Some researchers are sceptical regarding data archiving.
-We conducted a survey in order to find out how the adoption of data archiving policies by journals affects researcher's attitudes towards archiving and sharing data.
-
-# The Survey
-
-## Method
-
-```{r, cache=TRUE, message=FALSE, echo=FALSE}
+```{r, cache=TRUE, message=FALSE, echo=FALSE, warning=FALSE}
 
@@
 
-The survey was carried out using [Survey Monkey](www.surveymonkey.com).
-Invitations to participate were sent out monthly between February 2011 and March 2014 to a selection of between $`r min(n_invitations_by_sent_month$N)`$ and $`r max(n_invitations_by_sent_month$N)`$ (with an average of $`r round(mean(n_invitations_by_sent_month$N))`$) authors of recently published articles in a pre-selected sample of journals.
-<!-- TODO: how were the journals selected -->
-The invitations were sent out to a total of $`r nrow(invitation_timing)`$ authors, and $`r nrow(d)`$ responded (corresponding to a non-response rate of $`r round(100*nrow(d)/nrow(invitation_timing))`$\%).
-Figure 1 shows the numbers of invitations and responses by the date of the author's last publication.
-Participants filled in a questionnaire consisting of 15 multiple-choice questions regarding their attitudes, concerns and experiences with data archiving and sharing.
+[TODO: LIST THE JOURNALS IN CONTROL AND JDAP ARMS]
 
-## Results
+The invitations were sent out monthly between February 2011 and March 2014 to a total of $`r nrow(invitation_timing)`$ authors, and $`r nrow(d)`$ responded (corresponding to a response rate of $`r round(100*nrow(d)/nrow(invitation_timing))`$\%).
 
-In the following, I will present an overview of the responses to questions 1, 2, and 9. The questions asked about the strength of agreement/disagreement with the following statements:
+## Primary analysis
 
-* _Question 1_ It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
+### Attitudes on data sharing and data archiving norms
+
+The questions asked about the strength of agreement/disagreement with the following statements:
+
+* It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
 Include data sharing that occurs by any mechanism (e.g.
 emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
-* _Question 2_ It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
-* _Question 9_ I would seek alternative journals if JDAP was introduced.
+* It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
 
@@
 
-```{r, fig.width=10, fig.height=5, echo=FALSE}
+```{r, fig.width=10, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
 
+library(plyr)
 library(dplyr)
@@
 library(reshape2)
-source("./src/aux_functions.R")
 source("./src/plotLikert.R")
@@
 responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
-question_labels <- c('Q_1'='"Data sharing is a community norm."\n(Question 1)',
-                     'Q_2'='"Data archiving is a community norm."\n(Question 2)',
-                     'Q_9'='"I would seek alternative journals\nif JDAP was introduced."\n(Question 9)')
-tmp <- melt(d, measure.vars=c('Q_1','Q_2','Q_9')) #,'Q_12','Q_13'))
+question_labels <- c('Q_1'='"Data sharing is a community norm."',
+                     'Q_2'='"Data archiving is a community norm."')
+tmp <- melt(d, measure.vars=c('Q_1','Q_2'))
 tmp$variable <- as.character(tmp$variable)
@@
 print(p)
-
 ```
 
-### Inferential statistics
+The potential effect of JDAP adoption on authors' attitudes is might be confounded by two other factors.
+Firstly, groups of researchers publishing in journals which are not planning to adopt the JDAP (or at least have not done so yet) may inherently differ from groups publishing in journals which were open to adopting the JDAP.
+Secondly, attitudes regarding data archiving may improve over time.
 
-```{r, message=FALSE, eval=TRUE, echo=FALSE}
+[TODO: REPHASE PARAGRAPHS BELOW]
+
+In order to test for an effect of policy change on attitudes while controlling for potential confounding effects, we used an ordinal logistic regression model with three predictors: (i) journal type _(cNonJDAPJournal)_, (ii) (centered) publication date in years _(cDate)_, and (iii) a variable indicating whether the article was published after the the journal adopted a data archiving policy _(cAfterPolicyChange)_.
+
+```{r, message=FALSE, eval=TRUE, echo=FALSE, warning=FALSE}
 
@@
 
-The potential effect of JDAP adoption on authors' attitudes is might be confounded by two other factors.
-Firstly, groups of researchers publishing in journals which are not planning to adopt the JDAP (or at least have not done so yet) may inherently differ from groups publishing in journals which were open to adopting the JDAP.
-Secondly, attitudes regarding data archiving may improve over time.
-
-In order to test for an effect of policy change on attitudes while controlling for potential confounding effects, we used an ordinal logistic regression model with three predictors: (i) journal type _(cNonJDAPJournal)_, (ii) (centered) publication date in years _(cDate)_, and (iii) a variable indicating whether the article was published after the the journal adopted a data archiving policy _(cAfterPolicyChange)_.
-
 The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 1*.
@@
 
-The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 2*.
+Similarily, the following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 2*.
 According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data archiving* by a factor of $1.57$ (CI=$[1.33; 1.90]$), while the remaining two predictors do not show any statistically significant effects.
@@
 
-# Appendix
+## Exploratory analysis
 
-## Appendix A: Questionnaire Structure
-<!-- TODO: Add response options below. -->
+### Data sharing and archiving behavior
 
-How strongly do you disagree/agree with the following statements? (Regarding the next two questions.)
+<!-- Field: Q12 -->
+Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
 
-<!-- Field: Q4 -->
-1.
-It is the community norm in my field to share, with qualified researchers, datasets that support the results of peer-reviewed research articles.
-Include data sharing that occurs by any mechanism (e.g.
-emailing datasets upon request, posting datasets to lab websites, including datasets in journal supplementary information or data repositories).
+```{r, fig.width=10, fig.height=5, echo=FALSE, eval=FALSE}
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
 
-<!--
-_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
--->
+id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
+cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
+cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
+cur_d$variable <- NULL
 
-```{r, fig.width=7, fig.height=5, echo=FALSE}
+levels <- c("ALL datasets are publicly available online","SOME but not all of the datasets are publicly available online", "NONE of the datasets are publicly available online","We did not collect any data for that publication", "I don't know", "Other (please specify)")
+cur_d$value <- ordered(cur_d$value, levels=levels)
+
+tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
+
+p <- ggplot(tmp, aes(x = label_PolicyAdoptedAtPublication, y = 100*class.Proportion, fill = value)) + geom_bar(stat = "identity")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
+
+p + theme_bw()
+
+```
+
+<!-- Field: Q13 -->
+IF ALL or SOME datasets associated with this paper are publicly available, where are the datasets hosted?
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
 
@@
 
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
+cur_d <- d[,c(id_vars,paste0('Q_7_', 1:6))]
+cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
+cur_d$variable <- NULL
 
-tmp <- melt(d, measure.vars=c('Q_1'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website", "Not applicable", "The entire dataset is in the body of the paper", "Other (please specify)")
+cur_d$value <- ordered(cur_d$value, levels=levels)
+
+tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
+
+p <- ggplot(tmp, aes(x = label_PolicyAdoptedAtPublication, y = 100*class.Proportion, fill = value)) + geom_bar(stat = "identity")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
+
+p + theme_bw()
+
+```
+
+<!-- Field: Q14 -->
+If NONE or only SOME of the datasets are publicly available, which of the following reflect your experience for the dataset(s) not publicly available, for this paper? Choose all that apply.
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
+cur_d <- d[,c(id_vars,paste0('Q_8_', 1:10))]
+cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
+cur_d$variable <- NULL
+
+levels <- c("The dataset has been submitted to a repository and is currently under embargo",
+            "We plan to publicly archive the dataset in the future",
+            "We plan to share the dataset upon request",
+            "We hadn't considered publicly archiving the dataset",
+            "We considered publicly archiving data and decided not to",
+            "We wanted to publicly archive the data\nbut were not able to, due to resource limitations",
+            "We wanted to publicly archive the data\nbut were not able to, for other reasons",           
+            "We wanted to publicly archive the data\nbut were not able to, due to licencing or funder restrictions",
+            "Not applicable", "Other (please specify)")
+cur_d$value <- ordered(cur_d$value, levels=levels)
+
+tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
+
+p <- ggplot(tmp, aes(x = label_PolicyAdoptedAtPublication, y = 100*class.Proportion, fill = value)) + geom_bar(stat = "identity")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
+
+p + theme_bw()
+
+```
+
+<!-- Field: Q11-->
+To your knowledge, what are the policies of these stakeholders as they apply to online public archiving of the datasets associated with your (month) (year) publication in (journal)?
+Choose all that apply
+
+```{r, fig.width=10, fig.height=5, echo=FALSE}
+
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
+
+facet_labels <- c('Journal', 'Funder(s)', 'Employer or institution')
+responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
+tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
+tmp$variable <- facet_labels[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
+tmp$variable <- factor(tmp$variable, levels=facet_labels)
+
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+#p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
 
@@
 
-<!-- Field: Q5 -->
-2. It is the community norm in my field to publicly archive all supporting datasets online, for use by anyone for any purpose, upon publication of a peer-reviewed research article.
-
-<!--
-_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
--->
-
-```{r, fig.width=7, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
-
-tmp <- melt(d, measure.vars=c('Q_2'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
-print(p)
-
-```
+### Data archiving history
 
 <!-- Field: Q7 -->
-3. Do any of your published research papers have publicly archived datasets?
-  a. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
-  b. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
-  c. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
-  d. No, none of my paper-related datasets are publicly available on the internet
-  e. I've never published a paper based on a dataset collected by me or my co-authors
-  f. I'm not sure if any of my papers have publicly available datasets
+Do any of your published research papers have publicly archived datasets?
 
@@
 print(p)
-
 ```
 
+### Experiences with consequences of data archiving
+
 <!-- Field: Q9 -->
-4.
 To your knowledge, how often have you experienced the following situations as a result of sharing the datasets behind your published research with investigators outside your research groups?
 Include experiences from datasets shared outside your research groups through any mechanism, including public archiving, selected distribution, or shared individually upon request (for example, in response to an email request).
+
  a.  I formed new collaborations <!-- Field: Q9_1 / Q_4_1 -->
@@
 
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
-tmp <- melt(d, measure.vars=paste0('Q_4_',1:16 ))
-tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
-p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
-
-print(p)
-
-```
-
-And again, this time limited to people with at least one paper with archived data:
+Limited to people with at least one paper with archived data:
 
@@
 
-And one more time, for people with no archived data:
+```{r, fig.width=10, fig.height=5, echo=FALSE, eval=FALSE}
 
-And again, this time limited to people with at least one paper with archived data:
+# Everyone 
+library(ggplot2)
+library(reshape2)
+source("./src/plotLikert.R")
 
-```{r, fig.width=10, fig.height=5, echo=FALSE}
+responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
+tmp <- melt(d, measure.vars=paste0('Q_4_',1:16 ))
+tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+
+print(p)
+
+```
+
+```{r, fig.width=10, fig.height=5, echo=FALSE, eval=FALSE}
+
+# For people with no archived data:
 
@@
 responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
-tmp <- melt(d_with_data, measure.vars=paste0('Q_4_',1:16 ))
+tmp <- melt(d_with_no_data, measure.vars=paste0('Q_4_',1:16 ))
 tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
@@
 ```
-<!-- Field: Q11-->
-5.
-To your knowledge, what are the policies of these stakeholders as they apply to online public archiving of the datasets associated with your (month) (year) publication in (journal)?
-Choose all that apply
-	a.  The journal  <!-- Field: Q11_1 -->
-	b.  Your funder(s)  <!-- Field: Q11_2 -->
-	c.  Your employer or institution  <!-- Field: Q11_3 -->
+
+### Attitudes on data reuse
+
+How strongly do you disagree/agree with the following statements?
+
+<!-- Field: Q21 -->
 
@@
 
-facet_labels <- c('Journal', 'Funder(s)', 'Employer or institution')
-responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
-tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
-tmp$variable <- facet_labels[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
-tmp$variable <- factor(tmp$variable, levels=facet_labels)
+responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
 
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
-#p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
+question_labels <- c('Q_12'='"Using datasets collected by\ninvestigators outside my research group\nis important in my research."',
+                     'Q_13'='"Using datasets collected by\ninvestigators outside my research group\nis important in my teaching or other non-research projects."')
+tmp <- melt(d, measure.vars=c('Q_12','Q_13'))
+tmp$variable <- as.character(tmp$variable)
+tmp$variable <- ordered(nmap(tmp$variable, question_labels), levels=question_labels)
+#tmp$variable <- gsub("Q_", "Question ", tmp$variable) # gsub("Q_", "Question ", tmp$variable)
 
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
 print(p)
@@
 
-<!-- Field: Q12 -->
-6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
+### Opinions about JDAP policies
+The questions below refer to the Joint Data Archiving Policy.
 
-Response options:
-	a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
-	b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
-	c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
-	d.  I don't know   <!-- Field: Q12_4 -->
-	e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
-	f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
+Imagine you just found a great journal to target when submitting your next manuscript. You read the Instruction to Authors and discover the journal adheres to the Joint Data Archiving Policy (above).
 
-```{r, fig.width=10, fig.height=5, echo=FALSE, eval=FALSE}
-library(dplyr)
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
-cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
-cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
-cur_d$variable <- NULL
-
-levels <- c("ALL datasets are publicly available online","SOME but not all of the datasets are publicly available online",
-            "NONE of the datasets are publicly available online","We did not collect any data for that publication",
-            "I don't know", "Other (please specify)")
-cur_d$value <- ordered(cur_d$value, levels=levels)
-
-tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
-
-p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value, alpha=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
-p + theme_bw() + scale_fill_manual(values=c(rep("blue",2), rep("red",2), "grey", "green" )) + scale_alpha_manual(values=c(1,.5, 1,.5, 1,1))
-
-```
-
-<!-- Field: Q13 -->
-7. IF ALL or SOME datasets associated with this paper are publicly available, where are the datasets hosted?
-	a.  Journal supplementary information   <!-- Field: Q13_1 -->
-	b.  A repository for data or research output   <!-- Field: Q13_2 -->
-	c.  A personal or lab website   <!-- Field: Q13_3 -->
-	d.  The entire dataset is in the body of the paper   <!-- Field: Q13_4 -->
-	e.  Other (please specify)   <!-- Field: Q13_5/Q13_5_TEXT -->
-	f.  Not applicable   <!-- Field: Q13_6 -->
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
-cur_d <- d[,c(id_vars,paste0('Q_7_', 1:6))]
-cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
-cur_d$variable <- NULL
-
-levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website",
-            "Not applicable", "The entire dataset is in the body of the paper", "Other (please specify)")
-cur_d$value <- ordered(cur_d$value, levels=levels)
-
-tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
-
-p <- ggplot(tmp, aes(x = label_PolicyAdoptedAtPublication, y = 100*class.Proportion, fill = value)) + geom_bar(stat = "identity")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
-
-p + theme_bw()
-
-```
-
-<!-- Field: Q14 -->
-8. If NONE or only SOME of the datasets are publicly available, which of the following reflect your experience for the dataset(s) not publicly available, for this paper? Choose all that apply.
-	a.  The dataset has been submitted to a repository and is currently under embargo  <!-- Field: Q14_1 -->
-	b.  We plan to publicly archive the dataset in the future  <!-- Field: Q14_2 -->
-	c.  We plan to share the dataset upon request  <!-- Field: Q14_3 -->
-	d.  We hadn't considered publicly archiving the dataset  <!-- Field: Q14_4 -->
-	e.  We considered publicly archiving data and decided not to  <!-- Field: Q14_5 -->
-	f.  We wanted to publicly archive the data but were not able to, due to resource limitations  <!-- Field: Q14_6 -->
-	g.  We wanted to publicly archive the data but were not able to, for other reasons  <!-- Field: Q14_7 -->
-	h.  Other (please specify)  <!-- Field: Q14_8/Q14_8_TEXT -->
-	i.  Not applicable  <!-- Field: Q14_9 -->
-	j.  We wanted to publicly archive the data but were not able to, due to licencing or funder restrictions  <!-- Field: Q14_10 -->
-
-```{r, fig.width=10, fig.height=5, echo=FALSE}
-
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
-
-id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
-cur_d <- d[,c(id_vars,paste0('Q_8_', 1:10))]
-cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
-cur_d$variable <- NULL
-
-levels <- c("The dataset has been submitted to a repository and is currently under embargo",
-            "We plan to publicly archive the dataset in the future",
-            "We plan to share the dataset upon request",
-            "We hadn't considered publicly archiving the dataset",
-            "We considered publicly archiving data and decided not to",
-            "We wanted to publicly archive the data but were not able to, due to resource limitations",
-            "We wanted to publicly archive the data but were not able to, for other reasons",           
-            "We wanted to publicly archive the data but were not able to, due to licencing or funder restrictions",
-            "Not applicable", "Other (please specify)")
-cur_d$value <- ordered(cur_d$value, levels=levels)
-
-tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)
-
-p <- ggplot(tmp, aes(x = label_PolicyAdoptedAtPublication, y = 100*class.Proportion, fill = value)) + geom_bar(stat = "identity")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
-
-p + theme_bw()
-
-```
-
-The questions below refer to the Joint Data Archiving Policy, an example policy statement adopted by ... <!-- TODO -->
-
-<!-- Field: Q17 -->
-9. How strongly do you disagree/agree with this statement? I would seek alternative journals if I learned that my target journal had adopted the Joint Data Archiving Policy (above).
-
-<!--
-Response options:
-  i. Strongly Agree
-  ii. Agree
-  iii. Somewhat Agree
-  iv. Neutral
-  v. Somewhat Disagree
-  vi. Disagree
-  vii. Strongly Disagree
--->
+Would you seek an alternative journal?
 
@@
 
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+question_labels <- c('Q_9'='"I would seek alternative journals\nif JDAP was introduced')
+tmp <- melt(d, measure.vars=c('Q_9'))
+tmp$variable <- as.character(tmp$variable)
+tmp$variable <- ordered(nmap(tmp$variable, question_labels), levels=question_labels)
+#tmp$variable <- gsub("Q_", "Question ", tmp$variable) # gsub("Q_", "Question ", tmp$variable)
 
-tmp <- melt(d, measure.vars=c('Q_9'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
-
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
 print(p)
-
 ```
@@
 <!-- Field: Q18 -->
-10.
+
 Imagine you just found a great journal to target when submitting your next manuscript.
@@
 How strongly do you disagree/agree with the following statements?
-I am worried that ...
+How strongly do you disagree/agree with the following statements? I am worried that ...
+
  a.  others might do research I am currently working on  <!-- Field: Q18_1 -->
@@
 	k.  I might lose intellectual property or commercial opportunities  <!-- Field: Q18_11 -->
-	l.  Other worries (please specify)  <!-- Field: Q18_12/Q18_12_TEXT -->
 
@@
 
-responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
+responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
 tmp <- melt(d, measure.vars=paste0('Q_10_',1:11 ))
 tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("10_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
 p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
@@
 <!-- Field: Q19 -->
-11.
 Same instructions as the previous question: Imagine you just found a great journal to target when submitting your next manuscript.
@@
 I am pleased because...
+
  a.  others will build upon my work more easily  <!-- Field: Q19_1  -->
@@
 	h.  I think it is the right thing to do  <!-- Field: Q19_10  -->
-	i.  Other (please specify)  <!-- Field: Q19_11/Q19_11_TEXT  -->
 
@@
 
-responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
+responses <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+
 tmp <- melt(d, measure.vars=paste0('Q_11_',1:10 ))
@@
 tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("11_", "", .) %>% as.integer]
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
+p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
 p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
@@
 
-How strongly do you disagree/agree with the following statements?
+# Discussion
 
-<!-- Field: Q21 -->
-12.  Using datasets collected by investigators outside my research group is important in my research.
+What has happened since
 
-```{r, fig.width=7, fig.height=5, echo=FALSE}
+some more: `r citep(c(
+bib["2015thank-y"],
+bib["anagnostou2015when-da"],
+bib["nosek2015scienti"],
+bib["stodden2018an-empi"],
+bib["budin-ljosne2014data-sh"],
+bib["hate2015sweat-s"],
+bib["naudet2018data-sh"],
+bib["curty2017attitud"],
+bib["linek2017data-sh"],
+bib["longo2016data-sh"],
+bib["berger2016iscbs-i"],
+bib["chigusa2017state-o"],
+bib["womack2015researc"],
+bib["doi:10.1002/asi.23917"],
+bib["plos-medicine-editors2016can-dat"],
+bib["van-tuyl2016water-w"],
+bib["vasilevsky2017reprodu"],
+bib["doi:10.1002/asi.23336"],
+bib["pearce2011data-sh"],
+bib["alsheikh-ali2011public-"],
+bib["vines2013mandate"],
+bib["roche2014trouble"],
+bib["roche2015public-"],
+bib["lin2014recomme"],
+bib["whitlock2016a-balan"],
+bib["naughton-l2016making-"],
+bib["teunis2015do-corr"],
+bib["fetterman2015the-rep"]
+))
+`
 
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
+Response to plos
+Future work
+With this dataset
+Advanced stats
+Longer term study
+More jdap journals come out
 
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+## Future work
 
-tmp <- melt(d, measure.vars=c('Q_12'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+Did JDAP-adopting journals start being more eagerly adopted by people who like data archiving, or did the authors in JDAP journals change their minds?
 
-print(p)
+## Limitations
 
-```
+- This study makes no attempt to understand the rigor with which data sharing is encouraged in journals beyond their written policies:  many journals without policies nonetheless expect data sharing and many with written policies fail to enforce them.
+- The opinions of corresponding authors with respect to data sharing may not be typical of all authors:  a future study could be done to quantify this.
+- Respondents may be reluctant to self-report when they do not share their datasets, particularly as their sense of sharing as a community norm increases, since survey respondents are often reluctant to report engaging in socially undesirable behavior.
+This may take the form of non-response, or untruthful responses.
+- It will be difficult or impossible to derive causality direction for an association between reported data sharing behaviour and reported perception of data sharing as a community norm.
+- By only inviting authors to participate the first time they are listed as corresponding authors within our study scope, the population we are polling will shift gradually over time away from highly-prolific authors.
+- Finally, this study only facilitates a relatively short-term look at policy effect:  it will likely take many more years for the effect of these policies to be fully felt.
 
-<!-- Field: Q22 -->
-13. Using datasets collected by investigators outside my research group is important in my teaching or other non-research projects.
+# Data availability
 
-```{r, fig.width=7, fig.height=5, echo=FALSE}
+- IRB
+- Survey questions
+- Instructions to authors
+- Contact corresponding code
+- Comparison journals spreadsheet
+- R files
+- Raw data
 
-library(ggplot2)
-library(reshape2)
-source("./src/plotLikert.R")
+# Acknowlegements
 
-responses_agree_disagree <- c("Strongly Agree","Agree","Somewhat Agree","Somewhat Disagree","Disagree","Strongly Disagree") # response categories from top to bottom
+# Funding
 
-tmp <- melt(d, measure.vars=c('Q_13'))
-tmp$variable <- gsub("Q_", "Question ", tmp$variable)
-p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")
+Heather's postdoc funding.
 
-print(p)
-
-```
-
-<!-- Field: Q23/Q23_TEXT -->
-14. Please choose the title that most closely matches yours:
-
-<!-- Field: Q25 -->
-15. Do you have any comments on the topic, or suggestions for how to improve this questionnaire?
-
-<!-- Field: Q26 -->
-16. Thank you for completing this survey! If you would like to enter the drawing for a $20 Amazon gif... <!-- TODO -->
-
-## Appendix B: JDAP Adoption Dates
+# Appendix: JDAP Adoption Dates
 
@@
 
-## Bibliolography
+# Bibliolography
 

### 2018-03-21 manuscript.Rmd
updates

@@
 ---
-title: "Data Archiving Attitudes"
+title: Impact of journal data archiving mandates on author attitudes, experiences,
+  and practices
 author: "Heather A. Piwowar, Todd J. Vision"
-date: "March 20, 2018"
+csl: peerj.csl
 output:
+  md_document:
+    variant: markdown_github
   html_document:
@@
     fig_caption: yes
-csl: peerj.csl
 bibliography: input_references.bib
@@
 
-[TODO: LIST THE JOURNALS IN CONTROL AND JDAP ARMS]
+The invitations were sent out monthly between February 2011 and March 2014 to a total of $`r nrow(invitation_timing)`$ authors, and $`r nrow(d)`$ responded (corresponding to a response rate of $`r round(100*nrow(d)/nrow(invitation_timing))`$\%).
 
-The invitations were sent out monthly between February 2011 and March 2014 to a total of $`r nrow(invitation_timing)`$ authors, and $`r nrow(d)`$ responded (corresponding to a response rate of $`r round(100*nrow(d)/nrow(invitation_timing))`$\%).
+|position	| number of responses	| proprotion of responses |
+| ---       | ---           | --- |
+|postdoc|	        1049|	0.254|
+|tenured faculty|	986|	0.239|
+|(blank)|	        696|	0.169|
+|research staff|	470|   	0.114|
+|non-tenured faculty|	463|	0.112|
+|student|	        343|	0.083|
+|Other (please specify)|	117|	0.028|
+|Grand Total|	4124|	1|
+
+Journal policies as of December 2014:
+
+|journal	| policy start	| number of responses |
+| ---       | ---           | --- |
+|American Naturalist|2011-01-01|115|
+|Animal Behaviour||129|
+|Behavioral Ecology||62|
+|Behavioral Ecology and Sociobiology||78|
+|Biological Conservation||134|
+|Biological Journal of the Linnean Society|2011-09-03|102|
+|Biology Letters|2014-10-29|80|
+|BMC Biology|2014-08-19|22|
+|BMC Evolutionary Biology||102|
+|BMC Plant Biology||53|
+|Conservation Biology||71|
+|Conservation genetics||64|
+|Ecological Applications|2014-01-01|115|
+|Ecological Monographs|2011-01-01|25|
+|Ecology||156|
+|Evolution|2011-01-01|115|
+|Evolutionary Applications|2011-01-01|22|
+|Evolutionary Ecology||38|
+|FASEB Journal||143|
+|FEBBS Letters||113|
+|Functional Ecology|2012-12-05|59|
+|GENETICS|2010-01-01|95|
+|Genome research|2008-07-06|70|
+|Global Change Biology||124|
+|Heredity|2011-03-01|42|
+|ISME Journal||66|
+|Journal of Animal Ecology|2012-12-01|68|
+|Journal of Biogeography||70|
+|Journal of Ecology|2013-06-03|74|
+|Journal of Evolutionary Biology|2011-10-24|96|
+|Journal of Experimental Biology||179|
+|Journal of Experimental Botany||123|
+|Journal of Heredity|2013-01-01|32|
+|Journal of Molecular Evolution||23|
+|Journal of Paleontology||34|
+|Molecular Biology and Evolution|2010-12-31|104|
+|Molecular Ecology|2011-01-01|154|
+|Molecular Phylogenetics and Evolution||83|
+|Nature structural & molecular biology||50|
+|New Phytologist|2010-11-23|80|
+|Oecologia||151|
+|Oikos|2014-03-06|118|
+|Paleobiology||2|
+|Physiological Genomics||38|
+|PLoS Biology|2014-11-14|82|
+|Proceedings of the Royal Society B: Biological Sciences|2013-03-20|217|
+|Systematic Biology|2010-12-31|26|
+|The Plant Journal|2010-08-18|102|
 
@@
 
+### Free text comments
+
+There were 356 free text comments. A few representative ones:
+
+- You may wish to consider fields of research. In ecology I guard my data; for evolutionary studies I use online data. The fields have very different attitudes and approaches.
+- In ecology, we often spend years collecting datasets that are unique.  That effort, combined with the set of ideas that led to collection of the data, should convey a large degree of 'ownership'.  
+- Thanks for researching this question.
+I cannot share my data...
+unless someone directly requests it and guarantees shared authorship of the product.
+We invested tremendous amounts of money and personal effort in collecting and grooming these data, so we need to work through all the associated papers before others have a chance.
+- I think you could have more comments related to how cumbersome, time-consuming, and expensive this new requirement is to most researchers.
+- Putting the data into an archive will produce additional costs.
+How is going to pay for it?
+At the moment, we are rquested to keep the data for at least 10 years, and share them with colleagues upon request.
+This has worked so far, and I think we should leave it at that and not use up extra money that could be better used for funding science.
+- Science is about sharing ideas and data.
+If we don't do this it is not science.
+It's pretty simple.
+The only question is which datasets is it worth investing effort into sharing at what level of detail and standards.
+This is tricky to get the balance right but this debate should not negate the premise that we're about data sharing.
+- I personally find submitting your own data a bit tedious, and I would always be worried that someone would use arcane statistical models to contradict something I found, but in the end transparency is an important feature of science and it's ridiculous that we don't have to show our data.
+It is absolutely the right thing to do.
+
 # Discussion
@@
 some more: `r citep(c(
-bib["2015thank-y"],
 bib["anagnostou2015when-da"],
@@
 - Contact corresponding code
-- Comparison journals spreadsheet
 - R files
@@
 # Acknowlegements
+
+Everyone who took the survey.
 
@@
 
-table <- subset(relevant_jdap_adoption_dates, policy == "Required")[,c('JournalName','policy_start_str')]
-colnames(table) <- c('Journal', 'Adoption Date of JDAP or Equivalent Policy')
+table <- relevant_jdap_adoption_dates[,c('JournalName', 'policy', 'policy_start')]
+colnames(table) <- c('Journal', 'Policy', 'Adoption Date of JDAP or Equivalent Policy')
 rownames(table) <- NULL
-kable(table)
-
+# kable(table)
 ```

### 2018-03-21 data/src/pre_process_jdap_adoption_dates.R

@@ -3,7 +3,7 @@ library(zoo)
 source("../../src/aux_functions.R")
 
 
-dates <- read.csv("../info/Journal data archiving policies (as relevant to JDAP).csv", as.is=T)
+dates <- read.csv("../raw_data/Journal data archiving policies (as relevant to JDAP).csv", as.is=T)
 
 # extract only the relevant parts
 dates <- subset(dates, Abbreviation != "")[,c('Journal','Abbreviation','Policy.short','Date.policy.took.effect')]
@@ -28,5 +28,5 @@ dates$policy_start <- ""
 dates$policy_start[!is.na(dates$policy_start_str)] <- parse_date(dates$policy_start_str[!is.na(dates$policy_start_str)]) %>% as.character
 dates$policy_start
 
-write.table(dates, file="../Journal_JDAP_Adoption_Dates.csv")
-save(dates, file="../Journal_JDAP_Adoption_Dates.rda")
+write.table(dates, file="../derived/Journal_JDAP_Adoption_Dates.csv")
+save(dates, file="../derived/Journal_JDAP_Adoption_Dates.rda")

### 2018-03-21 data/src/pre_process_jdap_invitations.R

@@ -15,6 +15,6 @@ d$journal[d$journal=="unknown"] <- NA
 unique(d$note)
 d$note <- NULL
 
-write.table(d, file="../Invitations_Timing.csv")
+write.table(d, file="../derived/Invitations_Timing.csv")
 invitation_timing <- d
-save(invitation_timing, file="../Invitations_Timing.rda")
+save(invitation_timing, file="../derived/Invitations_Timing.rda")

### 2018-03-21 data/src/pre_process_responses.R

@@ -156,8 +156,8 @@ d <- select(d, ResponseID, ResponseDate, PublicationDate, Journal=journal, Q_1=Q
 d <- rename(d, Q_4_15_TEXT=Q_4_16, Q_4_16=Q_4_17, Q_6_6_TEXT=Q_6_7, Q_7_5_TEXT=Q_7_6, Q_7_6=Q_7_7, Q_8_8_TEXT=Q_8_9, 
             Q_8_9=Q_8_10, Q_8_10=Q_8_11, Q_10_12_TEXT=Q_10_13, Q_11_11_TEXT=Q_11_12 )
 
-save(d, file="../JDAP_Survey_Data_Tidy.rda")
-write.csv(d, file="../JDAP_Survey_Data_Tidy.csv")
+save(d, file="../derived/JDAP_Survey_Data_Tidy.rda")
+write.csv(d, file="../derived/JDAP_Survey_Data_Tidy.csv")
 
 
 

### 2018-03-21 manuscript.Rmd
updates to discussion

@@
 ---
-title: Impact of journal data archiving mandates on author attitudes, experiences,
+title: Influence of journal data archiving mandates on author attitudes, experiences,
   and practices
@@
 
-Journal policies as of December 2014:
+Journal policies as of December 2014 (surveys were sent out between February 2011 and March 2014 to authors who published between November 2010 and November 2013):
 
@@
 
-What has happened since
+data policies are becoming more prevalent: seven journals announced data archiving mandates during the course of the survey (and another three journals implemented policies shortly after the suvey completed).
 
-some more: `r citep(c(
-bib["anagnostou2015when-da"],
-bib["nosek2015scienti"],
-bib["stodden2018an-empi"],
-bib["budin-ljosne2014data-sh"],
-bib["hate2015sweat-s"],
-bib["naudet2018data-sh"],
-bib["curty2017attitud"],
-bib["linek2017data-sh"],
-bib["longo2016data-sh"],
-bib["berger2016iscbs-i"],
-bib["chigusa2017state-o"],
-bib["womack2015researc"],
-bib["doi:10.1002/asi.23917"],
-bib["plos-medicine-editors2016can-dat"],
-bib["van-tuyl2016water-w"],
-bib["vasilevsky2017reprodu"],
-bib["doi:10.1002/asi.23336"],
-bib["pearce2011data-sh"],
-bib["alsheikh-ali2011public-"],
-bib["vines2013mandate"],
-bib["roche2014trouble"],
-bib["roche2015public-"],
-bib["lin2014recomme"],
-bib["whitlock2016a-balan"],
-bib["naughton-l2016making-"],
-bib["teunis2015do-corr"],
-bib["fetterman2015the-rep"]
-))
-`
+even so, a minority of journal policies require data sharing `r citep(c(bib["vasilevsky2017reprodu"],bib["naughton-l2016making"]))`
 
-Response to plos
-Future work
-With this dataset
-Advanced stats
-Longer term study
-More jdap journals come out
+Even when there are journal policies, often not sufficient to achieve reproducability for the majority of studies `r citep(c(bib["roche2015public"], bib["stodden2018an-empi"], bib["naudet2018data-sh"]))`
 
-## Future work
+suggesting author personality `r citep(c(bib["linek2017data-sh"]))` or social norms `r citep(c(bib["anagnostou2015when-da"], bib["womack2015researc"]))` may play a larger factor than journal policy.
 
-Did JDAP-adopting journals start being more eagerly adopted by people who like data archiving, or did the authors in JDAP journals change their minds?
+Findings here are consistent with other findings that authors more likely to share data if they had prior experience sharing or reusing data
+`r citep(c(bib["Piwowar_2011"]))`.
 
-## Limitations
+Could be helpful for journals to help spread the word about worries that are unfounded.
+For example, authors are worried about scooping, but it rarely happens -- almost all of an author's papers about one of their own datasets occur within two years of its collection, whereas third-party papers are still accumulating six years later `r citep(c(bib["piwowar2013data-re"]))`.
+In areas where this is less true, journal policies could be modified to support it `r citep(c(bib["whitlock2016a-balan"], bib["doi:10.1002/asi.23336"]))`
+
+Similarily, although of course data archiving has a cost, it also has a good return on investment in terms of research output `r citep(c(bib["piwowar2011data-ar"]))`.
+
+The longitudinal study nature of this study is useful -- comparing across journals is frought, as stronger data archiving policies are disproportionately found in higher impact journals `r citep(c(bib["vasilevsky2017reprodu"], bib["piwowar2008a-revie"]))`.
+
+cite this? `r citep(c(bib["van-tuyl2016water-w"]))`. 
+also maybe this?  `r citep(c(bib["fetterman2015the-rep"]))`.
+
+still pulling these in to discussion notes `r citep(c(bib["budin-ljosne2014data-sh"],bib["lin2014recomme"],bib["roche2014trouble"],bib["vines2013mandate"],bib["pearce2011data-sh"],bib["alsheikh-ali2011public"]))`
+
+Limitations of this study include:
 
@@
 
-- IRB
-- Survey questions
-- Instructions to authors
-- Contact corresponding code
-- R files
-- Raw data
+- IRB (now in dropbox)
+- Recruitment emails (now in dropbox)
+- Journal policies (instructions to authors as of January 29, 2011): zip of html (now in dropbox)
+- Survey questions (now in dropbox)
+- [Survey responses](https://github.com/hpiwowar/jdap/blob/master/data/raw_data/JDAP_Survey_Data.csv)
+- [Full text comments](https://github.com/hpiwowar/jdap/blob/master/data/full_text_comments.txt)
+- [Contact corresponding authors scripts](https://github.com/hpiwowar/contact_corresponding)
+- [Manuscript R files](https://github.com/hpiwowar/jdap)
 
@@
 
-# Appendix: JDAP Adoption Dates
+```{r, fig.width=7, fig.height=5, echo=FALSE}
+# JDAP Adoption Dates
 
-```{r, fig.width=7, fig.height=5, echo=FALSE}
 library(knitr)

### 2018-03-22 manuscript.Rmd
methods, results, and discussion updates

@@
 
-## The promise of data sharing
+## Data archiving policies
 
@@
 `r citep(c(bib["blumenthal1997withhol"], bib["ochsner2008much-ro"], bib["savage2009empiric"]))`.
-
-## Data archiving journal policies
 
@@
 
-## Analysis
+## Analysis approach
 
-The responses of authors who published in JDAP-adopting journals were compared, over time, to  the responses of authors who published in similar journals that did not adopt JDAP.
+The primary analysis will be based on responses to be a seven-point Likert scale asking how strongly authors believe:  “It is the community norm in my field to publicly share datasets upon study publication by archiving all datasets online, for use by anyone for any purpose.”  Our goal is to see if author's responses to this question were influenced by publishing in a journal that had implemented JDAP.
 
-The primary analysis will be a seven-point Likert scale asking how strongly authors believe:  “It is the community norm in my field to publicly share datasets upon study publication by archiving all datasets online, for use by anyone for any purpose.”  About twelve other survey questions will allow secondary and exploratory analyses.
+The potential effect of JDAP adoption on authors' attitudes is might be confounded by two other factors.
+First, groups of researchers publishing in journals which are not planning to adopt JDAP may inherently differ from groups publishing in journals which were open to adopting the JDAP.
+Second, attitudes regarding data archiving may improve over time for all authors, independent of journal or policy.
+
+In order to test the effect of policy change on attitudes while controlling for potential confounding effects, we used an ordinal logistic regression model with three predictors: (i) whether the jounal adopted JDAP _(cNonJDAPJournal)_, (ii) the date the authors published their paper _(cDate)_, and (iii) a variable indicating whether the article was published after the the journal adopted a data archiving policy _(cAfterPolicyChange)_.
+Confidence intervals were obtained by profile likelihood.
+If the confidence intervals do not contain $1$ for the _(cAfterPolicyChange)_ variable then the policy would have had an affect on attitudes, independent of publication date or whether the journal was the type to adopt a JDAP policy.
+
+We further tested the policy correlation by comparing the fit of two models, one model with all three of the above variables, and one model with two variables excluding the policy change predictor (_cAfterPolicyChange_).
+If, using a likelihood-ratio test, the full model was a statistically better fit than the model without the policy change variable, it would support the hypothesis that the differences in authors attitudes were related to the policy adoption.
+
+Twelve other survey questions allowed secondary and exploratory analyses.
 
@@
 
-The following plots show the responses regarding the attitudes towards data sharing and archiving for participants who (i) published in journals which have note adopted the JDAP so far ('No JDAP'), (ii) published in journals which had not _yet_ adopted the JDAP before publication ('Before JDAP'), and (iii) journals which had adopted the JDAP before publication ('After JDAP).
+The following plots show the responses regarding the attitudes towards data sharing and archiving for participants who (i) published in journals which have note adopted the JDAP so far ('No JDAP'), (ii) published in journals which had not _yet_ adopted the JDAP before publication ('Before JDAP'), and (iii) journals which had adopted the JDAP after publication ('After JDAP).
 
@@
 
-The potential effect of JDAP adoption on authors' attitudes is might be confounded by two other factors.
-Firstly, groups of researchers publishing in journals which are not planning to adopt the JDAP (or at least have not done so yet) may inherently differ from groups publishing in journals which were open to adopting the JDAP.
-Secondly, attitudes regarding data archiving may improve over time.
+The following plots show the responses regarding the attitudes towards data sharing and archiving for participants who (i) published in journals which have note adopted the JDAP so far ('No JDAP'), (ii) published in journals which had not _yet_ adopted the JDAP before publication ('Before JDAP'), and (iii) journals which had adopted the JDAP after publication ('After JDAP).
 
-[TODO: REPHASE PARAGRAPHS BELOW]
-
-In order to test for an effect of policy change on attitudes while controlling for potential confounding effects, we used an ordinal logistic regression model with three predictors: (i) journal type _(cNonJDAPJournal)_, (ii) (centered) publication date in years _(cDate)_, and (iii) a variable indicating whether the article was published after the the journal adopted a data archiving policy _(cAfterPolicyChange)_.
+According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data sharing* by a factor of $1.36$ (CI=$[1.16; 1.60]$), while publishing date and whether the journal ever adopted a JDAP policy did not show any statistically significant effects.
+The estimated coefficients and confidence intervals are shown below.
 
@@
 # summary(m4)
-m4.justchange <- polr(respQ1 ~ 1 + cAfterPolicyChange, data=d , Hess=TRUE)
 m4.nochange <- polr(respQ1 ~ 1 + cNonJDAPJournal + cDate, data=d , Hess=TRUE)
@@
 m5 <- polr(respQ2 ~ 1  + cAfterPolicyChange + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
-m5.justchange <- polr(respQ2 ~ 1 + cAfterPolicyChange , data=d, Hess=TRUE)
 m5.nochange <- polr(respQ2 ~ 1 + cNonJDAPJournal + cDate, data=d, Hess=TRUE)
@@
 
-aov.m4.justchange <- anova(m4, m4.justchange)
 aov.m4.nochange <- anova(m4, m4.nochange)
-aov.m5.justchange <- anova(m5, m5.justchange)
 aov.m5.nochange <- anova(m5, m5.nochange)
@@
 
-The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 1*.
-Effects are statistically significant at the $\alpha=0.05$ level when the transformed confidence intervals do not contain $1$.
-Confidence intervals were obtained by profile likelihood.
-According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data sharing* by a factor of $1.36$ (CI=$[1.16; 1.60]$), while the remaining two predictors do not show any statistically significant effects.
-
 ```{r, message=FALSE, eval=TRUE, echo=FALSE}
@@
 
-We conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
-The first likelihood-ratio test, comparing the full three-predictor model with a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m4.nochange[["   Df"]][2]`)=`r aov.m4.nochange[["LR stat."]][2]`$, $p<0.001$).
-A second likelihood-ratio test comparing the full model with a reduced model using _only_ the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m4.justchange[["   Df"]][2]`)=`r aov.m4.justchange[["LR stat."]][2]`$, $p=`r aov.m4.justchange[["Pr(Chi)"]][2]`$).
+The result of two likelihood-ratio tests supported these findings.
+The first likelihood-ratio test, comparing the full three-predictor model to a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m4.nochange[["   Df"]][2]`)=`r aov.m4.nochange[["LR stat."]][2]`$, $p<0.001$), suggesting that the date of publication and whether a journal adopted JDAP are not as important in to an author's opinion about *data sharing* the data as whether the author published after a JDAP policy was introduced.
 
@@
 
-Similarily, the following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios) for responses to *question 2*.
-According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data archiving* by a factor of $1.57$ (CI=$[1.33; 1.90]$), while the remaining two predictors do not show any statistically significant effects.
+We found the similar results when we looked at the author's responses to community norms about *data archiving* rather than data sharing.
+The following table shows the estimated coefficients and 95\%-confidence intervals (transformed to odds ratios).
+According to the model estimates, the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding *data archiving* by a factor of $1.57$ (CI=$[1.33; 1.90]$).
+Being a nonJDAP journal is a significant predictor in this case, though with a much lower odds ratio.
 
-Here too, we conducted two likelihood-ratio tests to assess the effect of change in policy and the other predictors on reported attitudes.
-The first likelihood-ratio test, comparing the full three-predictor model with a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m5.nochange[["   Df"]][2]`)=`r aov.m5.nochange[["LR stat."]][2]`$, $p<0.001$).
-A second likelihood-ratio test comparing the full model with a reduced model using _only_ the policy change predictor (_cAfterPolicyChange_) revealed no statistically significantly difference ($\chi^2(`r aov.m5.justchange[["   Df"]][2]`)=`r aov.m5.justchange[["LR stat."]][2]`$, $p=`r aov.m5.justchange[["Pr(Chi)"]][2]`$).
+Comparing the full three-predictor model with a reduced model _without_ the effect of policy change revealed a significantly better fit for the full model ($\chi^2(`r aov.m5.nochange[["   Df"]][2]`)=`r aov.m5.nochange[["LR stat."]][2]`$, $p<0.001$), indicating again that the policy change was a statistically significant predictor of the author's responses about data archiving attitudes.
 
@@
 
-data policies are becoming more prevalent: seven journals announced data archiving mandates during the course of the survey (and another three journals implemented policies shortly after the suvey completed).
+We found that more authors believed that data sharing and data archiving were norms in their field after they published in a journal with a JDAP policy.
+
+Data archiving policies are becoming more prevalent: seven journals announced data archiving mandates during the course of the survey (and another three journals implemented policies shortly after the suvey completed).
 
@@
 
-Even when there are journal policies, often not sufficient to achieve reproducability for the majority of studies `r citep(c(bib["roche2015public"], bib["stodden2018an-empi"], bib["naudet2018data-sh"]))`
+Journal policies do help  `r citep(c(bib["vines2013mandate"], bib["Piwowar_2011"], bib["alsheikh-ali2011public"]))`, though often not sufficient to achieve data availability for the majority of studies `r citep(c(bib["Piwowar_2011"], bib["alsheikh-ali2011public"], bib["roche2015public"], bib["stodden2018an-empi"], bib["naudet2018data-sh"]))`.
 
-suggesting author personality `r citep(c(bib["linek2017data-sh"]))` or social norms `r citep(c(bib["anagnostou2015when-da"], bib["womack2015researc"]))` may play a larger factor than journal policy.
-
-Findings here are consistent with other findings that authors more likely to share data if they had prior experience sharing or reusing data
-`r citep(c(bib["Piwowar_2011"]))`.
+This suggests author personality `r citep(c(bib["linek2017data-sh"]))` or social norms `r citep(c(bib["anagnostou2015when-da"], bib["womack2015researc"]))` may play a larger factor.
 
@@
 
-Similarily, although of course data archiving has a cost, it also has a good return on investment in terms of research output `r citep(c(bib["piwowar2011data-ar"]))`.
+Similarily, the free text comments suggested authors are concerned about the cost of data archiving.
+It may help to spread the word that money research funders spend on data archiving is good return on investment in terms of research output `r citep(c(bib["piwowar2011data-ar"]))`.
 
@@
 
-cite this? `r citep(c(bib["van-tuyl2016water-w"]))`. 
-also maybe this?  `r citep(c(bib["fetterman2015the-rep"]))`.
+Our findings are consistent with previous studies that found authors were more likely to share data if they had prior experience sharing or reusing data: `r citep(c(bib["Piwowar_2011"]))`.
 
-still pulling these in to discussion notes `r citep(c(bib["budin-ljosne2014data-sh"],bib["lin2014recomme"],bib["roche2014trouble"],bib["vines2013mandate"],bib["pearce2011data-sh"],bib["alsheikh-ali2011public"]))`
+Several recommendations have been made for journals seeking to form a data archiving policy `r citep(c(
+bib["doi:10.1002/asi.23336"],
+bib["van-tuyl2016water-w"],
+bib["roche2014trouble"],
+bib["lin2014recomme"]))`
 
@@
 - [Manuscript R files](https://github.com/hpiwowar/jdap)
+- [News blog about the study](https://studyonimpactofjournaldatapolicies.wordpress.com/)
 

### 2018-05-02 manuscript.Rmd
add two more refs

@@
 
+Also work in these:
+- The influence of journal submission guidelines on authors' reporting of statistics and use of open research practices: bib["giofre2017the-inf"]
+- Journal Data Sharing Policies and Statistical Reporting Inconsistencies in Psycholog: bib["nuijten"]
+
 Limitations of this study include:

### 2018-11-21 manuscript.Rmd
make more past tense, add start of abstract, fix references

--- 2018-03-22 manuscript.Rmd
@@
 output:
+  word_document:
+    fig_caption: yes
   md_document:
     variant: markdown_github
+  pdf_document:
+    fig_caption: yes
+    number_sections: yes
+    toc: yes
   html_document:
@@
     toc: yes
-  pdf_document:
-    fig_caption: yes
-    number_sections: yes
-    toc: yes
-  word_document:
-    fig_caption: yes
 bibliography: input_references.bib
@@
 
+Several journals adopted the Joint Data Archiving Policy in early 2011, as described at http://datadryad.org/jdap.
+
+This was a great opportunity to study the effect of journal data sharing mandates on the attitudes, behaviour, experiences of authors to help inform future policy decisions.
+
+The invitations were sent out monthly between February 2011 and March 2014 to a total of 23853 23853  authors, and 4102 4102 responded (corresponding to a response rate of 17%).
+
+the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding data sharing by a factor of 1.36
+1.36
+ (CI=[1.16;1.60]
+1.16
+1.60
+), while publishing date and whether the journal ever adopted a JDAP policy did not show any statistically significant effects.
+
+We found the similar results when we looked at the author’s responses to community norms about public data archiving rather than peer-to-peer data sharing
+
+this study only facilitates a relatively short-term look at policy effect: it will likely take many more years for the effect of these policies to be fully felt.
+
 # Introduction
@@
 As a result, authors often actively or passively withhold their research datasets from other investigators
-`r citep(c(bib["blumenthal1997withhol"], bib["ochsner2008much-ro"], bib["savage2009empiric"]))`.
+`r citep(c(bib["blumenthal1997withhol"], bib["ochsner2008much"], bib["savage2009empiric"]))`.
 
@@
 The most direct impact is likely a change in frequency of data sharing, and a shift to data archiving locations specified in the policy.
-Early studies suggest that authors who publish in journals with data sharing policies are more likely to share their data than authors who publish similar studies in similar journals `r citep(c(bib["piwowar2008a-revie"], bib["Piwowar_2011"]))`, but these investigations were correlative and did not attempt to directly measure the impact of journal policies over time.
+Early studies suggest that authors who publish in journals with data sharing policies are more likely to share their data than authors who publish similar studies in similar journals `r citep(c(bib["piwowar2008a-revie"], bib["Piwowar2011"]))`, but these investigations were correlative and did not attempt to directly measure the impact of journal policies over time.
 Previous work emphasizes the importance of sharing data through best-practice archiving methods and locations.
@@
 
-A few previous studies have estimated the impact of sharing data on the experiences of authors `r citep(c(bib["blumenthal2006data-wi"], bib["gleditsch2003posting"], bib["piwowar2007sharing"], bib["ventura2005mandato"]))`, but there is much to be learned in this area to ground expectations, accurately estimate costs and benefits, and learn about ways policies could be improved to enhance positive experiences and avoid negative ones.
+A few previous studies have estimated the impact of sharing data on the experiences of authors `r citep(c(bib["blumenthal2006data-wi"], bib["gleditsch2003posting"], bib["piwowar2007sharing"], bib["ventura2005"]))`, but there is much to be learned in this area to ground expectations, accurately estimate costs and benefits, and learn about ways policies could be improved to enhance positive experiences and avoid negative ones.
 
@@
 
-## Upcoming policy change is a useful opportunity for policy evaluation
+## Policy change is a useful opportunity for policy evaluation
 
-Several journals plan to adopt the Joint Data Archiving Policy in early 2011, as described at http://datadryad.org/jdap.
+Several journals adopted the Joint Data Archiving Policy in early 2011, as described at http://datadryad.org/jdap.
 
-This is a great opportunity to study the effect of journal data sharing mandates on the attitudes, behaviour, experiences of authors to help inform future policy decisions.
+This was a great opportunity to study the effect of journal data sharing mandates on the attitudes, behaviour, experiences of authors to help inform future policy decisions.
 
 The JDAP policy requires data sharing in a public archive.
-Early evidence suggests stronger policies are associated with a higher frequency of data sharing `r citep(c(bib["piwowar2008a-revie"], bib["Piwowar_2011"]))`.
+Early evidence suggests stronger policies are associated with a higher frequency of data sharing `r citep(c(bib["piwowar2008a-revie"], bib["Piwowar2011"]))`.
 Since JDAP requires data sharing as a condition of publication, studying this policy adoption is an opportunity to possibly measure the maximum likely effect.
@@
 Because measurements of actual dataset archiving behavior can be accurately measured with a retrospective analysis of research artifacts, our proposed survey does not emphasize data archiving behaviour.
-Instead, the questionnaire will focus on information that is difficult or impossible to collect without a timely survey of data-producing investigators.
+Instead, the questionnaire focused on information that is difficult or impossible to collect without a timely survey of data-producing investigators.
 
@@
 
-Although some data sharing mandates appear to have achieved almost universal sharing `r citep(bib["noor2006data-sh"])`, this is not always the case `r citep(bib["ochsner2008much-ro"])`.
-Several surveys have asked about author’s perceived obstacle to sharing data `r citep(c(bib["hedstrom2008researc"], bib["scherle2008buildin"]))`, but changes in these attitudes have not been monitored across a policy change.
-To our knowledge, the impact of data sharing mandates have only been subject to one evaluation:  the editors of Physiological Genomics briefly surveyed their authors and reviewers two years after instituting a policy that required public archiving of gene expression microarray data `r citep(bib["ventura2005mandato"])`, though unfortunately no baseline measurements are available about attitudes before the policy.
-Interestingly, a recent large-scale evaluation `r citep(bib["Piwowar_2011"])` into the prevalence of microarray data sharing found this same journal to have the highest rate of public archiving.
+Although some data sharing mandates appear to have achieved almost universal sharing `r citep(bib["noor2006data-sh"])`, this is not always the case `r citep(c(bib["ochsner2008much"]))`.
+Several surveys have asked about author’s perceived obstacle to sharing data `r citep(c(bib["hedstrom2008researc"]))`  `r citep(c(bib["scherle2008buildin"]))`, but changes in these attitudes have not been monitored across a policy change.
+To our knowledge, the impact of data sharing mandates have only been subject to one evaluation:  the editors of Physiological Genomics briefly surveyed their authors and reviewers two years after instituting a policy that required public archiving of gene expression microarray data `r citep(c(bib["ventura2005"]))`, though unfortunately no baseline measurements are available about attitudes before the policy.
+Interestingly, a recent large-scale evaluation `r citep(c(bib["Piwowar2011"]))` into the prevalence of microarray data sharing found this same journal to have the highest rate of public archiving.
 
@@
 
-The instrument used to collect data is be an online questionnaire.
-The questionnaire is designed to elicit the respondent’s practices, experiences, and opinions around public archiving of research datasets by asking about their opinion of community norms, recent behaviour with respect to a recently published paper, previous experiences with data sharing, and attitudes toward hypothetical journal policies
+The instrument used to collect data was an online questionnaire.
+The questionnaire was designed to elicit the respondent’s practices, experiences, and opinions around public archiving of research datasets by asking about their opinion of community norms, recent behaviour with respect to a recently published paper, previous experiences with data sharing, and attitudes toward hypothetical journal policies.
 
-## Control jounrnals and sample size
+## Control journals and sample size
 
-The proposed study is subject to two different types of uncertainty:  uncertainty about the estimation of aggregate parameters, and also “uncertainty about the ability of the control group to reproduce the counterfactual of how the treated unit would have evolved in the absence of the treatment” (`r citep(bib["abadie2010synthet"])`.
-It was difficult to know how to conduct a formal power analysis in these conditions, so we  based our sample size decisions on the following information.
+The study was subject to two different types of uncertainty:  uncertainty about the estimation of aggregate parameters, and also “uncertainty about the ability of the control group to reproduce the counterfactual of how the treated unit would have evolved in the absence of the treatment” (`r citep(bib["abadie2010synthet"])`.
 
-For populating the “treatment arm,” we asked all corresponding authors of all JDAP-adopting journals.
+It was difficult to know how to conduct a formal power analysis in these conditions, so we  based our sample size decisions on the following information:
 
-For populating the “control arms,” we recognized that the uncertainty is predominantly determined by the applicability of the controls.
+- For populating the “treatment arm,” we asked all corresponding authors of all JDAP-adopting journals.
+
+- For populating the “control arms,” we recognized that the uncertainty is predominantly determined by the applicability of the controls.
 Little information is currently available to determine, a priori, which journals will serve as appropriate controls.
@@
 
-Control journals were selected by manual selection from a set of journals identified through ISI Journal Citation report categories as well as co-citation lists.
+- Control journals were selected by manual selection from a set of journals identified through ISI Journal Citation report categories as well as co-citation lists.
 Attempts were made to choose journals with comparable impact factors and inclination to produce quantitative datasets.
 
-Assuming a 20% response rate and a control arm that was twice as large as the treatment arm, we expected a maximum of 165 responses per month, or almost 6000 responses over the course of the three year study.
+- Assuming a 20% response rate and a control arm that was twice as large as the treatment arm, we expected a maximum of 165 responses per month, or almost 6000 responses over the course of the three year study.
 The actual number of responses was expected to be lower than this because only invited each corresponding author the first time they published a paper.
@@
 
-The email invitation included  a URL where subjects can learn more about the study and then read a fact sheet, consent, and participate if they choose.
+The email invitation included a URL where subjects could learn more about the study and then read a fact sheet, consent, and participate if they choose.
 This email contained contain an “opt out” option, which will remove their address from the reminder list.
@@
 
-The primary analysis will be based on responses to be a seven-point Likert scale asking how strongly authors believe:  “It is the community norm in my field to publicly share datasets upon study publication by archiving all datasets online, for use by anyone for any purpose.”  Our goal is to see if author's responses to this question were influenced by publishing in a journal that had implemented JDAP.
+The primary analysis was based on responses on a seven-point Likert scale asking how strongly authors believe:  “It is the community norm in my field to publicly share datasets upon study publication by archiving all datasets online, for use by anyone for any purpose.”  Our goal was to see if author's responses to this question were influenced by publishing in a journal that had implemented JDAP.
 
@@
 ```
-
-The following plots show the responses regarding the attitudes towards data sharing and archiving for participants who (i) published in journals which have note adopted the JDAP so far ('No JDAP'), (ii) published in journals which had not _yet_ adopted the JDAP before publication ('Before JDAP'), and (iii) journals which had adopted the JDAP after publication ('After JDAP).
 
@@
 
-Journal policies do help  `r citep(c(bib["vines2013mandate"], bib["Piwowar_2011"], bib["alsheikh-ali2011public"]))`, though often not sufficient to achieve data availability for the majority of studies `r citep(c(bib["Piwowar_2011"], bib["alsheikh-ali2011public"], bib["roche2015public"], bib["stodden2018an-empi"], bib["naudet2018data-sh"]))`.
+Journal policies do help  `r citep(c(bib["vines2013mandate"], bib["Piwowar2011"], bib["alsheikh-ali2011public"]))`, though often not sufficient to achieve data availability for the majority of studies `r citep(c(bib["Piwowar2011"], bib["alsheikh-ali2011public"], bib["roche2015public"], bib["stodden2018an-empi"], bib["naudet2018data-sh"]))`.
 
@@
 
-Our findings are consistent with previous studies that found authors were more likely to share data if they had prior experience sharing or reusing data: `r citep(c(bib["Piwowar_2011"]))`.
+Our findings are consistent with previous studies that found authors were more likely to share data if they had prior experience sharing or reusing data: `r citep(c(bib["Piwowar2011"]))`.
 
@@
 bib["lin2014recomme"]))`
+
+Also work in these:
+- The influence of journal submission guidelines on authors' reporting of statistics and use of open research practices: `r citep(c(bib["giofre2017the-inf"]))`
+- Journal Data Sharing Policies and Statistical Reporting Inconsistencies in Psychology: `r citep(c(bib["nuijten"]))`
+- 10.1371/journal.pone.0194768
 
@@
 
-# Acknowlegements
+# Acknowlegements and Notes
 
-Everyone who took the survey.
+We'd like to sincerely thank everyone who took the survey.
+
+The first paragraphs of the introduction are verbatim from Piwowar, Day & Fridsma (2007); its original publication was under a CC-BY license.
+
+The authors finally completed the analysis and posted this preprint more than five years after the study (and Heather's postdoc) ended: better late than never.
+The introduction has been only lightly revised since it was written 5 years ago; regretfully, important recent studies have no doubt been overlooked.
 
@@
 
-Heather's postdoc funding.
+This study was funded by DataONE (OCI-0830944) and Dryad (DBI-0743720). The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
 

### 2018-11-22 manuscript.Rmd
add a draft of the abstract

@@
 ---
-title: Influence of journal data archiving mandates on author attitudes, experiences,
-  and practices
+title: Influence of journal data archiving mandates on author attitudes, experiences, and practices
 author: "Heather A. Piwowar, Todd J. Vision"
@@
 output:
-  word_document:
+  html_document:
+    css: style.css
     fig_caption: yes
+    keep_md: yes
+    number_sections: yes
+    toc: yes
   md_document:
@@
     toc: yes
-  html_document:
-    css: style.css
+  word_document:
     fig_caption: yes
-    keep_md: yes
-    number_sections: yes
-    toc: yes
 bibliography: input_references.bib
@@
 
-Several journals adopted the Joint Data Archiving Policy in early 2011, as described at http://datadryad.org/jdap.
+INTRODUCTION: Some journals require that their authors share the raw data behind their analyses, but little is known about how the introduction of these mandates affects the attitudes, experiences, and behaviour of authors.
 
-This was a great opportunity to study the effect of journal data sharing mandates on the attitudes, behaviour, experiences of authors to help inform future policy decisions.
+OBJECTIVE: This study measures the correlation of journal data sharing policies with the data sharing attitudes, experiences, and behaviour of authors.
 
-The invitations were sent out monthly between February 2011 and March 2014 to a total of 23853 23853  authors, and 4102 4102 responded (corresponding to a response rate of 17%).
+METHODS: An online questionaire was sent to all corresponding authors of 48 journals in the fields of evolution, ecology, and general biology who published papers between November 2010 and March 2014.
+The online questionnaire was designed to measure the respondent’s practices, experiences, and opinions around public archiving of research datasets by asking about their opinion of community norms, recent behaviour with respect to a recently published paper, previous experiences with data sharing, and attitudes toward hypothetical journal policies.
 
-the introduction of the JDAP data archiving policy significantly increases the odds of a positive response regarding data sharing by a factor of 1.36
-1.36
- (CI=[1.16;1.60]
-1.16
-1.60
-), while publishing date and whether the journal ever adopted a JDAP policy did not show any statistically significant effects.
+RESULTS:  Survey invitations were sent out to 23,853 corresponding authors; 4,102 responded (response rate of 17%).
+Twenty-one of the journals had adopted a journal sharing requirement by the time the survey was completed.
+We found the introduction of a data archiving policy significantly increased the respodent's belief that data sharing was a community norm, whereas publishing date and whether the journal ever adopted a data sharing policy did not show any statistically significant effects.
+In exploratory analysis, the introduction of a journal data policy was correlated with a decrease in worries about "scooping", and increased the feeling that data archiving policies was "the right thing to do."
 
-We found the similar results when we looked at the author’s responses to community norms about public data archiving rather than peer-to-peer data sharing
+CONCLUSION: This study suggests that although journals may be afraid that data archiving policies will be met with resentment and a backlash from their authors, the attitudes of autohrs after policies go into effect is positive and the policies serve to increase and normalize data sharing within their disciplines.
 
-this study only facilitates a relatively short-term look at policy effect: it will likely take many more years for the effect of these policies to be fully felt.
+DATA AVAILABILITY:  The data from this study is publicly available.
 
